### 2022-09-05 manuscript.Rmd
Initial commit

---
title: "Analytical reproducibility of published meta-analyses on clinical psychological
  interventions"
shorttitle: "Meta-analyses reproducibility"
leftheader: "Lopez-Nicolas et al."

author:
 - name: "Rubén López-Nicolás"
   affiliation: "1"
   corresponding: yes
   adress: "Facultad de Psicología, Campus de Espinardo, Universidad de Murcia, edificio n° 31, 30100, Murcia, Spain"
   email: "rlopez@um.es"
 - name: "Daniel Lakens"
   affiliation: "2"
 - name: "Jose A. López-López"
   affiliation: "1"
 - name: "Maria Rubio-Aparicio"
   affiliation: "3"
 - name: "Carmen López-Ibáñez"
   affiliation: "1"
 - name: "Desirée Blázquez-Rincón"
   affiliation: "1"
 - name: "Alejandro Sandoval-Lentisco"
   affiliation: "1"
 - name: "Julio Sánchez-Meca"
   affiliation: "1"

affiliation: 
 - id: "1"
   institution: "University of Murcia, Spain"
 - id: "2"
   institution: "Eindhoven University of Technology, The Netherlands"
 - id: "3"
   institution: "University of Alicante, Spain"

author_note: |
 All materials, data, and analysis script coded have been made publicly available on the Open Science Framework: https://osf.io/6cmzh/. This research has been funded with a grant from the Spanish Ministry of Science and Innovation by FEDER funds (Project nº PID2019-104080GB-I00), and by a predoctoral grant (FPU18/04805) from the Spanish Ministry of Universities.The funders had no role in study design, data collection and analysis, decision to publish, or preparation of the manuscript.

abstract: |
  Nowadays, meta-analysis is one of the most useful and powerful research approaches, however, this relevance relies on its credibility. In recent years different concerns on credibility of psychological research have emerged. Analytical reproducibility of scientific results could be considered as the minimal threshold of it.  In this study, our purpose was to assess the analytical reproducibility of a set of meta-analyses, as well as the reusability of the data as it was available. From a random sample of papers containing at least one meta-analysis on effectiveness of interventions in psychology used in a previous study, 217 meta-analyses were selected. We first tried to retrieve the original data by recovering a data file, recoding the data from document files (pdf, doc) or on request. Second, through a multi-stage workflow, we tried to reproduce the main results of each meta-analysis using these data. The original data were retrieved for 146 meta-analyses from different sources. Of these, in a first stage 52 showed a discrepancy larger than 5% in the main results, in 25 of them this discrepancy was solved with minor adjustments, or correction of coding errors. In the remaining 27, different issues were identified in an in-depth review of the papers, such as: reporting inconsistencies, lack of some data or transcription errors. Current practices of data sharing in meta-analyses hamper the reusability of the meta-analyses. On the other hand, the implementation of new tools would help to avoid certain errors in the meta-analysis reporting process.

keywords: "meta-analysis, reproducibility, data sharing, data reusability, research synthesis"

bibliography: ["meta-analyses_reproducibility.bib"]

figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : no
mask              : no
csl               : "apa.csl"

class             : "jou, a4paper"
output            : papaja::apa6_pdf
header-includes:
   - \usepackage{caption}
   - \captionsetup[table]{textfont={it}, labelfont={bf}, singlelinecheck=false, labelsep=newline}
   - \captionsetup[figure]{textfont={it}, labelfont={bf}, singlelinecheck=false, labelsep=newline}
---

Nowadays, meta-analysis is widely considered as one of the most useful and powerful research approaches. Given the ongoing growth in the number of scientific publications [@bornmann2021], evidence synthesis approaches -such as meta-analysis- are becoming increasingly relevant. This relevance rests on their credibility, which can be threatened by a lack of rigorous application or poor-quality reporting [@gurevitch2018]. Therefore, given their importance and their role as a useful guide to evidence-based practice, these threats to their credibility need to be closely monitored.
In recent years different concerns on credibility -based on reproducibility and replicability issues- of psychological research -and of other scientific disciplines- have emerged. Several projects have systematically attempted to assess the replicability and reproducibility of different scientific published results (e.g., [@camerer2018; @errington2021a; @klein2014a; @opensciencecollaboration2015]. Those initiatives showed many failures to replicate the published results. In this context, the empirical assessment of scientific published results credibility has become a major task for the scientific community.

There are different approaches to the empirical assessment of scientific credibility or confidence. Reproducibility refers to the attempt to obtain the same results as in the original publication, using the same data and the same analytical procedure. Robustness refers to the assessment of the sensitivity of the originally published results and conclusions to variations in the original analytical strategy using the same data. Replicability is a core principle of the scientific method and refers to the fact that the same scientific evidence should be observed when independent researchers try to answer the same research question from the same approach at different moments using different data. In other words, obtaining the same results, using different data and answering the same question [@nationalacademiesofsciencesengineeringandmedicine2019; @nosek2022]. In this project we focus on the reproducibility of meta-analyses.

The reproducibility of all published scientific results could be considered as the minimal threshold of scientific credibility [@hardwicke2021]. Different approaches can be adopted for the empirical assessment of reproducibility, for instance @nosek2022 make the distinction between process reproducibility and outcome reproducibility. Following this framework, a process reproducibility assessment could be carried out reviewing the availability of the materials, data, and precise details of the analytical strategy in the report or in an analysis script file required to proceed with the reproduction attempt. On the other hand, an outcome reproducibility assessment would be carried out when the required elements are retrievable, and the reproduction attempt proceeds. It is worth noting that, depending on how the analytical details are available, the challenges, implications and workload of these outcome reproducibility checks are different. The availability of the original analysis script code (i.e., the original computational instructions in a programming language) facilitates reproducibility analysis by simply re-running it, although this is seldom available [@hardwicke2020; @hardwicke2022; @lopez-nicolas2021]. When only a summary is available in the research reports (which is the most common scenario in practice), a task of reconstruction of the original analysis scheme is required. The challenges and implications of failed reproductions in both cases may be of a different nature.

In the meta-analytic arena, some reproducibility attempts have been carried out in recent years. For instance, some process reproducibility assessments have shown an important lack of data availability in machine-readable formats, and an almost complete absence of analysis script code availability [@lopez-nicolas2021; @polanin2020]. Furthermore, some outcome reproducibility assessments have shown a considerable number of failures when trying to reproduce the primary effect sizes of some published meta-analyses by recollecting primary data from primary studies [@gotzsche2007; @maassen2020; @tendal2009] possibly due to lack of details on how primary effect sizes were selected and computed. In these outcome reproducibility studies, the main task entails reconstructing the original data by retrieving them from the source, namely the included primary studies. Thus, their assessment focus is on this stage of the analysis pipeline of a meta-analysis, which usually involves decisions on how to deal with the multiplicity of effects in the primary studies and the computation process of standardized effect sizes.

Usually, reproducibility studies use the original data available from the original authors (e.g., [@artner2020; @hardwicke2021; @hardwicke2018]. This puts the focus of the assessment at a different stage of the research pipeline: reusability of the available data, challenges for the reconstruction of the original analysis scheme, reporting errors, etc. Therefore, in order to carry out a reproducibility analysis in this way, the original data must be available. Although data availability seems to have improved in the last years [@hardwicke2018; @tedersoo2021; @wallach2018], systematic reviews and meta-analyses appear to be a special case. Typically, the data collected for a meta-analysis is study-level summary data extracted from published primary studies and is commonly reported in the paper itself through tables or forest plots. This may lead to the idea that common data sharing practices do not apply to meta-analysis. For instance, @page2022 analysed the content of data availability statements from a set of meta-analyses published in 2020. Only 31% included a data availability statement and only 13% of these included a link to access the data openly, with 23% stating that all relevant data are available in the paper itself, 10% stating that data sharing is no applicable as no datasets were generated, 8% stating that data sharing is no applicable as the data is drawn from already published literature, and 42% stating that data were available upon request. It is surprising that, even just considering meta-analyses that included a data availability statement, some of them assume that such practices do not apply to meta-analyses or that the data in the article itself is sufficient.

## Purpose 
Previous research has revealed that there is room for improvement at different stages of the meta-analytic process pipeline. In this study our purpose is twofold. First, we broadened previous process reproducibility assessments by considering the possible availability of the data upon request to the original authors and by assessing the reusability of the meta-analytic data in the different formats in which they are usually available. Second, we verified the outcome reproducibility of the meta-analyses that were process-reproducible using the available data. We attempted to explore meta-analysis outcome reproducibility at a different stage or level than previous work that is more focused on primary effect sizes reproducibility, using the primary effects sizes already coded by the original authors.

```{r importing_data_and_descriptives, include=FALSE}

library(here)
source(here::here("analysis", "01_importing_data_and_descriptives.R"))

```

# Method

The pre-data analysis protocol (https://osf.io/42r3p/) was pre-registered on 19 October 2021. Any deviation from this protocol is explicitly acknowledged.

## Identification and selection of articles and meta-analyses 
In previous research we identified a pool of published meta-analytic reports on clinical psychological interventions through a systematic electronic search [@lopez-nicolas2021]. Of this pool, 100 were randomly selected using a random number generator between 1 and the total number of meta-analyses identified. The full search strategies and a summary of the screening process are available at: https://osf.io/z5vrn/, and the workflow of the randomly selection process is available at: https://osf.io/cp293/.
From these 100 articles, each independent reported meta-analysis with at least 10 primary studies was selected. In case no meta-analysis reported in a paper had at least 10 studies, the meta-analysis with the highest number of primary studies was selected, even if this meta-analysis integrated less than 10 studies. `r Words(n_mas_less_10)` of the articles included in this report were in this situation. Therefore, our unit of analysis was each independent meta-analysis selected under these criteria. A total of `r n_mas_total` independent meta-analyses were selected.

## Retrieval of primary data
The availability of necessary primary data was checked. First, we looked for machine-readable data files through links leading to third-party repositories or in supplementary material hosted by the journal. Secondly, we looked for available data through tables or forest plots in document format in the meta-analytic report itself or supplementary material. In these cases, the primary data had to be manually re-coded to reuse it. On the other hand, if the primary data of a meta-analysis were not directly available, neither in a data file nor in a document file, we attempted to obtain the data through request to the corresponding author identified in the associated paper. We sent an initial request in June 2021 and a subsequent reminder in October 2021 if no reply was received. This reminder was sent to a more recent alternative email address if we were able to find one. If we were unable to obtain the data through the email request, the associated meta-analysis was labelled as not process reproducible. 
In order to be able to reproduce meta-analyses, mainly primary effects and their associated standard errors are required. These are generally computed from primary statistics retrieved from the primary studies such as means, standard deviations or sample sizes. In this sense, we tried to retrieve the least processed data possible. First, we sought for the primary statistics, recovered in `r sprintf("%0.0f%%", df_type_of_data$perc[3] * 100)` of the cases; second, we sought for the primary effects and their standard errors (or, alternatively, the sampling variances), recovered in `r sprintf("%0.0f%%", df_type_of_data$perc[2] * 100)` of the cases; finally, we sought for the primary effects and their confidential limits, recovered in `r sprintf("%0.0f%%", df_type_of_data$perc[1] * 100)` of the cases, from which the standard errors were approximated as follows:

$$se_i = (\frac{UB_i - LB_i}{2z_{\alpha/2}})$$

with $se_i$ being the standard error of the ith effect size, $UB_i$ and $LB_i$ the upper and lower confidence limits of confidence interval for the ith effect size, and $z_{\alpha/2}$ the $1 - z_{\alpha/2}$ quantile of the standard normal distribution (usually, $z_{\alpha/2} = 1.96$ assuming a 95% confidence interval).

## Reconstructing the original analytical scheme
To proceed with reproducibility attempts of the meta-analyses that were labelled as process reproducible, we first looked for the availability of the original analysis script. When it was available, analytical reproducibility was checked by rerunning the original script on the associated primary data. In most cases (`r sprintf("%0.0f%%", 100-((n_mas_w_script/df_process_rep$n[2]) * 100))`), the analysis script code was not available. Thus, in these cases we tried to reconstruct the original analytical scheme using the technical details reported in the paper. Specifically, we collected information on: (a) meta-analytic model originally assumed; (b) weighting scheme; (c) between-studies variance estimator; (d) confidence interval method; and (e) software used.  If any of these details about the analytical methods were not reported, but the software used was mentioned, we inferred the first four pieces of information from the default settings of the software used. If the software used was not reported, we inferred this information from the default settings of the most used software in the sample, which was *Comprehensive Meta-Analysis*. Additional information about the meta-analysis was collected that is not reported in this manuscript. The full list of variables collected is available in the Protocol (https://osf.io/tq4uf/) and a Codebook describing these variables is available at: https://osf.io/ym78s/.

## Data collection procedure 
Primary-level data and aggregate-level data described above, were coded by five members of the group. At a first pilot stage, a random sample of five articles of the total pool was independently coded by the five members and, subsequently, in a series of meetings, disagreements between the coders were resolved by consensus. Next, the initial pool of 100 included articles was split among four of them, 25 each. A random sample of 25 articles of the total pool was assigned to the fifth member to carry out independent double-coding of these cases, with the goal to track the reliability of the data collection process. Disagreements were resolved by consensus and checking the original materials.

## Reproducibility outcomes
Each meta-analysis was labelled using the following reproducibility success scheme: (a) reproducible; (b) not process-reproducible; (c) numerical error (d) decision error. Not process-reproducible refers to situations when we were unable to access the primary data neither through direct extraction nor upon request. Similar to previous studies (Artner et al., 2020; Hardwicke et al., 2018, 2021) an index of numerical error was computed (see Protocol https://osf.io/tq4uf/). This index expressed the differences between reproduced and original values as percentages. To avoid labelling minor numerical discrepancies related to numerical rounding as reproducibility problems, a 5% discrepancy threshold was set. Thus, a meta-analysis was labelled as numerical error if showed a discrepancy larger than 5%. 
Finally, decision error refers to situations where the $p_{reported}$ falls on the opposite side of the .05 boundary in relation to the $p_{reproduced}$. 
We mainly focused on analytical reproducibility of summary effects, their confidence bounds and the result of the null hypothesis significance test. Secondarily, we also assessed analytical reproducibility of other synthesis methods such as heterogeneity statistics.

## Reproducibility checks workflow 
Analytical reproducibility checks were carried out at different stages. Firstly, through reported analytic details or script code. When the analysis script code was available, computational reproducibility was checked by rerunning the script with the available primary data. In most cases, the analysis script code was not available. Thus, in these cases we coded the analytic details as explained above to fit equivalent meta-analytic models as a function of these details using the available primary data. This analysis scheme was programmed in the R environment [@r2022] using the *metafor* package [@viechtbauer2010]. The scripts are available at: …. 
Second, given that the manual recoding process is an error-prone task, some mistakes can appear. Thus, those meta-analyses labelled as numerical error and/or decision error in the previous stage were re-assessed by a different member of the team. In cases where an error was found in the originally coded results, analytic methods and/or primary data, the meta-analyses were reproduced again and re-labelled according to the updated results. 
Third, a qualitative assessment of the meta-analyses still labelled as numerical error and/or decision error was carried out. The same reviewers who checked for errors produced individual reports on the possible source of the discrepancy and its reproducibility was judged qualitatively by four of the other authors. This stage was a deviation from the pre-registered protocol, and made it possible to identify situations with obvious explanations, such as rounding, inverted signs, etc.
Finally, for meta-analyses that remained labelled as non-reproducible, an email was sent to the corresponding author of the associated paper explaining our aims, our approach, and our results regarding his/her meta-analysis and requesting additional information that could explain the mismatch between the original reported results and the reproduced results. We tried to solve the reproducibility issues within a month after the request and we updated the label accordingly.

# Results

From the 100 included papers, `r n_mas_total` independent meta-analyses were selected following the criteria explained above. These meta-analyses included `r round(k_mean, 2)` primary studies on average (`r sprintf("sd = %0.2f; median = %0.0f; interquartile range = %0.0f-%0.0f; range = %0.0f-%0.0f)", k_sd, k_median, k_q1, k_q3, range[1], range[2])`). Figure 1 displays the distribution of number of primary studies among the meta-analyses included in our sample. Original results and characteristics of these meta-analyses are available at: …

``` {r, fig.width = 6, fig.height=6, fig.cap="Distribution of the number of primary studies included in each of the meta-analyses. Vertical blue dotted lines represent the first quartile, median, and third quartile, respectively."}

hist_primary_studies

```

## Process reproducibility 
Figure 2 summarizes the primary data retrieval results. Based on the availability of primary data, either retrieved directly from the paper or upon request, `r df_process_rep$n[2]` meta-analyses (`r sprintf("%0.0f%%", df_process_rep$perc[2]*100)`, see Fig. 2a) were labelled as process reproducible. Of these `r df_process_rep$n[2]` meta-analyses, in about half of the cases the primary data was retrieved from a forest plot in the paper itself and in about a third of the cases the primary data was retrieved from supplementary files. Only in `r sprintf("%0.0f%%", df_source_primary_data$perc[1]*100)` of the cases the primary data was retrieved upon request (see Fig. 2b for further details). Although attempts were made to retrieve data for `r df_process_rep$n[1]+df_source_primary_data$n[1]` meta-analyses from `r sum(df_request$n)` different papers, data was only retrieved upon request for `r df_source_primary_data$n[1]` of them, from `r df_request$n[2]` different papers (`r sprintf("%0.0f%%", df_request$perc[2]*100)`, see Fig. 2c). In the remaining cases, a reply providing some reasons not to share was received in about a third of the cases (`r sprintf("%0.0f%%", df_request$perc[2]*100)`, see Fig 2c), whereas no reply was received in the rest. Table 1 summarises the different reasons given in cases where data was not provided upon request.

```{r}

kbl(
  df_reasons,
  format = "latex",
  booktabs = TRUE,
  col.names = c("Reason", "N", "%"),
  align = c("l", "c", "c"),
  caption = "Reasons given when data was not received upon request."
  ) %>% 
    column_spec(1, width = "7cm")

```

## Challenges faced retrieving primary data
In most cases, when the necessary data was available, such data was in document formats, as previously reported. Data available in tables or forest plots shared in *pdf* or *docx* format –either in the document itself or in the supplementary materials– was found to be highly prevalent. This led to a manual recoding of the primary data to be able to reuse them. Furthermore, when data was reported through general tables (i.e. tables listing all the primary studies included with their characteristics), it was not always obvious in which meta-analysis each data entry was included, leading to the time-consuming task of matching each data entry with each independent meta-analytic result reported in the paper. There were only `r df_source_primary_data$n[2]` meta-analyses (from`r sum(df_data_downloaded$Item)` different papers) of the `r df_process_rep$n[2]` labelled as process reproducible (`r sprintf("%0.0f%%", df_source_primary_data$perc[2]*100)`), where the task of retrieving the data required simply downloading the data in an machine-readable data file format.
On the other hand, as shown in Figure 2c, when the necessary data was not available, retrieving it upon request to the original authors led to a remarkably low success rate.

``` {r, fig.env = "figure*", fig.width = 10, fig.height=11, fig.cap="Percentage of (a) process-reproducible meta-analyses; (b) different types of sources of original data; and (c) data request results.", out.width = "100%"}

 figure2

```

## Outcome reproducibility 
The outcome reproducibility was checked in `r df_process_rep$n[2]` meta-analyses from `r nrow(df_nmas_wdata)` different papers. In `r filter(df_script, script == 1)$n` of these meta-analyses (`r sprintf("%0.0f%%", filter(df_script, script == 1)$n/sum(df_script$n)*100)`), all from the same paper, the original script code was available. Therefore, in these five cases, analytical reproducibility was checked running the original script analysis on the original primary data. In the remaining cases, the original analytical framework was reconstructed as explained above. 
```{r first_stage, include=FALSE}

rm(list=ls())
source(here::here("analysis", "02_first_stage.R"))

```
Following the first stage of re-analysis, `r nrow(df_to_rev)` meta-analyses were re-assessed because they were labelled as numerical error and/or decision error following the re-analysis scheme explained above. 
```{r second_stage, include=FALSE}

rm(list=ls())
source(here::here("analysis", "03_second_stage.R"))

```
Of these, `r nrow(df_to_reanalyse)` were re-analysed again as some coding errors were found in the second stage. After this, `r nrow(filter(df_to_reanalyse, numerical_error != "error"))` were re-labelled as reproduced and `r nrow(filter(df_to_reanalyse, numerical_error == "error"))` still had relevant discrepancies. Furthermore, `r nrow(filter(df_mas_revised, qualitative_check == "rep"))` were labelled as reproduced in the qualitative check because the discrepancy was probably explained by rounding issues, inverted signs for results (reported in absolute value) and primary data, minor reporting errors, or minor adjustments in the analytical scheme. In the remaining `r nrow(filter(df_mas_revised, qualitative_check == "request_information"))`, and in the `r nrow(filter(df_to_reanalyse, numerical_error == "error"))` re-analysed again without success, some issues or relevant discrepancies without apparent explanation were found. Figure 3 displays a scatterplot showing the consistency between the original and reproduced summary effect size and their confidence bounds of these `r nrow(df_to_scatter)` meta-analyses. 
Additionally, as a secondary analysis, the reproducibility of the $I^2$ heterogeneity statistic was explored. Figure 4 displays a scatterplot showing the consistency between the original and reproduced $I^2$ statistics. 
As shown in Figures 3 and 4, the discrepancies found in the heterogeneity statistic $I^2$ are larger than those found in the summary effects and their confidence intervals. The lack of precision of the available data (rounded data) or incomplete information on aspects such as the tau-squared estimator applied seem to have a substantial impact on the reproducibility of this result.

``` {r, fig.width = 7, fig.height=14, fig.cap="Scatterplot displaying the reproduced values as a function of the original values classified by whether or not decision error was found. Only the results of the 52 meta-analyses with a discrepancy of more than 5% identified in the first stage are displayed, but with the corrections made in the second stage. All values are in *d* scale. In panel (a) the summary effects are displayed and in panel (b) the confidence intervals. For (b) the colours represent lower or upper bound of the confidence interval."}
figure3

```

``` {r, fig.width = 7, fig.height=7, fig.cap="Scatterplot displaying the reproduced values as a function of the original values classified by whether or not decision error was found. Only the results of the 52 meta-analyses with a discrepancy of more than 5% identified in the first stage are displayed, but with the corrections made in the second stage. The values displayed are $I^2$ hetorogeneity statistics."}
figure4

```

## Main issues identified 
Different issues in these `r nrow(df_to_rev2)` meta-analyses were identified in the second stage. For instance, in one of the meta-analyses which showed discrepancies in the confidence limits, inconsistencies were found in the original meta-analytic report itself. The confidence limits originally reported for that meta-analysis were different in the abstract, main text and forest plot. Matching the reproduced results were those reported in the forest plot but not those reported in the text. Furthermore, inconsistencies in the original summary effect reported were found between the results reported in abstract and the results reported in the main text and the forest plot. This kind of original results reporting inconsistencies was also found in other cases. In another case where primary data were available in both a table and a forest plot, minor inconsistencies were also found between the primary data of the table and the forest plot. These appeared to be typos. 
Furthermore, regarding the number of primary data included, some inconsistencies were also found. For instance, in one of the meta-analyses, the main text reported the inclusion of 10 comparisons in the meta-analysis, whereas in a table of results 11 comparisons were reported for this meta-analysis. Furthermore, the results reported for this meta-analysis in the text and in the results table were different. Moreover, one apparently included primary study –it was cited in the text as such– did not appear in the table of main characteristics of included studies. On the other hand, in 11 meta-analyses the primary data retrieved from the supplementary materials were not sufficient to reach the number of primary studies stated as included in this meta-analysis in the original report.

```{r third_stage, include=FALSE}

rm(list=ls())
source(here::here("analysis", "04_third_stage.R"))

```

## Original authors clarifications
These `r nrow(df_to_rev2)` meta-analyses were from `r sum(df_success_request$n)` different papers. Therefore, `r sum(df_success_request$n)` clarification requests with information about the study aims, methods and preliminary results were sent to the corresponding authors of the original articles. A reply was received in only `r df_success_request$n[2]`  of the `r sum(df_success_request$n)` cases.
In one of them, the original authors sent back a link to an OSF repository where the original data and analysis script were stored. This link was not reported in the paper by mistake according to the authors themselves. The script was run on these data and the results were successfully reproduced. In this case, the data previously used were retrieved from a forest plot (means and standard deviations) and a table (sample sizes) reported in the paper. The previous discrepancy was explained by two cases included in the original meta-analysis from the same primary study that were reported with the same ID in the forest plot and were not correctly matched with their corresponding sample size extracted from the table. This situation exemplifies the potential issues arising from having to reconstruct the original data from tables and figures and not having open access to the original data file. 
In the other case, the data used was retrieved from a huge table in supplementary material (*docx*) with all effect sizes and their confidence limits. The original authors sent back this same table by increasing the number of decimal places of the effect sizes and after correcting some wrong values that they themselves detected in that process. This fixed the discrepancies for some of the meta-analyses in this paper.

# Discussion 
The main aim of this study was to explore the analytical reproducibility of a sample of published meta-analyses on the effectiveness of clinical psychology interventions. Firstly, by analysing the availability and reusability of original data and, secondly, by assessing the reproducibility of the published results using these retrieved original data and trying to reconstruct the original analysis scheme. Several findings have emerged from this process, such as some difficulties in retrieving the original data and some problems with the reproducibility of the meta-analyses examined.

Regarding original data availability –even taking availability in a broad sense (i.e. retrieving data from tables and figures when no data file was available) – for about a third of the included meta-analyses no available data was found.  In these cases, attempts were made to obtain the data on request to the corresponding author, with little success. Data was only received back in 12% of the requests made. This result is in line with what was found in a recent study where data availability statements from a set of primary studies were analysed [@gabelica2022], although 42% of these statements reported availability on request, only 6.8% of these shared their data when requested. Furthermore, [@page2022] found that of a set of meta-analyses that included a data availability statement, 42% also reported availability on request. Stating data availability on request seems very common, however obtaining the data on request seems highly challenging. Nowadays, there are straightforward, free and open ways to share data. Several repositories (e.g., OSF, GitHub, Zenodo, Figshare) are available for researchers to host openly the data associated with published results. On-request availability has proven to be neither useful nor necessary.

For the remaining meta-analyses (about two thirds), there was some way of retrieving the data used by the original authors. However, only 5% of these shared a machine-readable data file (e.g., *csv*, *xlsx*), whereas the rest of the data was retrieved from files in document format (e.g., *docx*, *pdf*). This forces manual recoding of the data for reuse, an inefficient task –adding avoidable workload–, as well as an error-prone one –adding a new source of error. In awareness of these problems, partial double coding was carried out and data extraction from meta-analyses with discrepancies was rechecked. This added to workload and as expected, even taking these precautions did not avoid some coding errors being detected at a later stage. Furthermore, sometimes the data associated with a particular meta-analytic result was available in a forest plot, associating a particular dataset with a particular meta-analytic result. However, on other occasions, the data presented, either in the paper itself or in a supplementary file, were in general tables, that is, tables with all the primary studies, which could be part of different independent meta-analyses reported in the same paper. This kind of tables are a good overview of the characteristics of the primary studies included, but also a problematic way to make data available. On the one hand, the retrieval process can be difficult, as it involves matching subsets of these primary data with different concrete meta-analytic results, which is not always clearly indicated; on the other hand, these tables are often generated manually in document file formats (e.g. Word), adding another source of error, as we saw in one of the cases included in this paper, where the original authors themselves detected an erroneous data point in such a table shared in a supplementary file. Nevertheless, even in very recent meta-analyses, presenting data in this way is considered a form of data availability [@page2022]. As mentioned above, there are now many simple alternatives for sharing data files and guidelines on how to do it properly [@wilkinson2016].

Moreover, the availability of the original analysis code script was very limited. Only in five meta-analyses (3%), all from the same paper, the original script code was openly available. In most cases, the original analyses were reconstructed from the description provided in the paper itself, not always rich in detail, so that many of these details had to be inferred from the default settings of the software used. The availability of analysis scripts often shows similar rates, both in meta-analyses [@page2022; @polanin2020] and in primary research [@hardwicke2020; @hardwicke2022]. This makes it more difficult to easily check the reproducibility of the results from such studies. Reconstructing the analytical scheme adds to the workload, with the potential to introduce errors, both in the original report and in the reconstruction, and deals with the eventual lack of relevant analytical information.

Despite these difficulties, by recovering the original data and reconstructing the original analysis scheme, the analytical reproducibility of the results was assessed in 146 meta-analyses. These attempts at analytical reproduction went through several stages as explained above, trying to minimize the impact of possible coding errors, and requesting clarifications from the original authors. Nevertheless, even with these efforts, some discrepancies remained in the results. In some of these cases, different issues related to these discrepancies were identified. For instance, in some cases internal discrepancies were found in the paper itself, text-figure discrepancies, text-abstract, or text-table discrepancies. Furthermore, some problems were found with the lack of some primary data, that is, data available in supplementary material that included fewer cases than those finally reported in the results of the published paper as included. These situations could be explained by typos in the manuscript, or unstated meta-analysis updates that produce different versions of the manuscript, data or supplementary material leading to different results. While it is important to note that discrepancies in the summary effect results and their confidence intervals were mostly minor, with little or no impact on the conclusions, these situations are easily avoidable. For instance, sharing the data in its native format, rather than a manually generated table in a supplementary document, would avoid transcription errors or lack of listing of some of the primary studies included in the meta-analysis, as was found in some of the cases. It would also reduce the workload –and error– for the authors themselves and for a reviewer or other researcher interested in assessing the reproducibility of the results, reusing the data or updating the meta-analysis. On the other hand, some of the problems identified could be explained by typos. Currently, there are tools that facilitate the production of so-called reproducible manuscripts, such as the R packages *kintr* [@xie2022] and *rmarkdown* [@allaire2022]. A reproducible manuscript embeds analysis code, data and results reporting in a single document, extracting and reporting the results from the output of the computational process itself, avoiding error-prone manual transcriptions.

Our results are complementary to those observed in previous research on the reproducibility of the primary effects of meta-analyses [@gotzsche2007; @maassen2020] and related problems due to the multiplicity of primary effects [@tendal2009]. These studies found problems in reproducing the primary effects of published meta-analyses, or in reaching agreement between independent coders in computing them. Such problems, to a greater or lesser extent, had some impact on the meta-analytic results. Our results show that, even when using the primary effects as originally coded, certain problems of reproducibility of the results may arise. Some of these problems are added error on the source of error found in previous research on reproducibility of primary effects, which in turn are added error on the sources of error types of primary estimates (e.g., measurement error, sampling error, or reporting errors). No scientific research is totally error-free, but one of the main tasks of scientists is to minimize this error, and in some cases, such as those observed in this study, minimizing some potential sources of error can be straightforward.

This study has some limitations. First, the time span covered is fairly wide. Thus, the findings may not capture the changes that have arisen in recent years. Therefore, additional research is needed to examine more specific changes over years. Second, most of the primary data was retrieved through manual re-coding, introducing some error, such data was rounded data, not precise values, and in many cases the standard error had to be approximated from the confidence limits., such points are both a limitation of our study and a feature of its results: meta-analytic data as they are often shared can lead to problems with the reproducibility of the results. This point leads to another limitation on what margin of discrepancy should be set as acceptable, given the non-precise nature of most of the data retrieved. In this study, a margin of 5% was set as acceptable. Although, being aware of the arbitrariness of this criteria, more emphasis was placed on trying to identify possible issues in the results that fell above this margin, than on establishing a ratio of non-reproduced meta-analyses.

In conclusion, being able to reproduce the meta-analyses included in this study showed several difficulties. Mainly two aspects can be highlighted: data availability and reusability of the data as they are shared, and apparent errors in the reporting of results in some cases. There are many reasons why this is especially hard to justify when it comes to meta-analyses. Firstly, one of the main difficulties had to do with the retrieval of the original data. The data collected for a meta-analysis can be especially useful for future research, these data represent collections of available evidence on a particular topic, direct and open access to such datasets allows for easy updates, re-analyses and, of course, quick reproducibility assessments. Secondly, meta-analytic data generally do not contain sensible or personal information, they represent summary data from specific samples. Sharing meta-analytical data openly does not involve ethical or legal conflicts. Third, meta-analytic results often represent the state of the art of the evidence on a particular topic. These results guide applied practice, public policy, or future research directions. This prominent status entails a major responsibility for the credibility, reliability, and validity of published meta-analytic results.

# References

### 2022-09-05 analysis/00_functions.R

@@ -1,0 +1,297 @@
+pacman::p_load(tidyverse, metafor)
+
+#####Functions for plotting#####
+
+#Inputs:
+#
+# d: data prepared for plotting, data subsetted by factor, each row representing a level of the factor, and perc represent de proportion
+#
+# pal: desired colour palette in the plot
+#
+# title: desired plot title
+#
+# legend: desired plot legend
+#
+# width: desired bar width
+#
+
+customized_barplot<- function(d, pal, title, legend, width=0.35){
+  
+  plt <- ggplot(data=d, aes(x=NA, y=perc, fill=Item)) +
+    geom_bar(colour = 'black', stat="identity", width = width) +
+    scale_x_discrete(breaks = NULL) +
+    scale_fill_manual(values=pal,
+                      guide = guide_legend(reverse=T)) +
+    scale_y_continuous(labels=scales::percent) +
+    theme_minimal(base_size = 10) +
+    theme(legend.position='bottom', 
+          legend.direction='horizontal',
+          legend.text = element_text(size = 13),
+          legend.key.size = unit(.25,"cm"),
+          axis.title.y=element_blank(),
+          axis.text.y=element_blank(),
+          axis.ticks.y=element_blank(),
+          axis.title.x=element_blank(),
+          plot.title = element_text(size = 15, face = "bold")) +
+    geom_text(aes(label=sprintf ("%i%%", round(perc*100, 0))), 
+              size = 4, 
+              position = position_stack(vjust = 0.5),
+              fontface = "bold") +
+    labs(fill=legend) +
+    ggtitle(sprintf("      %s", title)) +
+    coord_flip(clip = 'off') +
+    geom_text(
+      x = 0.5,
+      y = sum(d$perc),
+      inherit.aes = FALSE,
+      label = sprintf("N = %i", sum(d$n)),
+      check_overlap = TRUE,
+      hjust = 1,
+      fontface = 'bold',
+      size = 3.5
+    )
+  return(plt)
+}
+
+#Inputs:
+#
+# d: data prepared for plotting
+#
+# x: x-axis variable
+#
+# y: y-axis variable
+#
+# shape: shape variable
+#
+# shape_name: name of the shape variable
+#
+# shape_labels: levels of the shape variable
+#
+# size: size of the shape
+#
[…]

### 2022-09-05 analysis/01_importing_data_and_descriptives.R

@@ -1,0 +1,322 @@
+if(!require(pacman)){
+  install.packages("pacman")
+}
+library(pacman)
+
+pacman::p_load(readxl, tidyverse, papaja, kableExtra, english, knitr, here, DescTools, wesanderson, ggpubr)
+
+source(here::here("analysis", "00_functions.R"))
+
+####Importing original results and methods####
+
+#This dataset contains the summary results, characteristics,  and original reported methodology of each included meta-analysis
+
+df_mas<- read_xlsx(here::here("data", 
+                              "mas_original_results.xlsx"),
+                   col_names = TRUE)
+
+
+####Descriptives####
+
+n_mas_total<- nrow(df_mas)
+k_mean<- round(mean(df_mas$k),3)
+k_median<- median(df_mas$k)
+k_sd<- round(sd(df_mas$k), 3)
+range<- c(min(df_mas$k), max(df_mas$k))
+k_iqr<- IQR(df_mas$k)
+k_q1<-quantile(df_mas$k)[2]
+k_q3<-quantile(df_mas$k)[4]
+n_mas_less_10<- df_mas %>% filter(k < 10) %>% 
+  nrow(.)
+
+
+#Process reproducibility
+
+df_process_rep<- df_mas %>% 
+  select(order, ID, orign_data) %>% 
+  mutate(Item = ifelse(orign_data!="not_available", "Yes", "No")) %>% 
+  group_by(Item) %>% 
+  tally() %>% 
+  cbind(rbind(BinomCI(.$n[1], .$n[1]+.$n[2], conf.level = 0.95, method = "wilson"),
+              BinomCI(.$n[2], .$n[1]+.$n[2], conf.level = 0.95, method = "wilson")))%>%
+  rename(perc=est)%>%
+  mutate_if(is.numeric, round, 2)
+
+
+#Source of primary data
+
+df_source_primary_data<- df_mas %>% 
+  select(order, ID, Item=orign_data) %>% 
+  filter(Item!="not_available") %>% 
+  mutate(Item=ifelse(str_detect(Item, "xls"), "Machine-readable data file", Item)) %>% 
+  group_by(Item) %>% 
+  tally() %>%   
+  cbind(MultinomCI(.$n, conf.level = 0.95, method = "sisonglaz"))%>%
+  rename(perc=est)%>%
+  mutate_if(is.numeric, round, 2) %>% 
+  mutate(Item=fct_recode(Item, "Upon request"="from_request", "Forest plot from paper itself"="paper_forest", 
[…]

### 2022-09-05 analysis/02_first_stage.R

@@ -1,0 +1,332 @@
+####Importing data####
+
+load(file = "data/first_stage/data.Rdata")
+
+####Imputation of non-available analytic details through the software used.####
+
+df_mas<- df_mas %>% 
+  filter(orign_data!="not_available") %>% 
+  mutate(tau2_estimator=replace(tau2_estimator, 
+                                Model== "random-effects" &
+                                  tau2_estimator=="not_available" &           #REML metafor's default tau2 estimator
+                                  software=="R (metafor)", 
+                                "REML")) %>% 
+  mutate(tau2_estimator=replace(tau2_estimator, 
+                                Model=="random-effects" &
+                                  tau2_estimator=="not_available" &
+                                  software=="HLM6 statistical software", 
+                                "ML")) %>%                                      #I could not find the default tau2 estimator of HLM6, but https://doi.org/10.1002/jrsm.1164
+  #mentions ML and REML as the only available options. 
+  mutate(tau2_estimator=replace(tau2_estimator,
+                                Model== "random-effects" &
+                                  tau2_estimator=="not_available" &             #All others use DL by default.
+                                  (software!= "R (metafor)" | software !="HLM6 statistical software"), 
+                                "DL")) %>%
+  mutate(weight_factor=replace(weight_factor, 
+                               weight_factor=="not_available", 
+                               "inverse_variance")) %>% 
+  mutate(AC=UL_CI-LL_CI) 
+
+
[…]

### 2022-09-05 analysis/03_second_stage.R

@@ -1,0 +1,262 @@
+#####Loading data####
+
+pacman::p_load(openxlsx, grid)
+source(here::here("analysis", "00_functions.R"))
+
+df_mas_revised2<-read_xlsx(here::here("data", "second_stage", "df_to_rev_coder2.xlsx"),
+                           col_names = TRUE)
+
+df_mas_revised3<-read_xlsx(here::here("data", "second_stage", "df_to_rev_coder3.xlsx"),
+                           col_names = TRUE)
+
+df_mas_revised4<-read_xlsx(here::here("data", "second_stage", "df_to_rev_coder4.xlsx"),
+                           col_names = TRUE)
+
+df_mas_revised5<-read_xlsx(here::here("data", "second_stage", "df_to_rev_coder5.xlsx"),
+                           col_names = TRUE)
+
+df_mas_revised<- rbind(df_mas_revised2, df_mas_revised3, df_mas_revised4, df_mas_revised5) %>% 
+  arrange(order)
+
+
+df_to_reanalyse<- df_mas_revised %>% filter(qualitative_check=="re-analyse")
+
+#Number of meta-analyses to be reproduced in each paper. 
+
+df_nmas<- df_to_reanalyse %>% 
+  select(ID, order, type_of_data) %>% 
+  group_by(order, ID, type_of_data) %>%
+  tally()
+
+
+####Importing primary data####
+
+
+#Importing the coded primary data
+
+dat_to_rev<- list()
+
+t<-0
+
+for (j in c(df_nmas$order)) {
+  
+  t<- t+1  
+  
+  dat_to_rev[[t]]<-read_xlsx(here::here("data", "second_stage", paste0("BBDD_0", j, ".xlsx")), 
+                             col_names = TRUE)
+  
+  
+}
+
+#Tidying the primary data 
+
+mas_dat_to_rev<- list()
+
+
+for (l in 1:length(dat_to_rev)) {
+  
+  
+  mas_dat_to_rev[[l]]<- ind_ma(dat= dat_to_rev[[l]], type = paste0(df_nmas$type_of_data[l]), n_mas = df_nmas$n[l])
+  
+}
+
+
+
+#Removing the hierarchy of the list 
+
+mas_df_to_rev<- flatten(mas_dat_to_rev)
+
[…]

### 2022-09-05 analysis/04_third_stage.R

@@ -1,0 +1,94 @@
+####Loading data####
+
+source(here::here("analysis", "00_functions.R"))
+
+df_to_rev2<- read_xlsx(here::here("results", "second_stage", "df_to_rev2.xlsx"))
+
+df_to_rev2<- df_to_rev2 %>% 
+  mutate(clarification_request_results = ifelse(ID == "Mitchell2019" | ID == "Braun2013", "Reply", "No reply"))
+
+df_success_request<- df_to_rev2 %>% 
+  group_by(ID) %>% 
+  filter(row_number()==1) %>% 
+  group_by(clarification_request_results) %>% 
+  tally() %>%   
+  cbind(rbind(BinomCI(.$n[1], .$n[1]+.$n[2], conf.level = 0.95, method = "wilson"),
+                       BinomCI(.$n[2], .$n[1]+.$n[2], conf.level = 0.95, method = "wilson")))%>%
+  dplyr::rename(perc=est)%>%
+  mutate_if(is.numeric, round, 2)
+
+
+df_to_reanalyse<- df_to_rev2 %>% 
+  filter(clarification_request_results == "Reply")
+
+
+dat_019<- read_csv(here::here("data", "third_stage", "BBDD_019.csv")) %>% 
+  escalc(n1i=tN, n2i=cN, m1i=tMean, m2i=cMean, sd1i = tSD, sd2i = cSD, data=., measure = "SMD", append = TRUE) %>% 
+  mutate(sei=sqrt(vi)) %>% 
+  select(Study, Outcome, Measurement, yi, sei)
+
+
+dat_061<- read_xlsx(here::here("data", "third_stage", "BBDD_061.xlsx"),
+                    col_names = TRUE) %>% 
+          ind_ma(., type = "gs_ci", n_mas = 9)
+
+dat_to_rev<- list(filter(dat_019, Outcome == "SOL" & Measurement == "Actigraphy"),
+                  filter(dat_019, Outcome == "WASO" & Measurement == "Actigraphy"),
+                  filter(dat_019, Outcome == "SOL" & Measurement == "Diary"),
+                  filter(dat_019, Outcome == "SE" & Measurement == "Actigraphy"),
[…]

### 2022-09-05 analysis/script_075.R

@@ -1,0 +1,276 @@
+## ============================================================
+## This file contains R code for reproducing the analyses from:
+##
+## Woll, C.F.J. & Schönbrodt, F.D. (2018). A Series of Meta-Analytic Tests of the Efficacy of Long-Term Psychoanalytic Psychotherapy.
+##
+## This script file is licensed under a CC-BY 4.0 license. 
+## For a human-readable summary of that license, 
+## see http://creativecommons.org/licenses/by/4.0/
+##
+## (c) 2018 Christian Woll (Christian.Woll@psy.lmu.de). Last update: 2018-03-03
+## ============================================================
+
+## ============================================================
+## This file computes pre-post-controlled Hedges' g for our main outcome (post data based on means and standard deviations AND other metrics!), 
+## runs tests for publication bias and conducts sensitivity analyses.
+## THIS IS THE CENTRAL SCRIPT FOR THE MAIN RESULTS REPORTED IN THE PAPER
+## ============================================================
+
+# (1) install packages if necessary
+# install.packages("metafor") 
+# install.packages("Matrix")
+# install.packages("compute.es")
+# install.packages("openxlsx")
+# install.packages("plyr")
+# install.packages("foreign")
+# install.packages("lme4")
+# install.packages("lmerTest")
+
+# install.packages("weightr")
+# install.packages("devtools")
+# devtools::install_github("RobbievanAert/puniform")
+
+# load packages:
+#library(puniform)
+#library(weightr)
+#library(Matrix)
+#library(metafor)
+#library(compute.es)
+#library(openxlsx)
+#library(stats)
+#library(plyr)
+#library(foreign)
+#library(lme4)
+#library(lmerTest)
+
+pacman::p_load(metafor, openxlsx, plyr)
+
+sum_standard_g <- read.xlsx(here::here("data", "primary_data", 
+                              "dat_075.xlsx"), sheet = 2)
+sum_standard_g
+# now the sum_standard_g variable represents the mixed excel chart (ppc Hedges' g plus yi and vi from special cases and plus 
+# standard g for missing ppc g cases)
+
+
+
+
+# example for referencing: bsp4 [(bsp4$Geschlecht=="weiblich") & (bsp4$Einkommen>1500) ,]
+# divide data set in pre_post and pre_follow_up data:
+
+# standard Hedges' g:
[…]

### 2022-09-05 analysis/02_first_stage.R
Minor change

@@ -1,6 +1,6 @@
 ####Importing data####
 
-load(file = "data/first_stage/data.Rdata")
+load(file = here::here("data", "first_stage", "data.Rdata"))
 
 ####Imputation of non-available analytic details through the software used.####
 

### 2022-09-05 analysis/01_importing_data_and_descriptives.R
Minor change

@@ -1,5 +1,5 @@
 if(!require(pacman)){
-  install.packages("pacman")
+  install.packages("pacman", repos = "https://cran.rstudio.com/")
 }
 library(pacman)
 

### 2022-09-05 manuscript.Rmd
Adding data

@@
    affiliation: "1"
+ - name: "Alejandro Sandoval-Lentisco"
+   affiliation: "1"
  - name: "Maria Rubio-Aparicio"
@@
  - name: "Desirée Blázquez-Rincón"
-   affiliation: "1"
- - name: "Alejandro Sandoval-Lentisco"
    affiliation: "1"

### 2022-11-17 manuscript.Rmd
Changues for the lastest version

@@
 ---
-title: "Analytical reproducibility of published meta-analyses on clinical psychological
+title: "Analytical reproducibility and data reusability of published meta-analyses on clinical psychological
   interventions"
@@
    affiliation: "1"
+ - name: "Maria Rubio-Aparicio"
+   affiliation: "3"
  - name: "Alejandro Sandoval-Lentisco"
    affiliation: "1"
- - name: "Maria Rubio-Aparicio"
-   affiliation: "3"
  - name: "Carmen López-Ibáñez"
@@
 abstract: |
-  Nowadays, meta-analysis is one of the most useful and powerful research approaches, however, this relevance relies on its credibility.
+  Meta-analysis is one of the most useful and powerful research approaches, however, this relevance relies on its credibility.
 In recent years different concerns on credibility of psychological research have emerged.
 Analytical reproducibility of scientific results could be considered as the minimal threshold of it.
-In this study, our purpose was to assess the analytical reproducibility of a set of meta-analyses, as well as the reusability of the data as it was available.
-From a random sample of papers containing at least one meta-analysis on effectiveness of interventions in psychology used in a previous study, 217 meta-analyses were selected.
+In this study, our purpose was to assess the analytical reproducibility and data reusability of a set of published meta-analyses.
+From a random sample of 100 papers containing at least one meta-analysis on effectiveness of interventions in psychology used in a previous study, 217 meta-analyses were selected.
 We first tried to retrieve the original data by recovering a data file, recoding the data from document files (pdf, doc) or on request.
@@
 In the remaining 27, different issues were identified in an in-depth review of the papers, such as: reporting inconsistencies, lack of some data or transcription errors.
-Current practices of data sharing in meta-analyses hamper the reusability of the meta-analyses.
+Current practices of data sharing in meta-analyses hamper the reusability of meta-analytic data.
 On the other hand, the implementation of new tools would help to avoid certain errors in the meta-analysis reporting process.
@@
 csl               : "apa.csl"
+nocite            : |
+                    @koffel016, @maggio2011, @nguyen2022, @page2018, @page2016, @tendal2011, @wayant2019
 
@@
 
-Nowadays, meta-analysis is widely considered as one of the most useful and powerful research approaches.
-Given the ongoing growth in the number of scientific publications [@bornmann2021], evidence synthesis approaches -such as meta-analysis- are becoming increasingly relevant.
-This relevance rests on their credibility, which can be threatened by a lack of rigorous application or poor-quality reporting [@gurevitch2018].
-Therefore, given their importance and their role as a useful guide to evidence-based practice, these threats to their credibility need to be closely monitored.
-In recent years different concerns on credibility -based on reproducibility and replicability issues- of psychological research -and of other scientific disciplines- have emerged.
-Several projects have systematically attempted to assess the replicability and reproducibility of different scientific published results (e.g., [@camerer2018; @errington2021a; @klein2014a; @opensciencecollaboration2015].
-Those initiatives showed many failures to replicate the published results.
+Meta-analysis is widely considered as an important approach to evaluate a body of work.
+Given the ongoing growth in the number of scientific publications [@bornmann2021], evidence synthesis approaches -such as meta-analysis- are becoming increasingly relevant for a cumulative science.
+This relevance rests on the credibility of meta-analytic results, which can be threatened by a lack of rigorous application or poor-quality reporting [@gurevitch2018].
+Given the importance of meta-analyses for evidence-based practice, these threats to their credibility need to be closely monitored.
+In recent years different concerns on credibility of  empirical claims have emerged.
+Several projects have systematically attempted to assess the replicability and reproducibility of published scientific results (e.g., @artner2020; @errington2021a; @opensciencecollaboration2015).
+Those initiatives showed many failures to replicate or reproduce the published results.
 In this context, the empirical assessment of scientific published results credibility has become a major task for the scientific community.
 
-There are different approaches to the empirical assessment of scientific credibility or confidence.
+There are different approaches to the empirical assessment of scientific credibility.
 Reproducibility refers to the attempt to obtain the same results as in the original publication, using the same data and the same analytical procedure.
@@
 In other words, obtaining the same results, using different data and answering the same question [@nationalacademiesofsciencesengineeringandmedicine2019; @nosek2022].
-In this project we focus on the reproducibility of meta-analyses.
+In this project, we focus on the reproducibility of meta-analyses.
 
 The reproducibility of all published scientific results could be considered as the minimal threshold of scientific credibility [@hardwicke2021].
-Different approaches can be adopted for the empirical assessment of reproducibility, for instance @nosek2022 make the distinction between process reproducibility and outcome reproducibility.
-Following this framework, a process reproducibility assessment could be carried out reviewing the availability of the materials, data, and precise details of the analytical strategy in the report or in an analysis script file required to proceed with the reproduction attempt.
-On the other hand, an outcome reproducibility assessment would be carried out when the required elements are retrievable, and the reproduction attempt proceeds.
-It is worth noting that, depending on how the analytical details are available, the challenges, implications and workload of these outcome reproducibility checks are different.
-The availability of the original analysis script code (i.e., the original computational instructions in a programming language) facilitates reproducibility analysis by simply re-running it, although this is seldom available [@hardwicke2020; @hardwicke2022; @lopez-nicolas2021].
-When only a summary is available in the research reports (which is the most common scenario in practice), a task of reconstruction of the original analysis scheme is required.
+Different approaches can be adopted for the empirical assessment of reproducibility.
+For example @nosek2022 make the distinction between process reproducibility and outcome reproducibility.
+Following this framework, a process reproducibility assessment could be carried out by reviewing the availability of the materials, data, and precise details of the analytical strategy in the report that are required to proceed with the reproduction attempt.
+An outcome reproducibility assessment can be carried out when the required elements are retrievable by actually reproducing the analyses.
+It is worth noting that the difficulty of performing an outcome reproducibility assessment depends on which analytical information is available.
+The availability of the original analysis code (i.e., the original computational instructions in a programming language) facilitates reproducibility analysis by enabling simply re-running the code on the data.
+Regrettably, the analysis code is currently seldom available [@hardwicke2020; @hardwicke2022; @lopez-nicolas2021].
+When only a verbal summary of the performed analyses is available in the research report (which is the most common scenario in practice), the original analysis needs to be reconstructed.
 The challenges and implications of failed reproductions in both cases may be of a different nature.
 
-In the meta-analytic arena, some reproducibility attempts have been carried out in recent years.
-For instance, some process reproducibility assessments have shown an important lack of data availability in machine-readable formats, and an almost complete absence of analysis script code availability [@lopez-nicolas2021; @polanin2020].
+Several reproducibility analyses of meta-analyses have been performed in recent years.
+For example, some process reproducibility assessments have shown an important lack of data availability in machine-readable formats, and an almost complete absence of analysis script code availability [@lopez-nicolas2021; @polanin2020].
 Furthermore, some outcome reproducibility assessments have shown a considerable number of failures when trying to reproduce the primary effect sizes of some published meta-analyses by recollecting primary data from primary studies [@gotzsche2007; @maassen2020; @tendal2009] possibly due to lack of details on how primary effect sizes were selected and computed.
 In these outcome reproducibility studies, the main task entails reconstructing the original data by retrieving them from the source, namely the included primary studies.
-Thus, their assessment focus is on this stage of the analysis pipeline of a meta-analysis, which usually involves decisions on how to deal with the multiplicity of effects in the primary studies and the computation process of standardized effect sizes.
+Thus, their assessment focus is on this stage of the analysis pipeline of a meta-analysis, which usually involves decisions on how to select the primary outcomes and how to deal with possible dependency, and the computation of (standardized) effect sizes.
+Figure 1 displays a summary of the basic meta-analysis pipeline through a flowchart, outlining the different stages and listing previous work that has explored different facets of reproducibility of these as well as the required elements to be able to reproduce each stage.
 
-Usually, reproducibility studies use the original data available from the original authors (e.g., [@artner2020; @hardwicke2021; @hardwicke2018].
-This puts the focus of the assessment at a different stage of the research pipeline: reusability of the available data, challenges for the reconstruction of the original analysis scheme, reporting errors, etc.
-Therefore, in order to carry out a reproducibility analysis in this way, the original data must be available.
+\begin{figure*}
+\begin{center}
+\includegraphics[width=\textwidth, height=\textheight]{results/Figure 1.png}
+
+\caption{Flowchart displaying the basic pipeline of a meta-analysis.
+Each of the stages may be subject to reproducibility evaluation.
+On the left, known studies that have evaluated some facet of the reproducibility of each stage are listed.
+On the right, the various elements that must be available to reproduce each stage are enumerated.
+}
+
+\label{fig:figs1}
+\end{center}
+\end{figure*}
+
+Reproducibility analysis typically uses the original data available from the original authors (e.g., [@artner2020; @hardwicke2021; @hardwicke2018].
+This puts the focus of the assessment at factors such as the reusability of the available data, challenges for the reconstruction of the original analysis scheme, reporting errors, etc.
 Although data availability seems to have improved in the last years [@hardwicke2018; @tedersoo2021; @wallach2018], systematic reviews and meta-analyses appear to be a special case.
-Typically, the data collected for a meta-analysis is study-level summary data extracted from published primary studies and is commonly reported in the paper itself through tables or forest plots.
+Typically, the data collected for a meta-analysis is study-level summary data extracted from published primary studies which is commonly reported in the paper through tables or forest plots.
 This may lead to the idea that common data sharing practices do not apply to meta-analysis.
-For instance, @page2022 analysed the content of data availability statements from a set of meta-analyses published in 2020.
-Only 31% included a data availability statement and only 13% of these included a link to access the data openly, with 23% stating that all relevant data are available in the paper itself, 10% stating that data sharing is no applicable as no datasets were generated, 8% stating that data sharing is no applicable as the data is drawn from already published literature, and 42% stating that data were available upon request.
-It is surprising that, even just considering meta-analyses that included a data availability statement, some of them assume that such practices do not apply to meta-analyses or that the data in the article itself is sufficient.
+For example, @page2022 analysed the content of data availability statements from a set of meta-analyses published in 2020.
+Only 31% included a data availability statement and only 13% of these included a link to access the data openly, with 23% stating that all relevant data are available in the paper itself, 10% stating that data sharing is not applicable as no datasets were generated, 8% stating that data sharing is not applicable as the data is drawn from already published literature, and 42% stating that data were available upon request.
+It is surprising that, even just considering meta-analyses that included a data availability statement, the authors of these meta-analysis  assume that such practices do not apply to meta-analyses or that the data in the article itself is sufficient.
 
@@
 In this study our purpose is twofold.
-First, we broadened previous process reproducibility assessments by considering the possible availability of the data upon request to the original authors and by assessing the reusability of the meta-analytic data in the different formats in which they are usually available.
+First, we broadened previous process reproducibility assessments by considering data availability on request and by contacting original authors to request required information to reproduce the meta-analysis.
 Second, we verified the outcome reproducibility of the meta-analyses that were process-reproducible using the available data.
-We attempted to explore meta-analysis outcome reproducibility at a different stage or level than previous work that is more focused on primary effect sizes reproducibility, using the primary effects sizes already coded by the original authors.
+Where previous work focussed on the reproducibility of primary effect sizes, we explored meta-analysis outcome reproducibility using the primary effects sizes already coded by the original authors.
 
@@
 # Method
-
+## Preregistration
 The pre-data analysis protocol (https://osf.io/42r3p/) was pre-registered on 19 October 2021. Any deviation from this protocol is explicitly acknowledged.
 
+## Data, materials, and online resources
+
 ## Identification and selection of articles and meta-analyses 
-In previous research we identified a pool of published meta-analytic reports on clinical psychological interventions through a systematic electronic search [@lopez-nicolas2021].
+In previous research we identified a pool of 664 meta-analytic reports on clinical psychological interventions published between 2000 and 2020 through a systematic electronic search [@lopez-nicolas2021].
 Of this pool, 100 were randomly selected using a random number generator between 1 and the total number of meta-analyses identified.
-The full search strategies and a summary of the screening process are available at: https://osf.io/z5vrn/, and the workflow of the randomly selection process is available at: https://osf.io/cp293/.
+The full search strategies and a summary of the screening process are available at: https://osf.io/z5vrn/, and the workflow of the random selection process is available at: https://osf.io/cp293/.
 From these 100 articles, each independent reported meta-analysis with at least 10 primary studies was selected.
-In case no meta-analysis reported in a paper had at least 10 studies, the meta-analysis with the highest number of primary studies was selected, even if this meta-analysis integrated less than 10 studies.
-`r Words(n_mas_less_10)` of the articles included in this report were in this situation.
-Therefore, our unit of analysis was each independent meta-analysis selected under these criteria.
+In case no meta-analysis reported in a paper had at least 10 studies, the meta-analysis with the highest number of primary studies was selected, which was the case for `r n_mas_less_10` of the articles included in this report.
+Our unit of analysis was each independent meta-analysis selected under these criteria.
 A total of `r n_mas_total` independent meta-analyses were selected.
@@
 The availability of necessary primary data was checked.
-First, we looked for machine-readable data files through links leading to third-party repositories or in supplementary material hosted by the journal.
-Secondly, we looked for available data through tables or forest plots in document format in the meta-analytic report itself or supplementary material.
+First, we searched for machine-readable data files through links leading to third-party repositories or in supplementary material hosted by the journal.
+Second, we looked for available data through tables or forest plots in the meta-analytic report itself, or in supplementary material.
 In these cases, the primary data had to be manually re-coded to reuse it.
-On the other hand, if the primary data of a meta-analysis were not directly available, neither in a data file nor in a document file, we attempted to obtain the data through request to the corresponding author identified in the associated paper.
-We sent an initial request in June 2021 and a subsequent reminder in October 2021 if no reply was received.
+Finally, if the primary data of a meta-analysis were not directly available after the previous steps, we attempted to obtain the data through a request to the corresponding author identified in the associated paper.
+We sent an initial request in June 2021 and, if there was no reply, a subsequent reminder in October 2021.
 This reminder was sent to a more recent alternative email address if we were able to find one.
 If we were unable to obtain the data through the email request, the associated meta-analysis was labelled as not process reproducible.
-In order to be able to reproduce meta-analyses, mainly primary effects and their associated standard errors are required.
+In order to be able to reproduce meta-analyses, primary effects and their associated standard errors are required.
 These are generally computed from primary statistics retrieved from the primary studies such as means, standard deviations or sample sizes.
-In this sense, we tried to retrieve the least processed data possible.
-First, we sought for the primary statistics, recovered in `r sprintf("%0.0f%%", df_type_of_data$perc[3] * 100)` of the cases; second, we sought for the primary effects and their standard errors (or, alternatively, the sampling variances), recovered in `r sprintf("%0.0f%%", df_type_of_data$perc[2] * 100)` of the cases; finally, we sought for the primary effects and their confidential limits, recovered in `r sprintf("%0.0f%%", df_type_of_data$perc[1] * 100)` of the cases, from which the standard errors were approximated as follows:
+We attempted to retrieve the least processed data possible.
+First, we sought for the primary statistics, recovered in `r sprintf("%0.0f%%", df_type_of_data$perc[3] * 100)` of the cases.
+Second, we sought for the primary effects and their standard errors (or, alternatively, the sampling variances), recovered in `r sprintf("%0.0f%%", df_type_of_data$perc[2] * 100)` of the cases.
+Finally, we sought for the primary effects and their confidential limits, recovered in `r sprintf("%0.0f%%", df_type_of_data$perc[1] * 100)` of the cases, from which the standard errors were approximated as follows:
 
@@
 
-with $se_i$ being the standard error of the ith effect size, $UB_i$ and $LB_i$ the upper and lower confidence limits of confidence interval for the ith effect size, and $z_{\alpha/2}$ the $1 - z_{\alpha/2}$ quantile of the standard normal distribution (usually, $z_{\alpha/2} = 1.96$ assuming a 95% confidence interval).
+with $se_i$ being the standard error of the ith effect size, $UB_i$ and $LB_i$ the upper and lower confidence limits of confidence interval for the ith effect size, and $z_{\alpha/2}$ the $1 - z_{\alpha/2}$ quantile of the standard normal distribution (usually, $z_{\alpha/2} = 1.96$ assuming a two-sided 95% confidence interval).
 
@@
 When it was available, analytical reproducibility was checked by rerunning the original script on the associated primary data.
-In most cases (`r sprintf("%0.0f%%", 100-((n_mas_w_script/df_process_rep$n[2]) * 100))`), the analysis script code was not available.
-Thus, in these cases we tried to reconstruct the original analytical scheme using the technical details reported in the paper.
-Specifically, we collected information on: (a) meta-analytic model originally assumed; (b) weighting scheme; (c) between-studies variance estimator; (d) confidence interval method; and (e) software used.
+In `r df_process_rep$n[2] -  n_mas_w_script` cases (`r sprintf("%0.0f%%", 100-((n_mas_w_script/df_process_rep$n[2]) * 100))`), the analysis script code was not available.
+In these cases we tried to reconstruct the original analytical scheme using the technical details reported in the paper.
+Specifically, we collected information on: (a) the meta-analytic model originally assumed; (b) the weighting scheme; (c) the between-studies variance estimator; (d) the method used to compute the confidence interval; and (e) the software used to perform the meta-analysis.
 If any of these details about the analytical methods were not reported, but the software used was mentioned, we inferred the first four pieces of information from the default settings of the software used.
@@
 ## Data collection procedure 
-Primary-level data and aggregate-level data described above, were coded by five members of the group.
+Primary-level data and aggregate-level data described above were coded by five members of the group.
 At a first pilot stage, a random sample of five articles of the total pool was independently coded by the five members and, subsequently, in a series of meetings, disagreements between the coders were resolved by consensus.
-Next, the initial pool of 100 included articles was split among four of them, 25 each.
-A random sample of 25 articles of the total pool was assigned to the fifth member to carry out independent double-coding of these cases, with the goal to track the reliability of the data collection process.
-Disagreements were resolved by consensus and checking the original materials.
+Next, the initial pool of 100 included articles was split among four coders, 25 articles each.
+A random sample of 25 articles of the total pool was assigned to the fifth member to carry out independent double-coding, with the goal to examine the reliability of the data collection process.
+Disagreements were resolved by consensus and by double-checking the original materials.
 
 ## Reproducibility outcomes
-Each meta-analysis was labelled using the following reproducibility success scheme: (a) reproducible; (b) not process-reproducible; (c) numerical error (d) decision error.
-Not process-reproducible refers to situations when we were unable to access the primary data neither through direct extraction nor upon request.
+Each meta-analysis was labelled using the following reproducibility success scheme: (a) reproducible; (b) not process-reproducible; (c) numerical error, and (d) decision error.
+Not process-reproducible refers to situations where we were unable to access the primary data neither through direct extraction nor upon request.
 Similar to previous studies (Artner et al., 2020; Hardwicke et al., 2018, 2021) an index of numerical error was computed (see Protocol https://osf.io/tq4uf/).
-This index expressed the differences between reproduced and original values as percentages.
+This index expressed the difference between reproduced and original values as a percentage.
 To avoid labelling minor numerical discrepancies related to numerical rounding as reproducibility problems, a 5% discrepancy threshold was set.
-Thus, a meta-analysis was labelled as numerical error if showed a discrepancy larger than 5%.
-Finally, decision error refers to situations where the $p_{reported}$ falls on the opposite side of the .05 boundary in relation to the $p_{reproduced}$. 
-We mainly focused on analytical reproducibility of summary effects, their confidence bounds and the result of the null hypothesis significance test.
+Thus, a meta-analysis was labelled as 'numerical error' if it showed a discrepancy larger than 5%.^[A sensitivity analysis using other possible criteria is reported in the supplementary file.]
+Finally, the label 'decision error' refers to situations where the $p_{reported}$ fell on the opposite side of the .05 boundary in relation to the $p_{reproduced}$. 
+We focus on analytical reproducibility of summary effects, their confidence bounds and the result of the null hypothesis significance test.
 Secondarily, we also assessed analytical reproducibility of other synthesis methods such as heterogeneity statistics.
@@
 Analytical reproducibility checks were carried out at different stages.
-Firstly, through reported analytic details or script code.
+First, through reported analytic details or script code.
 When the analysis script code was available, computational reproducibility was checked by rerunning the script with the available primary data.
@@
 The scripts are available at: ….
+
 Second, given that the manual recoding process is an error-prone task, some mistakes can appear.
 Thus, those meta-analyses labelled as numerical error and/or decision error in the previous stage were re-assessed by a different member of the team.
-In cases where an error was found in the originally coded results, analytic methods and/or primary data, the meta-analyses were reproduced again and re-labelled according to the updated results.
-Third, a qualitative assessment of the meta-analyses still labelled as numerical error and/or decision error was carried out.
+In cases where an error was found in the originally coded results, analytic methods and/or primary data, the meta-analyses were once reproduced again and re-labelled according to the updated results.
+Additionally, a qualitative assessment of the meta-analyses still labelled as numerical error and/or decision error was also carried out.
 The same reviewers who checked for errors produced individual reports on the possible source of the discrepancy and its reproducibility was judged qualitatively by four of the other authors.
-This stage was a deviation from the pre-registered protocol, and made it possible to identify situations with obvious explanations, such as rounding, inverted signs, etc.
+This stage was a deviation from the pre-registered protocol, and made it possible to identify situations with obvious explanations, such as rounding issues, inverted signs, etc.
+
 Finally, for meta-analyses that remained labelled as non-reproducible, an email was sent to the corresponding author of the associated paper explaining our aims, our approach, and our results regarding his/her meta-analysis and requesting additional information that could explain the mismatch between the original reported results and the reproduced results.
@@
 These meta-analyses included `r round(k_mean, 2)` primary studies on average (`r sprintf("sd = %0.2f; median = %0.0f; interquartile range = %0.0f-%0.0f; range = %0.0f-%0.0f)", k_sd, k_median, k_q1, k_q3, range[1], range[2])`).
-Figure 1 displays the distribution of number of primary studies among the meta-analyses included in our sample.
+Figure 2 displays the distribution of number of primary studies among the meta-analyses included in our sample.
 Original results and characteristics of these meta-analyses are available at: …
@@
 ## Process reproducibility 
-Figure 2 summarizes the primary data retrieval results.
+Figure 3 summarizes the primary data retrieval results.
 Based on the availability of primary data, either retrieved directly from the paper or upon request, `r df_process_rep$n[2]` meta-analyses (`r sprintf("%0.0f%%", df_process_rep$perc[2]*100)`, see Fig.
@@
 2b for further details).
-Although attempts were made to retrieve data for `r df_process_rep$n[1]+df_source_primary_data$n[1]` meta-analyses from `r sum(df_request$n)` different papers, data was only retrieved upon request for `r df_source_primary_data$n[1]` of them, from `r df_request$n[2]` different papers (`r sprintf("%0.0f%%", df_request$perc[2]*100)`, see Fig.
+Although attempts were made to retrieve data for `r df_process_rep$n[1]+df_source_primary_data$n[1]` meta-analyses from `r sum(df_request$n)` different papers by emailing the corresponding authors, data was only retrieved for `r df_source_primary_data$n[1]` meta-analyses, from `r df_request$n[2]` different papers (`r sprintf("%0.0f%%", df_request$perc[2]*100)`, see Fig.
 2c).
-In the remaining cases, a reply providing some reasons not to share was received in about a third of the cases (`r sprintf("%0.0f%%", df_request$perc[2]*100)`, see Fig 2c), whereas no reply was received in the rest.
-Table 1 summarises the different reasons given in cases where data was not provided upon request.
+For the remaining `r df_process_rep$n[1]` from `r df_request$n[1] + df_request$n[3]` different papers, a reply providing some reasons not to share was received in `r sprintf("%0.0f%%", df_request$perc[2]*100)` (see Fig 2c), whereas no reply was received for the remainder of the meta-analyses.
+Table 1 summarises the different reasons corresponding authors given when data was not provided upon request.
 
@@
 ## Challenges faced retrieving primary data
-In most cases, when the necessary data was available, such data was in document formats, as previously reported.
+In most cases, when the meta-analytic data was available, it was shared in document formats, as previously reported.
 Data available in tables or forest plots shared in *pdf* or *docx* format –either in the document itself or in the supplementary materials– was found to be highly prevalent.
-This led to a manual recoding of the primary data to be able to reuse them.
+This required a manual recoding of the primary data to be able to reuse them.
 Furthermore, when data was reported through general tables (i.e.
-tables listing all the primary studies included with their characteristics), it was not always obvious in which meta-analysis each data entry was included, leading to the time-consuming task of matching each data entry with each independent meta-analytic result reported in the paper.
-There were only `r df_source_primary_data$n[2]` meta-analyses (from`r sum(df_data_downloaded$Item)` different papers) of the `r df_process_rep$n[2]` labelled as process reproducible (`r sprintf("%0.0f%%", df_source_primary_data$perc[2]*100)`), where the task of retrieving the data required simply downloading the data in an machine-readable data file format.
-On the other hand, as shown in Figure 2c, when the necessary data was not available, retrieving it upon request to the original authors led to a remarkably low success rate.
+tables listing all the primary studies included with their characteristics), the meta-analysis associated with each data entry was not always obvious, leading to the time-consuming task of matching each data entry with each independent meta-analytic result reported in the paper.
+There were only `r df_source_primary_data$n[2]` meta-analyses (from `r words(sum(df_data_downloaded$Item))` different papers) of the `r df_process_rep$n[2]` meta-analyses labelled as process reproducible (`r sprintf("%0.0f%%", df_source_primary_data$perc[2]*100)`), where the task of retrieving the data required simply downloading the data in an machine-readable data file format.
+On the other hand, as shown in Figure 3c, when the necessary data was not available, retrieving it upon request to the original authors led to a remarkably low reponse rate.
 
@@
 
- figure2
+ figure3
 
@@
 The outcome reproducibility was checked in `r df_process_rep$n[2]` meta-analyses from `r nrow(df_nmas_wdata)` different papers.
-In `r filter(df_script, script == 1)$n` of these meta-analyses (`r sprintf("%0.0f%%", filter(df_script, script == 1)$n/sum(df_script$n)*100)`), all from the same paper, the original script code was available.
-Therefore, in these five cases, analytical reproducibility was checked running the original script analysis on the original primary data.
-In the remaining cases, the original analytical framework was reconstructed as explained above.
+As mentioned above, in `r filter(df_script, script == 1)$n` of these meta-analyses (`r sprintf("%0.0f%%", filter(df_script, script == 1)$n/sum(df_script$n)*100)`), all from the same published article, the original script code was available.
+Therefore, in these five cases, analytical reproducibility was checked running the original analysis script on the original primary data.
+In the remaining cases, the original analytical framework was reconstructed as explained in the method section.
 ```{r first_stage, include=FALSE}
@@
 ```
-Following the first stage of re-analysis, `r nrow(df_to_rev)` meta-analyses were re-assessed because they were labelled as numerical error and/or decision error following the re-analysis scheme explained above.
+Following the first stage of re-analysis, `r nrow(df_to_rev)` meta-analyses were re-assessed because they were labelled as numerical error and/or decision error.
 ```{r second_stage, include=FALSE}
@@
 After this, `r nrow(filter(df_to_reanalyse, numerical_error != "error"))` were re-labelled as reproduced and `r nrow(filter(df_to_reanalyse, numerical_error == "error"))` still had relevant discrepancies.
-Furthermore, `r nrow(filter(df_mas_revised, qualitative_check == "rep"))` were labelled as reproduced in the qualitative check because the discrepancy was probably explained by rounding issues, inverted signs for results (reported in absolute value) and primary data, minor reporting errors, or minor adjustments in the analytical scheme.
+Furthermore, `r nrow(filter(df_mas_revised, qualitative_check == "rep"))` were labelled as reproduced in the qualitative check because the discrepancy was probably explained by rounding issues, inverted signs for results (where effect sizes were reported in absolute values) and primary data, minor reporting errors, or minor adjustments in the analytical scheme.
 In the remaining `r nrow(filter(df_mas_revised, qualitative_check == "request_information"))`, and in the `r nrow(filter(df_to_reanalyse, numerical_error == "error"))` re-analysed again without success, some issues or relevant discrepancies without apparent explanation were found.
-Figure 3 displays a scatterplot showing the consistency between the original and reproduced summary effect size and their confidence bounds of these `r nrow(df_to_scatter)` meta-analyses.
+
+Figure 4 displays a scatterplot showing the consistency between the original and reproduced summary effect size and their confidence bounds of these `r nrow(df_to_scatter)` meta-analyses. 
 Additionally, as a secondary analysis, the reproducibility of the $I^2$ heterogeneity statistic was explored.
-Figure 4 displays a scatterplot showing the consistency between the original and reproduced $I^2$ statistics.
-As shown in Figures 3 and 4, the discrepancies found in the heterogeneity statistic $I^2$ are larger than those found in the summary effects and their confidence intervals.
+Figure 5 displays a scatterplot showing the consistency between the original and reproduced $I^2$ statistics.
+As shown in Figures 4 and 5, the discrepancies found in the heterogeneity statistic $I^2$ are larger than those found in the summary effects and their confidence intervals.
 The lack of precision of the available data (rounded data) or incomplete information on aspects such as the tau-squared estimator applied seem to have a substantial impact on the reproducibility of this result.
@@
 Only the results of the 52 meta-analyses with a discrepancy of more than 5% identified in the first stage are displayed, but with the corrections made in the second stage.
-All values are in *d* scale.
 In panel (a) the summary effects are displayed and in panel (b) the confidence intervals.
 For (b) the colours represent lower or upper bound of the confidence interval."}
-figure3
+figure4
 
@@
 Only the results of the 52 meta-analyses with a discrepancy of more than 5% identified in the first stage are displayed, but with the corrections made in the second stage.
-The values displayed are $I^2$ hetorogeneity statistics."}
-figure4
+The values displayed are $I^2$ hetorogeneity statistics.
+The size of the crosses is function of the discrepancy in the summary effect."}
+figure5
 
@@
 Different issues in these `r nrow(df_to_rev2)` meta-analyses were identified in the second stage.
-For instance, in one of the meta-analyses which showed discrepancies in the confidence limits, inconsistencies were found in the original meta-analytic report itself.
+For example, for one of the meta-analyses which showed a discrepancy in the confidence limits, inconsistencies were found in the original meta-analytic report itself.
 The confidence limits originally reported for that meta-analysis were different in the abstract, main text and forest plot.
@@
 Furthermore, inconsistencies in the original summary effect reported were found between the results reported in abstract and the results reported in the main text and the forest plot.
-This kind of original results reporting inconsistencies was also found in other cases.
-In another case where primary data were available in both a table and a forest plot, minor inconsistencies were also found between the primary data of the table and the forest plot.
+This example of inconsistencies in original results was also found in other cases.
+Also, in a paper where primary data were available in both a table and a forest plot, minor inconsistencies were found between the primary data of the table and the forest plot.
 These appeared to be typos.
-Furthermore, regarding the number of primary data included, some inconsistencies were also found.
-For instance, in one of the meta-analyses, the main text reported the inclusion of 10 comparisons in the meta-analysis, whereas in a table of results 11 comparisons were reported for this meta-analysis.
-Furthermore, the results reported for this meta-analysis in the text and in the results table were different.
-Moreover, one apparently included primary study –it was cited in the text as such– did not appear in the table of main characteristics of included studies.
+Furthermore, some inconsistencies were found with respect to the number of primary studies included in each meta-analysis.
+For example, in one of the meta-analyses, the main text reported the inclusion of 10 comparisons in the meta-analysis, whereas in a table of results 11 comparisons were reported for this meta-analysis.
 On the other hand, in 11 meta-analyses the primary data retrieved from the supplementary materials were not sufficient to reach the number of primary studies stated as included in this meta-analysis in the original report.
@@
 In one of them, the original authors sent back a link to an OSF repository where the original data and analysis script were stored.
-This link was not reported in the paper by mistake according to the authors themselves.
+According to the authors, this link was not reported in the paper by mistake.
 The script was run on these data and the results were successfully reproduced.
@@
 This situation exemplifies the potential issues arising from having to reconstruct the original data from tables and figures and not having open access to the original data file.
-In the other case, the data used was retrieved from a huge table in supplementary material (*docx*) with all effect sizes and their confidence limits.
+In the other case, the original data was retrieved from a huge table in supplementary material with all effect sizes and their confidence limits.
 The original authors sent back this same table by increasing the number of decimal places of the effect sizes and after correcting some wrong values that they themselves detected in that process.
@@
 
+Figure 6 summarises the results of the whole process of outcome reproducibility assessment.
+
+\begin{figure*}
+\begin{center}
+\includegraphics[width=\textwidth]{results/Figure 6.png}
+
+\caption{Results of the different stages carried out in the evaluation of the outcome reproducibility. 
+}
+
+\label{fig:fig6}
+\end{center}
+\end{figure*}
+
 # Discussion 
-The main aim of this study was to explore the analytical reproducibility of a sample of published meta-analyses on the effectiveness of clinical psychology interventions.
-Firstly, by analysing the availability and reusability of original data and, secondly, by assessing the reproducibility of the published results using these retrieved original data and trying to reconstruct the original analysis scheme.
-Several findings have emerged from this process, such as some difficulties in retrieving the original data and some problems with the reproducibility of the meta-analyses examined.
+The main aim of this study was to examine the analytical reproducibility of a sample of published meta-analyses on the effectiveness of clinical psychology interventions.
+We analyzed the availability and reusability of original data and, assessed the reproducibility of the published results using these retrieved original data, and tried to reconstruct the original analysis plan.
+We encountered both difficulties in retrieving the original data and some problems with the reproducibility of the meta-analyses examined.
 
-Regarding original data availability –even taking availability in a broad sense (i.e.
-retrieving data from tables and figures when no data file was available) – for about a third of the included meta-analyses no available data was found.
-In these cases, attempts were made to obtain the data on request to the corresponding author, with little success.
-Data was only received back in 12% of the requests made.
-This result is in line with what was found in a recent study where data availability statements from a set of primary studies were analysed [@gabelica2022], although 42% of these statements reported availability on request, only 6.8% of these shared their data when requested.
-Furthermore, [@page2022] found that of a set of meta-analyses that included a data availability statement, 42% also reported availability on request.
-Stating data availability on request seems very common, however obtaining the data on request seems highly challenging.
-Nowadays, there are straightforward, free and open ways to share data.
-Several repositories (e.g., OSF, GitHub, Zenodo, Figshare) are available for researchers to host openly the data associated with published results.
-On-request availability has proven to be neither useful nor necessary.
+Even when we interpret data availability in the broad sense (i.e.
+retrieving data from tables and figures when no data file was available), for about a third of the included meta-analyses no data was available.
+In these cases, attempts were made to obtain the data on request to the corresponding author, with little success.Authors only shared data in 12% of the requests that were made.
+This result is in line with what was found in a recent study where data availability statements from a set of primary studies were analysed [@gabelica2022].Where 42% of primary studies in @gabelica2022 reported data was available on request (and identical percentage was found in @page2022 for meta-analyses), only 6.8% of the authors shared the underlying data when requested.
+Even though it is common to see authors state data is available on request, actually obtaining the data on request seems highly challenging.
+Although this problem of retrieving data on request is well known [@wicherts2006], the situation does not seem to have improved.
+Nowadays, there are straightforward, free, and open ways to share data, including meta-analytic data files.
+Several repositories (e.g., OSF, GitHub, Zenodo, Figshare) are available for researchers to openly share the data associated with published results.
+On-request availability has proven to be inadequate, and with the availability of data repositories is no longer necessary.
+Journals publishing meta-analyses should require that authors share the underlying data in a public data repository.
 
-For the remaining meta-analyses (about two thirds), there was some way of retrieving the data used by the original authors.
-However, only 5% of these shared a machine-readable data file (e.g., *csv*, *xlsx*), whereas the rest of the data was retrieved from files in document format (e.g., *docx*, *pdf*).
-This forces manual recoding of the data for reuse, an inefficient task –adding avoidable workload–, as well as an error-prone one –adding a new source of error.
-In awareness of these problems, partial double coding was carried out and data extraction from meta-analyses with discrepancies was rechecked.
-This added to workload and as expected, even taking these precautions did not avoid some coding errors being detected at a later stage.
-Furthermore, sometimes the data associated with a particular meta-analytic result was available in a forest plot, associating a particular dataset with a particular meta-analytic result.
-However, on other occasions, the data presented, either in the paper itself or in a supplementary file, were in general tables, that is, tables with all the primary studies, which could be part of different independent meta-analyses reported in the same paper.
-This kind of tables are a good overview of the characteristics of the primary studies included, but also a problematic way to make data available.
-On the one hand, the retrieval process can be difficult, as it involves matching subsets of these primary data with different concrete meta-analytic results, which is not always clearly indicated; on the other hand, these tables are often generated manually in document file formats (e.g.
-Word), adding another source of error, as we saw in one of the cases included in this paper, where the original authors themselves detected an erroneous data point in such a table shared in a supplementary file.
-Nevertheless, even in very recent meta-analyses, presenting data in this way is considered a form of data availability [@page2022].
-As mentioned above, there are now many simple alternatives for sharing data files and guidelines on how to do it properly [@wilkinson2016].
+For the remaining meta-analyses (about two thirds), we were able to retrieve the data used by the original authors.
+In only 5% of these cases data was shared in a machine-readable data file (e.g., *csv*, *xlsx*, ...), while the data had to be retrieved from files in document format (e.g., *docx*, *pdf*) for the rest of cases.
+This forces people who want to re-use the data to manually recode the data, which is both inefficient and error-prone task.
+Even after partial double coding was carried out, this procedure did not avoid some coding errors, which were detected by double checking meta-analyses with discrepancies.
+In out experience, the data retrieval process can be difficult when results are presented in general tables, as it involves matching subsets of these primary data with different meta-analytic results, while is not always clear which studies were used in which meta-analysis reported in a paper.
+Furthermore, because the tables in manuscript are often generated manually in document file formats (e.g.
+Word), we observed examples where this introduced another source of error.
+There are good guidelines on how to share research data properly [@wilkinson2016], and authors should share data in machine-readable formats.
 
-Moreover, the availability of the original analysis code script was very limited.
-Only in five meta-analyses (3%), all from the same paper, the original script code was openly available.
-In most cases, the original analyses were reconstructed from the description provided in the paper itself, not always rich in detail, so that many of these details had to be inferred from the default settings of the software used.
+An important finding is that the availability of the original analysis script was very limited.
+Only in five meta-analyses (3%, all from the same paper), was the original script openly available.
+In most cases, the original analyses were reconstructed from the description provided in the paper itself, which was not always rich in detail, so that many of these computational details had to be inferred from the default settings of the software authors used.
 The availability of analysis scripts often shows similar rates, both in meta-analyses [@page2022; @polanin2020] and in primary research [@hardwicke2020; @hardwicke2022].
-This makes it more difficult to easily check the reproducibility of the results from such studies.
+This makes it more difficult to easily check the computational reproducibility of the results from such studies.
 Reconstructing the analytical scheme adds to the workload, with the potential to introduce errors, both in the original report and in the reconstruction, and deals with the eventual lack of relevant analytical information.
+With the increasing availability of excellent open-source tools to perform meta-analysis (e.g., *metafor* [@viechtbauer2010] in R) and useful templates [@moreau2020], meta-analysts can use workflows that allow them to create and share analysis code for meta-analyses.
 
-Despite these difficulties, by recovering the original data and reconstructing the original analysis scheme, the analytical reproducibility of the results was assessed in 146 meta-analyses.
+Despite these difficulties, we were able to recover the original data and reconstruct the original analysis approach, for 146 meta-analyses, for which the analytical reproducibility of the results was assessed.
 These attempts at analytical reproduction went through several stages as explained above, trying to minimize the impact of possible coding errors, and requesting clarifications from the original authors.
 Nevertheless, even with these efforts, some discrepancies remained in the results.
-In some of these cases, different issues related to these discrepancies were identified.
-For instance, in some cases internal discrepancies were found in the paper itself, text-figure discrepancies, text-abstract, or text-table discrepancies.
-Furthermore, some problems were found with the lack of some primary data, that is, data available in supplementary material that included fewer cases than those finally reported in the results of the published paper as included.
-These situations could be explained by typos in the manuscript, or unstated meta-analysis updates that produce different versions of the manuscript, data or supplementary material leading to different results.
+We identified different issued that hindered our reproducibility attempts.
+For example, in some cases internal discrepancies were found in the paper itself (e.g., text-figure discrepancies, text-abstract, or text-table discrepancies).
+Furthermore, some problems were found with the lack of some primary data, where data available in the supplementary material included fewer cases than those finally reported in the results of the published paper.
+These situations could be explained by typos in the manuscript, or updates when performing the meta-analysis that produced different versions of the manuscript, data, or supplementary material.
 While it is important to note that discrepancies in the summary effect results and their confidence intervals were mostly minor, with little or no impact on the conclusions, these situations are easily avoidable.
-For instance, sharing the data in its native format, rather than a manually generated table in a supplementary document, would avoid transcription errors or lack of listing of some of the primary studies included in the meta-analysis, as was found in some of the cases.
-It would also reduce the workload –and error– for the authors themselves and for a reviewer or other researcher interested in assessing the reproducibility of the results, reusing the data or updating the meta-analysis.
-On the other hand, some of the problems identified could be explained by typos.
+Some of the problems identified could be explained by typos.
 Currently, there are tools that facilitate the production of so-called reproducible manuscripts, such as the R packages *kintr* [@xie2022] and *rmarkdown* [@allaire2022].
@@
 Such problems, to a greater or lesser extent, had some impact on the meta-analytic results.
-Our results show that, even when using the primary effects as originally coded, certain problems of reproducibility of the results may arise.
+Our results show that, even when re-using the primary effects as originally coded, certain problems of reproducibility of the results may remain.
 Some of these problems are added error on the source of error found in previous research on reproducibility of primary effects, which in turn are added error on the sources of error types of primary estimates (e.g., measurement error, sampling error, or reporting errors).
@@
 
-This study has some limitations.
+Our study has some limitations.
 First, the time span covered is fairly wide.
 Thus, the findings may not capture the changes that have arisen in recent years.
-Therefore, additional research is needed to examine more specific changes over years.
-Second, most of the primary data was retrieved through manual re-coding, introducing some error, such data was rounded data, not precise values, and in many cases the standard error had to be approximated from the confidence limits., such points are both a limitation of our study and a feature of its results: meta-analytic data as they are often shared can lead to problems with the reproducibility of the results.
-This point leads to another limitation on what margin of discrepancy should be set as acceptable, given the non-precise nature of most of the data retrieved.
-In this study, a margin of 5% was set as acceptable.
-Although, being aware of the arbitrariness of this criteria, more emphasis was placed on trying to identify possible issues in the results that fell above this margin, than on establishing a ratio of non-reproduced meta-analyses.
+Therefore, future studies should examine more specific changes over years, to evaluate whether better practices emerge that facilitate reproducibility.
+Second, most of the primary data was retrieved through manual re-coding, which introduces some error.
+The reported data was rounded, which means we did not have access to precise values, and in many cases the standard error had to be approximated from the confidence limits.
+These limitation of our study are caused by the suboptimal practices when sharing data we discussed above.
+Given the non-precise nature of most of the data retrieved, we had to make a decision about which margin of discrepancy was acceptable.
+In this study, a margin of 5% was chosen.
+Because this cut-off is arbitrary, we have tried to focus more on possible issues in the results that fell above this margin, than on establishing a exact ratio of non-reproduced meta-analyses based on this arbitrary cut-off.
 
-In conclusion, being able to reproduce the meta-analyses included in this study showed several difficulties.
-Mainly two aspects can be highlighted: data availability and reusability of the data as they are shared, and apparent errors in the reporting of results in some cases.
-There are many reasons why this is especially hard to justify when it comes to meta-analyses.
-Firstly, one of the main difficulties had to do with the retrieval of the original data.
-The data collected for a meta-analysis can be especially useful for future research, these data represent collections of available evidence on a particular topic, direct and open access to such datasets allows for easy updates, re-analyses and, of course, quick reproducibility assessments.
-Secondly, meta-analytic data generally do not contain sensible or personal information, they represent summary data from specific samples.
-Sharing meta-analytical data openly does not involve ethical or legal conflicts.
+In conclusion, we observed several difficulties when attempting to reproduce meta-analyses.
+Two aspects can be highlighted: (1) data availability and reusability of the data as they are shared, (2) and apparent errors in the reporting of results.
+As data collected for a meta-analysis can be especially useful for future research, direct and open access to such datasets allows for easy updates, and re-analyses, which are valuable in a cumulative science.
+Meta-analytic data generally do not contain sensitive or personal information, and can therefore almost always be shared openly, as doing so does not involve ethical or legal conflicts.
 Third, meta-analytic results often represent the state of the art of the evidence on a particular topic.
@@
 
+## Author Contributions
+Conceptualization: R.
+Lopez-Nicolas and J.
+Sanchez-Meca; Methodology: R.
+Lopez-Nicolas, D.
+Lakens, J.A.
+Lopez-Lopez and J.
+Sanchez-Meca; Formal Analysis: R Lopez-Nicolas; Investigation: R Lopez-Nicolas, M.
+Rubio-Aparicio, A.
+Sandoval-Lentisco, C.
+Lopez-Ibañez and D.
+Blazquez-Rincon: Data curation: R Lopez-Nicolas; Writing – Original Draft Preparation: R.
+Lopez-Nicolas; Writing – Review & Editing: D.
+Lakens, J.A.
+Lopez-Lopez, J.
+Sanchez-Meca, M.
+Rubio-Aparicio, A.
+Sandoval-Lentisco, C.
+Lopez-Ibañez, D.
+Blazquez-Rincon.
+
+## Conflict of interest
+The author(s) declare that there were no conflicts of interest with respect to the authorship or the publication of this article.
+
+## Acknowledgments 
+We thank the research group of the Meta-Research Centre of Tilburg University for providing feedback on an earlier version of this manuscript.
+We would also like to thank all the original authors of the included meta-analyses who enabled access to the data used in this project as well as the authors who provided clarifications in response to requests for clarification in step 3.
+
+## Funding 
+This research has been funded with a grant from the Spanish Ministry of Science and Innovation (Project PID2019-104080GB-I00, FEDER funds) and by the Spanish Ministry of Universities (predoctoral grant: FPU18/04805).
+
+# Supplemental Material
+
+# Prior versions
+
 # References

### 2022-11-17 manuscript.tex
Changues for the lastest version

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  ,jou, a4paper,floatsintext]{apa6}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{english}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

% Table formatting
\usepackage{longtable}
\usepackage{lscape}
% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
\usepackage{multirow}		% Table styling
\usepackage{tabularx}		% Control Column width
\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
\usepackage{threeparttablex}            % Lets threeparttable work with longtable

% Create new environments so endfloat can handle them
% \newenvironment{ltable}
%   {\begin{landscape}\centering\begin{threeparttable}}
%   {\end{threeparttable}\end{landscape}}
\newenvironment{lltable}{\begin{landscape}\centering\begin{ThreePartTable}}{\end{ThreePartTable}\end{landscape}}

% Enables adjusting longtable caption width to table width
% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}

% \setlength{\parindent}{0.5in}
% \setlength{\parskip}{0pt plus 0pt minus 0pt}

% Overwrite redefinition of paragraph and subparagraph by the default LaTeX template
% See https://github.com/crsh/papaja/issues/292
\makeatletter
\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
  {-1em}%
  {\normalfont\normalsize\bfseries\itshape\typesectitle}}

\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
  {-\z@\relax}%
  {\normalfont\normalsize\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
\makeatother

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\HyOrg@maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{meta-analysis, reproducibility, data sharing, data reusability, research synthesis}
\usepackage{dblfloatfix}

\usepackage{csquotes}
\usepackage{caption}
\captionsetup[table]{textfont={it}, labelfont={bf}, singlelinecheck=false, labelsep=newline}
\captionsetup[figure]{textfont={it}, labelfont={bf}, singlelinecheck=false, labelsep=newline}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Analytical reproducibility and data reusability of published meta-analyses on clinical psychological interventions},
  pdfauthor={Rubén López-Nicolás1, Daniel Lakens2, Jose A. López-López1, Maria Rubio-Aparicio3, Alejandro Sandoval-Lentisco1, Carmen López-Ibáñez1, Desirée Blázquez-Rincón1, \& Julio Sánchez-Meca1},
  pdflang={en-EN},
  pdfkeywords={meta-analysis, reproducibility, data sharing, data reusability, research synthesis},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{Analytical reproducibility and data reusability of published meta-analyses on clinical psychological interventions}
\author{Rubén López-Nicolás\textsuperscript{1}, Daniel Lakens\textsuperscript{2}, Jose A. López-López\textsuperscript{1}, Maria Rubio-Aparicio\textsuperscript{3}, Alejandro Sandoval-Lentisco\textsuperscript{1}, Carmen López-Ibáñez\textsuperscript{1}, Desirée Blázquez-Rincón\textsuperscript{1}, \& Julio Sánchez-Meca\textsuperscript{1}}
\date{}

\shorttitle{Meta-analyses reproducibility}

\authornote{

Correspondence concerning this article should be addressed to Rubén López-Nicolás. E-mail: \href{mailto:rlopez@um.es}{\nolinkurl{rlopez@um.es}}

}

\affiliation{\vspace{0.5cm}\textsuperscript{1} University of Murcia, Spain\\\textsuperscript{2} Eindhoven University of Technology, The Netherlands\\\textsuperscript{3} University of Alicante, Spain}

\leftheader{Lopez-Nicolas et al.}

\abstract{%
Meta-analysis is one of the most useful and powerful research approaches, however, this relevance relies on its credibility. In recent years different concerns on credibility of psychological research have emerged. Analytical reproducibility of scientific results could be considered as the minimal threshold of it. In this study, our purpose was to assess the analytical reproducibility and data reusability of a set of published meta-analyses. From a random sample of 100 papers containing at least one meta-analysis on effectiveness of interventions in psychology used in a previous study, 217 meta-analyses were selected. We first tried to retrieve the original data by recovering a data file, recoding the data from document files (pdf, doc) or on request. Second, through a multi-stage workflow, we tried to reproduce the main results of each meta-analysis using these data. The original data were retrieved for 146 meta-analyses from different sources. Of these, in a first stage 52 showed a discrepancy larger than 5\% in the main results, in 25 of them this discrepancy was solved with minor adjustments, or correction of coding errors. In the remaining 27, different issues were identified in an in-depth review of the papers, such as: reporting inconsistencies, lack of some data or transcription errors. Current practices of data sharing in meta-analyses hamper the reusability of meta-analytic data. On the other hand, the implementation of new tools would help to avoid certain errors in the meta-analysis reporting process.
}

\begin{document}
\maketitle

Meta-analysis is widely considered as an important approach to evaluate a body of work. Given the ongoing growth in the number of scientific publications (Bornmann et al., 2021), evidence synthesis approaches -such as meta-analysis- are becoming increasingly relevant for a cumulative science. This relevance rests on the credibility of meta-analytic results, which can be threatened by a lack of rigorous application or poor-quality reporting (Gurevitch et al., 2018). Given the importance of meta-analyses for evidence-based practice, these threats to their credibility need to be closely monitored.
In recent years different concerns on credibility of empirical claims have emerged. Several projects have systematically attempted to assess the replicability and reproducibility of published scientific results (e.g., Artner et al. (2020); Errington et al. (2021); Open Science Collaboration (2015)). Those initiatives showed many failures to replicate or reproduce the published results. In this context, the empirical assessment of scientific published results credibility has become a major task for the scientific community.

There are different approaches to the empirical assessment of scientific credibility. Reproducibility refers to the attempt to obtain the same results as in the original publication, using the same data and the same analytical procedure. Robustness refers to the assessment of the sensitivity of the originally published results and conclusions to variations in the original analytical strategy using the same data. Replicability is a core principle of the scientific method and refers to the fact that the same scientific evidence should be observed when independent researchers try to answer the same research question from the same approach at different moments using different data. In other words, obtaining the same results, using different data and answering the same question (National Academies of Sciences, Engineering, and Medicine, 2019; Nosek et al., 2022). In this project, we focus on the reproducibility of meta-analyses.

The reproducibility of all published scientific results could be considered as the minimal threshold of scientific credibility (Hardwicke et al., 2021). Different approaches can be adopted for the empirical assessment of reproducibility. For example Nosek et al. (2022) make the distinction between process reproducibility and outcome reproducibility. Following this framework, a process reproducibility assessment could be carried out by reviewing the availability of the materials, data, and precise details of the analytical strategy in the report that are required to proceed with the reproduction attempt. An outcome reproducibility assessment can be carried out when the required elements are retrievable by actually reproducing the analyses. It is worth noting that the difficulty of performing an outcome reproducibility assessment depends on which analytical information is available. The availability of the original analysis code (i.e., the original computational instructions in a programming language) facilitates reproducibility analysis by enabling simply re-running the code on the data. Regrettably, the analysis code is currently seldom available (Hardwicke et al., 2022, 2020; López-Nicolás et al., 2022). When only a verbal summary of the performed analyses is available in the research report (which is the most common scenario in practice), the original analysis needs to be reconstructed. The challenges and implications of failed reproductions in both cases may be of a different nature.

Several reproducibility analyses of meta-analyses have been performed in recent years. For example, some process reproducibility assessments have shown an important lack of data availability in machine-readable formats, and an almost complete absence of analysis script code availability (López-Nicolás et al., 2022; Polanin et al., 2020). Furthermore, some outcome reproducibility assessments have shown a considerable number of failures when trying to reproduce the primary effect sizes of some published meta-analyses by recollecting primary data from primary studies (Gøtzsche et al., 2007; Maassen et al., 2020; Tendal et al., 2009) possibly due to lack of details on how primary effect sizes were selected and computed. In these outcome reproducibility studies, the main task entails reconstructing the original data by retrieving them from the source, namely the included primary studies. Thus, their assessment focus is on this stage of the analysis pipeline of a meta-analysis, which usually involves decisions on how to select the primary outcomes and how to deal with possible dependency, and the computation of (standardized) effect sizes. Figure 1 displays a summary of the basic meta-analysis pipeline through a flowchart, outlining the different stages and listing previous work that has explored different facets of reproducibility of these as well as the required elements to be able to reproduce each stage.

\begin{figure*}
\begin{center}
\includegraphics[width=\textwidth, height=\textheight]{results/Figure 1.png}

\caption{Flowchart displaying the basic pipeline of a meta-analysis. Each of the stages may be subject to reproducibility evaluation. On the left, known studies that have evaluated some facet of the reproducibility of each stage are listed. On the right, the various elements that must be available to reproduce each stage are enumerated.
}

\label{fig:figs1}
\end{center}
\end{figure*}

Reproducibility analysis typically uses the original data available from the original authors (e.g., (Artner et al., 2020; Hardwicke et al., 2021, 2018). This puts the focus of the assessment at factors such as the reusability of the available data, challenges for the reconstruction of the original analysis scheme, reporting errors, etc. Although data availability seems to have improved in the last years (Hardwicke et al., 2018; Tedersoo et al., 2021; Wallach et al., 2018), systematic reviews and meta-analyses appear to be a special case. Typically, the data collected for a meta-analysis is study-level summary data extracted from published primary studies which is commonly reported in the paper through tables or forest plots. This may lead to the idea that common data sharing practices do not apply to meta-analysis. For example, Page et al. (2022) analysed the content of data availability statements from a set of meta-analyses published in 2020. Only 31\% included a data availability statement and only 13\% of these included a link to access the data openly, with 23\% stating that all relevant data are available in the paper itself, 10\% stating that data sharing is not applicable as no datasets were generated, 8\% stating that data sharing is not applicable as the data is drawn from already published literature, and 42\% stating that data were available upon request. It is surprising that, even just considering meta-analyses that included a data availability statement, the authors of these meta-analysis assume that such practices do not apply to meta-analyses or that the data in the article itself is sufficient.

\hypertarget{purpose}{%
\subsection{Purpose}\label{purpose}}

Previous research has revealed that there is room for improvement at different stages of the meta-analytic process pipeline. In this study our purpose is twofold. First, we broadened previous process reproducibility assessments by considering data availability on request and by contacting original authors to request required information to reproduce the meta-analysis. Second, we verified the outcome reproducibility of the meta-analyses that were process-reproducible using the available data. Where previous work focussed on the reproducibility of primary effect sizes, we explored meta-analysis outcome reproducibility using the primary effects sizes already coded by the original authors.

\hypertarget{method}{%
\section{Method}\label{method}}

\hypertarget{preregistration}{%
\subsection{Preregistration}\label{preregistration}}

The pre-data analysis protocol (\url{https://osf.io/42r3p/}) was pre-registered on 19 October 2021. Any deviation from this protocol is explicitly acknowledged.

\hypertarget{data-materials-and-online-resources}{%
\subsection{Data, materials, and online resources}\label{data-materials-and-online-resources}}

\hypertarget{identification-and-selection-of-articles-and-meta-analyses}{%
\subsection{Identification and selection of articles and meta-analyses}\label{identification-and-selection-of-articles-and-meta-analyses}}

In previous research we identified a pool of 664 meta-analytic reports on clinical psychological interventions published between 2000 and 2020 through a systematic electronic search (López-Nicolás et al., 2022). Of this pool, 100 were randomly selected using a random number generator between 1 and the total number of meta-analyses identified. The full search strategies and a summary of the screening process are available at: \url{https://osf.io/z5vrn/}, and the workflow of the random selection process is available at: \url{https://osf.io/cp293/}.
From these 100 articles, each independent reported meta-analysis with at least 10 primary studies was selected. In case no meta-analysis reported in a paper had at least 10 studies, the meta-analysis with the highest number of primary studies was selected, which was the case for 29 of the articles included in this report. Our unit of analysis was each independent meta-analysis selected under these criteria. A total of 217 independent meta-analyses were selected.

\hypertarget{retrieval-of-primary-data}{%
\subsection{Retrieval of primary data}\label{retrieval-of-primary-data}}

The availability of necessary primary data was checked. First, we searched for machine-readable data files through links leading to third-party repositories or in supplementary material hosted by the journal. Second, we looked for available data through tables or forest plots in the meta-analytic report itself, or in supplementary material. In these cases, the primary data had to be manually re-coded to reuse it. Finally, if the primary data of a meta-analysis were not directly available after the previous steps, we attempted to obtain the data through a request to the corresponding author identified in the associated paper. We sent an initial request in June 2021 and, if there was no reply, a subsequent reminder in October 2021. This reminder was sent to a more recent alternative email address if we were able to find one. If we were unable to obtain the data through the email request, the associated meta-analysis was labelled as not process reproducible.\\
In order to be able to reproduce meta-analyses, primary effects and their associated standard errors are required. These are generally computed from primary statistics retrieved from the primary studies such as means, standard deviations or sample sizes. We attempted to retrieve the least processed data possible. First, we sought for the primary statistics, recovered in 26\% of the cases. Second, we sought for the primary effects and their standard errors (or, alternatively, the sampling variances), recovered in 5\% of the cases. Finally, we sought for the primary effects and their confidential limits, recovered in 69\% of the cases, from which the standard errors were approximated as follows:

\[se_i = (\frac{UB_i - LB_i}{2z_{\alpha/2}})\]

with \(se_i\) being the standard error of the ith effect size, \(UB_i\) and \(LB_i\) the upper and lower confidence limits of confidence interval for the ith effect size, and \(z_{\alpha/2}\) the \(1 - z_{\alpha/2}\) quantile of the standard normal distribution (usually, \(z_{\alpha/2} = 1.96\) assuming a two-sided 95\% confidence interval).

\hypertarget{reconstructing-the-original-analytical-scheme}{%
\subsection{Reconstructing the original analytical scheme}\label{reconstructing-the-original-analytical-scheme}}

To proceed with reproducibility attempts of the meta-analyses that were labelled as process reproducible, we first looked for the availability of the original analysis script. When it was available, analytical reproducibility was checked by rerunning the original script on the associated primary data. In 141 cases (97\%), the analysis script code was not available. In these cases we tried to reconstruct the original analytical scheme using the technical details reported in the paper. Specifically, we collected information on: (a) the meta-analytic model originally assumed; (b) the weighting scheme; (c) the between-studies variance estimator; (d) the method used to compute the confidence interval; and (e) the software used to perform the meta-analysis. If any of these details about the analytical methods were not reported, but the software used was mentioned, we inferred the first four pieces of information from the default settings of the software used. If the software used was not reported, we inferred this information from the default settings of the most used software in the sample, which was \emph{Comprehensive Meta-Analysis}. Additional information about the meta-analysis was collected that is not reported in this manuscript. The full list of variables collected is available in the Protocol (\url{https://osf.io/tq4uf/}) and a Codebook describing these variables is available at: \url{https://osf.io/ym78s/}.

\hypertarget{data-collection-procedure}{%
\subsection{Data collection procedure}\label{data-collection-procedure}}

Primary-level data and aggregate-level data described above were coded by five members of the group. At a first pilot stage, a random sample of five articles of the total pool was independently coded by the five members and, subsequently, in a series of meetings, disagreements between the coders were resolved by consensus. Next, the initial pool of 100 included articles was split among four coders, 25 articles each. A random sample of 25 articles of the total pool was assigned to the fifth member to carry out independent double-coding, with the goal to examine the reliability of the data collection process. Disagreements were resolved by consensus and by double-checking the original materials.

\hypertarget{reproducibility-outcomes}{%
\subsection{Reproducibility outcomes}\label{reproducibility-outcomes}}

Each meta-analysis was labelled using the following reproducibility success scheme: (a) reproducible; (b) not process-reproducible; (c) numerical error, and (d) decision error. Not process-reproducible refers to situations where we were unable to access the primary data neither through direct extraction nor upon request. Similar to previous studies (Artner et al., 2020; Hardwicke et al., 2018, 2021) an index of numerical error was computed (see Protocol \url{https://osf.io/tq4uf/}). This index expressed the difference between reproduced and original values as a percentage. To avoid labelling minor numerical discrepancies related to numerical rounding as reproducibility problems, a 5\% discrepancy threshold was set. Thus, a meta-analysis was labelled as `numerical error' if it showed a discrepancy larger than 5\%.\footnote{A sensitivity analysis using other possible criteria is reported in the supplementary file.}
Finally, the label `decision error' refers to situations where the \(p_{reported}\) fell on the opposite side of the .05 boundary in relation to the \(p_{reproduced}\).
We focus on analytical reproducibility of summary effects, their confidence bounds and the result of the null hypothesis significance test. Secondarily, we also assessed analytical reproducibility of other synthesis methods such as heterogeneity statistics.

\hypertarget{reproducibility-checks-workflow}{%
\subsection{Reproducibility checks workflow}\label{reproducibility-checks-workflow}}

Analytical reproducibility checks were carried out at different stages. First, through reported analytic details or script code. When the analysis script code was available, computational reproducibility was checked by rerunning the script with the available primary data. In most cases, the analysis script code was not available. Thus, in these cases we coded the analytic details as explained above to fit equivalent meta-analytic models as a function of these details using the available primary data. This analysis scheme was programmed in the R environment (R Core Team, 2022) using the \emph{metafor} package (Viechtbauer, 2010). The scripts are available at: \ldots.

Second, given that the manual recoding process is an error-prone task, some mistakes can appear. Thus, those meta-analyses labelled as numerical error and/or decision error in the previous stage were re-assessed by a different member of the team. In cases where an error was found in the originally coded results, analytic methods and/or primary data, the meta-analyses were once reproduced again and re-labelled according to the updated results. Additionally, a qualitative assessment of the meta-analyses still labelled as numerical error and/or decision error was also carried out. The same reviewers who checked for errors produced individual reports on the possible source of the discrepancy and its reproducibility was judged qualitatively by four of the other authors. This stage was a deviation from the pre-registered protocol, and made it possible to identify situations with obvious explanations, such as rounding issues, inverted signs, etc.

Finally, for meta-analyses that remained labelled as non-reproducible, an email was sent to the corresponding author of the associated paper explaining our aims, our approach, and our results regarding his/her meta-analysis and requesting additional information that could explain the mismatch between the original reported results and the reproduced results. We tried to solve the reproducibility issues within a month after the request and we updated the label accordingly.

\hypertarget{results}{%
\section{Results}\label{results}}

From the 100 included papers, 217 independent meta-analyses were selected following the criteria explained above. These meta-analyses included 18.35 primary studies on average (sd = 17.25; median = 13; interquartile range = 10-19; range = 3-134)). Figure 2 displays the distribution of number of primary studies among the meta-analyses included in our sample. Original results and characteristics of these meta-analyses are available at: \ldots{}

\begin{figure}
\centering
\includegraphics{manuscript_files/figure-latex/unnamed-chunk-1-1.pdf}
\caption{\label{fig:unnamed-chunk-1}Distribution of the number of primary studies included in each of the meta-analyses. Vertical blue dotted lines represent the first quartile, median, and third quartile, respectively.}
\end{figure}

\hypertarget{process-reproducibility}{%
\subsection{Process reproducibility}\label{process-reproducibility}}

Figure 3 summarizes the primary data retrieval results. Based on the availability of primary data, either retrieved directly from the paper or upon request, 146 meta-analyses (67\%, see Fig. 2a) were labelled as process reproducible. Of these 146 meta-analyses, in about half of the cases the primary data was retrieved from a forest plot in the paper itself and in about a third of the cases the primary data was retrieved from supplementary files. Only in 3\% of the cases the primary data was retrieved upon request (see Fig. 2b for further details). Although attempts were made to retrieve data for 75 meta-analyses from 25 different papers by emailing the corresponding authors, data was only retrieved for 4 meta-analyses, from 3 different papers (12\%, see Fig. 2c). For the remaining 71 from 22 different papers, a reply providing some reasons not to share was received in 12\% (see Fig 2c), whereas no reply was received for the remainder of the meta-analyses. Table 1 summarises the different reasons corresponding authors given when data was not provided upon request.

\begin{table}

\caption{\label{tab:unnamed-chunk-2}Reasons given when data was not received upon request.}
\centering
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{7cm}cc}
\toprule
Reason & N & \%\\
\midrule
Data held by a co-author, and do not have his contact details & 1 & 12\%\\
Propietary dataset & 1 & 12\%\\
The author no longer has the data. & 5 & 62\%\\
The author requested more information and a written agreement including possible authorship. 
                                                      Additional details were sent and after some email exchanges there was no further response. & 1 & 12\%\\
\bottomrule
\end{tabular}
\end{table}

\hypertarget{challenges-faced-retrieving-primary-data}{%
\subsection{Challenges faced retrieving primary data}\label{challenges-faced-retrieving-primary-data}}

In most cases, when the meta-analytic data was available, it was shared in document formats, as previously reported. Data available in tables or forest plots shared in \emph{pdf} or \emph{docx} format --either in the document itself or in the supplementary materials-- was found to be highly prevalent. This required a manual recoding of the primary data to be able to reuse them. Furthermore, when data was reported through general tables (i.e.~tables listing all the primary studies included with their characteristics), the meta-analysis associated with each data entry was not always obvious, leading to the time-consuming task of matching each data entry with each independent meta-analytic result reported in the paper. There were only 7 meta-analyses (from three different papers) of the 146 meta-analyses labelled as process reproducible (5\%), where the task of retrieving the data required simply downloading the data in an machine-readable data file format.
On the other hand, as shown in Figure 3c, when the necessary data was not available, retrieving it upon request to the original authors led to a remarkably low reponse rate.

\begin{figure*}
\includegraphics[width=1\linewidth]{manuscript_files/figure-latex/unnamed-chunk-3-1} \caption{Percentage of (a) process-reproducible meta-analyses; (b) different types of sources of original data; and (c) data request results.}\label{fig:unnamed-chunk-3}
\end{figure*}

\hypertarget{outcome-reproducibility}{%
\subsection{Outcome reproducibility}\label{outcome-reproducibility}}

The outcome reproducibility was checked in 146 meta-analyses from 82 different papers. As mentioned above, in 5 of these meta-analyses (3\%), all from the same published article, the original script code was available. Therefore, in these five cases, analytical reproducibility was checked running the original analysis script on the original primary data. In the remaining cases, the original analytical framework was reconstructed as explained in the method section.

Following the first stage of re-analysis, 52 meta-analyses were re-assessed because they were labelled as numerical error and/or decision error.

Of these, 17 were re-analysed again as some coding errors were found in the second stage. After this, 10 were re-labelled as reproduced and 7 still had relevant discrepancies. Furthermore, 15 were labelled as reproduced in the qualitative check because the discrepancy was probably explained by rounding issues, inverted signs for results (where effect sizes were reported in absolute values) and primary data, minor reporting errors, or minor adjustments in the analytical scheme. In the remaining 20, and in the 7 re-analysed again without success, some issues or relevant discrepancies without apparent explanation were found.

Figure 4 displays a scatterplot showing the consistency between the original and reproduced summary effect size and their confidence bounds of these 52 meta-analyses.
Additionally, as a secondary analysis, the reproducibility of the \(I^2\) heterogeneity statistic was explored. Figure 5 displays a scatterplot showing the consistency between the original and reproduced \(I^2\) statistics. As shown in Figures 4 and 5, the discrepancies found in the heterogeneity statistic \(I^2\) are larger than those found in the summary effects and their confidence intervals. The lack of precision of the available data (rounded data) or incomplete information on aspects such as the tau-squared estimator applied seem to have a substantial impact on the reproducibility of this result.

\begin{figure}
\centering
\includegraphics{manuscript_files/figure-latex/unnamed-chunk-4-1.pdf}
\caption{\label{fig:unnamed-chunk-4}Scatterplot displaying the reproduced values as a function of the original values classified by whether or not decision error was found. Only the results of the 52 meta-analyses with a discrepancy of more than 5\% identified in the first stage are displayed, but with the corrections made in the second stage. In panel (a) the summary effects are displayed and in panel (b) the confidence intervals. For (b) the colours represent lower or upper bound of the confidence interval.}
\end{figure}

\begin{figure}
\centering
\includegraphics{manuscript_files/figure-latex/unnamed-chunk-5-1.pdf}
\caption{\label{fig:unnamed-chunk-5}Scatterplot displaying the reproduced values as a function of the original values classified by whether or not decision error was found. Only the results of the 52 meta-analyses with a discrepancy of more than 5\% identified in the first stage are displayed, but with the corrections made in the second stage. The values displayed are \(I^2\) hetorogeneity statistics. The size of the crosses is function of the discrepancy in the summary effect.}
\end{figure}

\hypertarget{main-issues-identified}{%
\subsection{Main issues identified}\label{main-issues-identified}}

Different issues in these 27 meta-analyses were identified in the second stage. For example, for one of the meta-analyses which showed a discrepancy in the confidence limits, inconsistencies were found in the original meta-analytic report itself. The confidence limits originally reported for that meta-analysis were different in the abstract, main text and forest plot. Matching the reproduced results were those reported in the forest plot but not those reported in the text. Furthermore, inconsistencies in the original summary effect reported were found between the results reported in abstract and the results reported in the main text and the forest plot. This example of inconsistencies in original results was also found in other cases. Also, in a paper where primary data were available in both a table and a forest plot, minor inconsistencies were found between the primary data of the table and the forest plot. These appeared to be typos.
Furthermore, some inconsistencies were found with respect to the number of primary studies included in each meta-analysis. For example, in one of the meta-analyses, the main text reported the inclusion of 10 comparisons in the meta-analysis, whereas in a table of results 11 comparisons were reported for this meta-analysis. On the other hand, in 11 meta-analyses the primary data retrieved from the supplementary materials were not sufficient to reach the number of primary studies stated as included in this meta-analysis in the original report.

\hypertarget{original-authors-clarifications}{%
\subsection{Original authors clarifications}\label{original-authors-clarifications}}

These 27 meta-analyses were from 10 different papers. Therefore, 10 clarification requests with information about the study aims, methods and preliminary results were sent to the corresponding authors of the original articles. A reply was received in only 2 of the 10 cases.
In one of them, the original authors sent back a link to an OSF repository where the original data and analysis script were stored. According to the authors, this link was not reported in the paper by mistake. The script was run on these data and the results were successfully reproduced. In this case, the data previously used were retrieved from a forest plot (means and standard deviations) and a table (sample sizes) reported in the paper. The previous discrepancy was explained by two cases included in the original meta-analysis from the same primary study that were reported with the same ID in the forest plot and were not correctly matched with their corresponding sample size extracted from the table. This situation exemplifies the potential issues arising from having to reconstruct the original data from tables and figures and not having open access to the original data file.
In the other case, the original data was retrieved from a huge table in supplementary material with all effect sizes and their confidence limits. The original authors sent back this same table by increasing the number of decimal places of the effect sizes and after correcting some wrong values that they themselves detected in that process. This fixed the discrepancies for some of the meta-analyses in this paper.

Figure 6 summarises the results of the whole process of outcome reproducibility assessment.

\begin{figure*}
\begin{center}
\includegraphics[width=\textwidth]{results/Figure 6.png}

\caption{Results of the different stages carried out in the evaluation of the outcome reproducibility. 
}

\label{fig:fig6}
\end{center}
\end{figure*}

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

The main aim of this study was to examine the analytical reproducibility of a sample of published meta-analyses on the effectiveness of clinical psychology interventions. We analyzed the availability and reusability of original data and, assessed the reproducibility of the published results using these retrieved original data, and tried to reconstruct the original analysis plan. We encountered both difficulties in retrieving the original data and some problems with the reproducibility of the meta-analyses examined.

Even when we interpret data availability in the broad sense (i.e.~retrieving data from tables and figures when no data file was available), for about a third of the included meta-analyses no data was available. In these cases, attempts were made to obtain the data on request to the corresponding author, with little success.Authors only shared data in 12\% of the requests that were made. This result is in line with what was found in a recent study where data availability statements from a set of primary studies were analysed (Gabelica et al., 2022).Where 42\% of primary studies in Gabelica et al. (2022) reported data was available on request (and identical percentage was found in Page et al. (2022) for meta-analyses), only 6.8\% of the authors shared the underlying data when requested. Even though it is common to see authors state data is available on request, actually obtaining the data on request seems highly challenging. Although this problem of retrieving data on request is well known (Wicherts et al., 2006), the situation does not seem to have improved. Nowadays, there are straightforward, free, and open ways to share data, including meta-analytic data files. Several repositories (e.g., OSF, GitHub, Zenodo, Figshare) are available for researchers to openly share the data associated with published results. On-request availability has proven to be inadequate, and with the availability of data repositories is no longer necessary. Journals publishing meta-analyses should require that authors share the underlying data in a public data repository.

For the remaining meta-analyses (about two thirds), we were able to retrieve the data used by the original authors. In only 5\% of these cases data was shared in a machine-readable data file (e.g., \emph{csv}, \emph{xlsx}, \ldots), while the data had to be retrieved from files in document format (e.g., \emph{docx}, \emph{pdf}) for the rest of cases. This forces people who want to re-use the data to manually recode the data, which is both inefficient and error-prone task. Even after partial double coding was carried out, this procedure did not avoid some coding errors, which were detected by double checking meta-analyses with discrepancies. In out experience, the data retrieval process can be difficult when results are presented in general tables, as it involves matching subsets of these primary data with different meta-analytic results, while is not always clear which studies were used in which meta-analysis reported in a paper. Furthermore, because the tables in manuscript are often generated manually in document file formats (e.g.~Word), we observed examples where this introduced another source of error. There are good guidelines on how to share research data properly (Wilkinson et al., 2016), and authors should share data in machine-readable formats.

An important finding is that the availability of the original analysis script was very limited. Only in five meta-analyses (3\%, all from the same paper), was the original script openly available. In most cases, the original analyses were reconstructed from the description provided in the paper itself, which was not always rich in detail, so that many of these computational details had to be inferred from the default settings of the software authors used. The availability of analysis scripts often shows similar rates, both in meta-analyses (Page et al., 2022; Polanin et al., 2020) and in primary research (Hardwicke et al., 2022, 2020). This makes it more difficult to easily check the computational reproducibility of the results from such studies. Reconstructing the analytical scheme adds to the workload, with the potential to introduce errors, both in the original report and in the reconstruction, and deals with the eventual lack of relevant analytical information. With the increasing availability of excellent open-source tools to perform meta-analysis (e.g., \emph{metafor} (Viechtbauer, 2010) in R) and useful templates (Moreau \& Gamble, 2020), meta-analysts can use workflows that allow them to create and share analysis code for meta-analyses.

Despite these difficulties, we were able to recover the original data and reconstruct the original analysis approach, for 146 meta-analyses, for which the analytical reproducibility of the results was assessed. These attempts at analytical reproduction went through several stages as explained above, trying to minimize the impact of possible coding errors, and requesting clarifications from the original authors. Nevertheless, even with these efforts, some discrepancies remained in the results. We identified different issued that hindered our reproducibility attempts. For example, in some cases internal discrepancies were found in the paper itself (e.g., text-figure discrepancies, text-abstract, or text-table discrepancies). Furthermore, some problems were found with the lack of some primary data, where data available in the supplementary material included fewer cases than those finally reported in the results of the published paper. These situations could be explained by typos in the manuscript, or updates when performing the meta-analysis that produced different versions of the manuscript, data, or supplementary material. While it is important to note that discrepancies in the summary effect results and their confidence intervals were mostly minor, with little or no impact on the conclusions, these situations are easily avoidable. Some of the problems identified could be explained by typos. Currently, there are tools that facilitate the production of so-called reproducible manuscripts, such as the R packages \emph{kintr} (Xie, 2022) and \emph{rmarkdown} (Allaire et al., 2022). A reproducible manuscript embeds analysis code, data and results reporting in a single document, extracting and reporting the results from the output of the computational process itself, avoiding error-prone manual transcriptions.

Our results are complementary to those observed in previous research on the reproducibility of the primary effects of meta-analyses (Gøtzsche et al., 2007; Maassen et al., 2020) and related problems due to the multiplicity of primary effects (Tendal et al., 2009). These studies found problems in reproducing the primary effects of published meta-analyses, or in reaching agreement between independent coders in computing them. Such problems, to a greater or lesser extent, had some impact on the meta-analytic results. Our results show that, even when re-using the primary effects as originally coded, certain problems of reproducibility of the results may remain. Some of these problems are added error on the source of error found in previous research on reproducibility of primary effects, which in turn are added error on the sources of error types of primary estimates (e.g., measurement error, sampling error, or reporting errors). No scientific research is totally error-free, but one of the main tasks of scientists is to minimize this error, and in some cases, such as those observed in this study, minimizing some potential sources of error can be straightforward.

Our study has some limitations. First, the time span covered is fairly wide. Thus, the findings may not capture the changes that have arisen in recent years. Therefore, future studies should examine more specific changes over years, to evaluate whether better practices emerge that facilitate reproducibility. Second, most of the primary data was retrieved through manual re-coding, which introduces some error. The reported data was rounded, which means we did not have access to precise values, and in many cases the standard error had to be approximated from the confidence limits. These limitation of our study are caused by the suboptimal practices when sharing data we discussed above. Given the non-precise nature of most of the data retrieved, we had to make a decision about which margin of discrepancy was acceptable. In this study, a margin of 5\% was chosen. Because this cut-off is arbitrary, we have tried to focus more on possible issues in the results that fell above this margin, than on establishing a exact ratio of non-reproduced meta-analyses based on this arbitrary cut-off.

In conclusion, we observed several difficulties when attempting to reproduce meta-analyses. Two aspects can be highlighted: (1) data availability and reusability of the data as they are shared, (2) and apparent errors in the reporting of results. As data collected for a meta-analysis can be especially useful for future research, direct and open access to such datasets allows for easy updates, and re-analyses, which are valuable in a cumulative science. Meta-analytic data generally do not contain sensitive or personal information, and can therefore almost always be shared openly, as doing so does not involve ethical or legal conflicts. Third, meta-analytic results often represent the state of the art of the evidence on a particular topic. These results guide applied practice, public policy, or future research directions. This prominent status entails a major responsibility for the credibility, reliability, and validity of published meta-analytic results.

\hypertarget{author-contributions}{%
\subsection{Author Contributions}\label{author-contributions}}

Conceptualization: R. Lopez-Nicolas and J. Sanchez-Meca; Methodology: R. Lopez-Nicolas, D. Lakens, J.A. Lopez-Lopez and J. Sanchez-Meca; Formal Analysis: R Lopez-Nicolas; Investigation: R Lopez-Nicolas, M. Rubio-Aparicio, A. Sandoval-Lentisco, C. Lopez-Ibañez and D. Blazquez-Rincon: Data curation: R Lopez-Nicolas; Writing -- Original Draft Preparation: R. Lopez-Nicolas; Writing -- Review \& Editing: D. Lakens, J.A. Lopez-Lopez, J. Sanchez-Meca, M. Rubio-Aparicio, A. Sandoval-Lentisco, C. Lopez-Ibañez, D. Blazquez-Rincon.

\hypertarget{conflict-of-interest}{%
\subsection{Conflict of interest}\label{conflict-of-interest}}

The author(s) declare that there were no conflicts of interest with respect to the authorship or the publication of this article.

\hypertarget{acknowledgments}{%
\subsection{Acknowledgments}\label{acknowledgments}}

We thank the research group of the Meta-Research Centre of Tilburg University for providing feedback on an earlier version of this manuscript. We would also like to thank all the original authors of the included meta-analyses who enabled access to the data used in this project as well as the authors who provided clarifications in response to requests for clarification in step 3.

\hypertarget{funding}{%
\subsection{Funding}\label{funding}}

This research has been funded with a grant from the Spanish Ministry of Science and Innovation (Project PID2019-104080GB-I00, FEDER funds) and by the Spanish Ministry of Universities (predoctoral grant: FPU18/04805).

\hypertarget{supplemental-material}{%
\section{Supplemental Material}\label{supplemental-material}}

\hypertarget{prior-versions}{%
\section{Prior versions}\label{prior-versions}}

\hypertarget{references}{%
\section*{References}\label{references}}
\addcontentsline{toc}{section}{References}

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-allaire2022}{}}%
Allaire, J., Xie, Y., McPherson, J., Luraschi, J., Ushey, K., Atkins, A., Wickham, H., Cheng, J., Chang, W., \& Iannone, R. (2022). \emph{Rmarkdown: Dynamic documents for r}. \url{https://github.com/rstudio/rmarkdown}

\leavevmode\vadjust pre{\hypertarget{ref-artner2020}{}}%
Artner, R., Verliefde, T., Steegen, S., Gomes, S., Traets, F., Tuerlinckx, F., \& Vanpaemel, W. (2020). The reproducibility of statistical results in psychological research: {An} investigation using unpublished raw data. \emph{Psychological Methods}, No Pagination Specified--No Pagination Specified. \url{https://doi.org/10.1037/met0000365}

\leavevmode\vadjust pre{\hypertarget{ref-bornmann2021}{}}%
Bornmann, L., Haunschild, R., \& Mutz, R. (2021). Growth rates of modern science: A latent piecewise growth curve approach to model publication numbers from established and new literature databases. \emph{Humanities and Social Sciences Communications}, \emph{8}(1), 1--15. \url{https://doi.org/10.1057/s41599-021-00903-w}

\leavevmode\vadjust pre{\hypertarget{ref-errington2021a}{}}%
Errington, T. M., Mathur, M., Soderberg, C. K., Denis, A., Perfito, N., Iorns, E., \& Nosek, B. A. (2021). Investigating the replicability of preclinical cancer biology. \emph{eLife}, \emph{10}, e71601. \url{https://doi.org/10.7554/eLife.71601}

\leavevmode\vadjust pre{\hypertarget{ref-gabelica2022}{}}%
Gabelica, M., Bojčić, R., \& Puljak, L. (2022). Many researchers were not compliant with their published data sharing statement: Mixed-methods study. \emph{Journal of Clinical Epidemiology}. \url{https://doi.org/10.1016/j.jclinepi.2022.05.019}

\leavevmode\vadjust pre{\hypertarget{ref-gotzsche2007}{}}%
Gøtzsche, P. C., Hróbjartsson, A., Marić, K., \& Tendal, B. (2007). Data {Extraction Errors} in {Meta-analyses That Use Standardized Mean Differences}. \emph{JAMA}, \emph{298}(4), 430--437. \url{https://doi.org/10.1001/jama.298.4.430}

\leavevmode\vadjust pre{\hypertarget{ref-gurevitch2018}{}}%
Gurevitch, J., Koricheva, J., Nakagawa, S., \& Stewart, G. (2018). Meta-analysis and the science of research synthesis. \emph{Nature}, \emph{555}(7695), 175--182. \url{https://doi.org/10.1038/nature25753}

\leavevmode\vadjust pre{\hypertarget{ref-hardwicke2021}{}}%
Hardwicke, T. E., Bohn, M., MacDonald, K., Hembacher, E., Nuijten, M. B., Peloquin, B. N., deMayo, B. E., Long, B., Yoon, E. J., \& Frank, M. C. (2021). Analytic reproducibility in articles receiving open data badges at the journal {Psychological Science}: An observational study. \emph{Royal Society Open Science}, \emph{8}(1), 201494. \url{https://doi.org/10.1098/rsos.201494}

\leavevmode\vadjust pre{\hypertarget{ref-hardwicke2018}{}}%
Hardwicke, T. E., Mathur, M. B., MacDonald, K., Nilsonne, G., Banks, G. C., Kidwell, M. C., Hofelich Mohr, A., Clayton, E., Yoon, E. J., Henry Tessler, M., Lenne, R. L., Altman, S., Long, B., \& Frank, M. C. (2018). Data availability, reusability, and analytic reproducibility: Evaluating the impact of a mandatory open data policy at the journal {Cognition}. \emph{Royal Society Open Science}, \emph{5}(8), 180448. \url{https://doi.org/10.1098/rsos.180448}

\leavevmode\vadjust pre{\hypertarget{ref-hardwicke2022}{}}%
Hardwicke, T. E., Thibault, R. T., Kosie, J. E., Wallach, J. D., Kidwell, M. C., \& Ioannidis, J. P. A. (2022). Estimating the {Prevalence} of {Transparency} and {Reproducibility-Related Research Practices} in {Psychology} (2014\textendash 2017). \emph{Perspectives on Psychological Science}, \emph{17}(1), 239--251. \url{https://doi.org/10.1177/1745691620979806}

\leavevmode\vadjust pre{\hypertarget{ref-hardwicke2020}{}}%
Hardwicke, T. E., Wallach, J. D., Kidwell, M. C., Bendixen, T., Crüwell, S., \& Ioannidis, J. P. A. (2020). An empirical assessment of transparency and reproducibility-related research practices in the social sciences (2014-2017). \emph{Royal Society Open Science}, \emph{7}(2), 190806. \url{https://doi.org/10.1098/rsos.190806}

\leavevmode\vadjust pre{\hypertarget{ref-koffel016}{}}%
Koffel, J. B., \& Rethlefsen, M. L. (2016). Reproducibility of {Search} {Strategies} {Is} {Poor} in {Systematic} {Reviews} {Published} in {High}-{Impact} {Pediatrics}, {Cardiology} and {Surgery} {Journals}: {A} {Cross}-{Sectional} {Study}. \emph{PLOS ONE}, \emph{11}(9), e0163309. \url{https://doi.org/10.1371/journal.pone.0163309}

\leavevmode\vadjust pre{\hypertarget{ref-lopez-nicolas2021}{}}%
López-Nicolás, R., López-López, J. A., Rubio-Aparicio, M., \& Sánchez-Meca, J. (2022). A meta-review of transparency and reproducibility-related reporting practices in published meta-analyses on clinical psychological interventions (2000--2020). \emph{Behavior Research Methods}, \emph{54}(1), 334--349. \url{https://doi.org/10.3758/s13428-021-01644-z}

\leavevmode\vadjust pre{\hypertarget{ref-maassen2020}{}}%
Maassen, E., Assen, M. A. L. M. van, Nuijten, M. B., Olsson-Collentine, A., \& Wicherts, J. M. (2020). Reproducibility of individual effect sizes in meta-analyses in psychology. \emph{PLOS ONE}, \emph{15}(5), e0233107. \url{https://doi.org/10.1371/journal.pone.0233107}

\leavevmode\vadjust pre{\hypertarget{ref-maggio2011}{}}%
Maggio, L. A., Tannery, N. H., \& Kanter, S. L. (2011). Reproducibility of {Literature} {Search} {Reporting} in {Medical} {Education} {Reviews}. \emph{Academic Medicine}, \emph{86}(8), 1049--1054. \url{https://doi.org/10.1097/ACM.0b013e31822221e7}

\leavevmode\vadjust pre{\hypertarget{ref-moreau2020}{}}%
Moreau, D., \& Gamble, B. (2020). Conducting a meta-analysis in the age of open science: Tools, tips, and practical recommendations. \emph{Psychological Methods}, \emph{27}(3), 426--432. \url{https://doi.org/10.1037/met0000351}

\leavevmode\vadjust pre{\hypertarget{ref-nationalacademiesofsciencesengineeringandmedicine2019}{}}%
National Academies of Sciences, Engineering, and Medicine. (2019). \emph{Reproducibility and {Replicability} in {Science}}. {The National Academies Press}. \url{https://doi.org/10.17226/25303}

\leavevmode\vadjust pre{\hypertarget{ref-nguyen2022}{}}%
Nguyen, P.-Y., Kanukula, R., McKenzie, J. E., Alqaidoom, Z., Brennan, S. E., Haddaway, N. R., Hamilton, D. G., Karunananthan, S., McDonald, S., Moher, D., Nakagawa, S., Nunan, D., Tugwell, P., Welch, V. A., \& Page, M. J. (2022). \emph{Changing patterns in reporting and sharing of review data in systematic reviews with meta-analysis of the effects of interventions: A meta-research study}. medRxiv. \url{https://doi.org/10.1101/2022.04.11.22273688}

\leavevmode\vadjust pre{\hypertarget{ref-nosek2022}{}}%
Nosek, B. A., Hardwicke, T. E., Moshontz, H., Allard, A., Corker, K. S., Dreber, A., Fidler, F., Hilgard, J., Kline Struhl, M., Nuijten, M. B., Rohrer, J. M., Romero, F., Scheel, A. M., Scherer, L. D., Schönbrodt, F. D., \& Vazire, S. (2022). Replicability, {Robustness}, and {Reproducibility} in {Psychological Science}. \emph{Annual Review of Psychology}, \emph{73}(1), 719--748. \url{https://doi.org/10.1146/annurev-psych-020821-114157}

\leavevmode\vadjust pre{\hypertarget{ref-opensciencecollaboration2015}{}}%
Open Science Collaboration. (2015). Estimating the reproducibility of psychological science. \emph{Science}, \emph{349}(6251), aac4716. \url{https://doi.org/10.1126/science.aac4716}

\leavevmode\vadjust pre{\hypertarget{ref-page2018}{}}%
Page, M. J., Altman, D. G., Shamseer, L., McKenzie, J. E., Ahmadzai, N., Wolfe, D., Yazdi, F., Catalá-López, F., Tricco, A. C., \& Moher, D. (2018). Reproducible research practices are underused in systematic reviews of biomedical interventions. \emph{Journal of Clinical Epidemiology}, \emph{94}, 8--18. \url{https://doi.org/10.1016/j.jclinepi.2017.10.017}

\leavevmode\vadjust pre{\hypertarget{ref-page2022}{}}%
Page, M. J., Nguyen, P.-Y., Hamilton, D. G., Haddaway, N. R., Kanukula, R., Moher, D., \& McKenzie, J. E. (2022). Data and code availability statements in systematic reviews of interventions were often missing or inaccurate: A content analysis. \emph{Journal of Clinical Epidemiology}, \emph{147}, 1--10. \url{https://doi.org/10.1016/j.jclinepi.2022.03.003}

\leavevmode\vadjust pre{\hypertarget{ref-page2016}{}}%
Page, M. J., Shamseer, L., Altman, D. G., Tetzlaff, J., Sampson, M., Tricco, A. C., Catalá-López, F., Li, L., Reid, E. K., Sarkis-Onofre, R., \& Moher, D. (2016). Epidemiology and {Reporting} {Characteristics} of {Systematic} {Reviews} of {Biomedical} {Research}: {A} {Cross}-{Sectional} {Study}. \emph{PLOS Medicine}, \emph{13}(5), e1002028. \url{https://doi.org/10.1371/journal.pmed.1002028}

\leavevmode\vadjust pre{\hypertarget{ref-polanin2020}{}}%
Polanin, J. R., Hennessy, E. A., \& Tsuji, S. (2020). Transparency and {Reproducibility} of {Meta-Analyses} in {Psychology}: {A Meta-Review}. \emph{Perspectives on Psychological Science}, \emph{15}(4), 1026--1041. \url{https://doi.org/10.1177/1745691620906416}

\leavevmode\vadjust pre{\hypertarget{ref-r2022}{}}%
R Core Team. (2022). \emph{R: A language and environment for statistical computing}. R Foundation for Statistical Computing. \url{https://www.R-project.org/}

\leavevmode\vadjust pre{\hypertarget{ref-tedersoo2021}{}}%
Tedersoo, L., Küngas, R., Oras, E., Köster, K., Eenmaa, H., Leijen, Ä., Pedaste, M., Raju, M., Astapova, A., Lukner, H., Kogermann, K., \& Sepp, T. (2021). Data sharing practices and data availability upon request differ across scientific disciplines. \emph{Scientific Data}, \emph{8}(1), 192. \url{https://doi.org/10.1038/s41597-021-00981-0}

\leavevmode\vadjust pre{\hypertarget{ref-tendal2009}{}}%
Tendal, B., Higgins, J. P. T., Jüni, P., Hróbjartsson, A., Trelle, S., Nüesch, E., Wandel, S., Jørgensen, A. W., Gesser, K., Ilsøe-Kristensen, S., \& Gøtzsche, P. C. (2009). Disagreements in meta-analyses using outcomes measured on continuous or rating scales: Observer agreement study. \emph{BMJ}, \emph{339}, b3128. \url{https://doi.org/10.1136/bmj.b3128}

\leavevmode\vadjust pre{\hypertarget{ref-tendal2011}{}}%
Tendal, B., Nüesch, E., Higgins, J. P. T., Jüni, P., \& Gøtzsche, P. C. (2011). Multiplicity of data in trial reports and the reliability of meta-analyses: Empirical study. \emph{BMJ}, \emph{343}, d4829. \url{https://doi.org/10.1136/bmj.d4829}

\leavevmode\vadjust pre{\hypertarget{ref-viechtbauer2010}{}}%
Viechtbauer, W. (2010). Conducting {Meta-Analyses} in {R} with the metafor {Package}. \emph{Journal of Statistical Software}, \emph{36}, 1--48. \url{https://doi.org/10.18637/jss.v036.i03}

\leavevmode\vadjust pre{\hypertarget{ref-wallach2018}{}}%
Wallach, J. D., Boyack, K. W., \& Ioannidis, J. P. A. (2018). Reproducible research practices, transparency, and open access data in the biomedical literature, 2015\textendash 2017. \emph{PLOS Biology}, \emph{16}(11), e2006930. \url{https://doi.org/10.1371/journal.pbio.2006930}

\leavevmode\vadjust pre{\hypertarget{ref-wayant2019}{}}%
Wayant, C., Page, M. J., \& Vassar, M. (2019). Evaluation of {Reproducible} {Research} {Practices} in {Oncology} {Systematic} {Reviews} {With} {Meta}-analyses {Referenced} by {National} {Comprehensive} {Cancer} {Network} {Guidelines}. \emph{JAMA Oncology}, \emph{5}(11), 1550--1555. \url{https://doi.org/10.1001/jamaoncol.2019.2564}

\leavevmode\vadjust pre{\hypertarget{ref-wicherts2006}{}}%
Wicherts, J. M., Borsboom, D., Kats, J., \& Molenaar, D. (2006). The poor availability of psychological research data for reanalysis. \emph{American Psychologist}, \emph{61}(7), 726. \url{https://doi.org/10.1037/0003-066X.61.7.726}

\leavevmode\vadjust pre{\hypertarget{ref-wilkinson2016}{}}%
Wilkinson, M. D., Dumontier, M., Aalbersberg, Ij. J., Appleton, G., Axton, M., Baak, A., Blomberg, N., Boiten, J.-W., da Silva Santos, L. B., Bourne, P. E., Bouwman, J., Brookes, A. J., Clark, T., Crosas, M., Dillo, I., Dumon, O., Edmunds, S., Evelo, C. T., Finkers, R., \ldots{} Mons, B. (2016). The {FAIR Guiding Principles} for scientific data management and stewardship. \emph{Scientific Data}, \emph{3}(1), 160018. \url{https://doi.org/10.1038/sdata.2016.18}

\leavevmode\vadjust pre{\hypertarget{ref-xie2022}{}}%
Xie, Y. (2022). \emph{Knitr: A general-purpose package for dynamic report generation in r}. \url{https://yihui.org/knitr/}

\end{CSLReferences}

\end{document}

### 2022-11-17 supplementary_file.Rmd
Changues for the lastest version

---
title: "Supplementary Material" 
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r supplementary analysis, include=FALSE}

rm(list=ls())
source(here::here("analysis", "06_supplementary.R"))

```

# Sensitivity analysis using other possible criteria

In the first stage, a cut-off point of 5% discrepancy between reported and reproduced results was set to screen meta-analyses. In Figure S1 this criterion is compared with other possibilities in absolute value. Figure S1 shows that the criterion used is one of the most liberal of those compared. Due to our design, the stage where the criterion was applied is only an initial screening, so the meta-analyses labelled by this criterion were reviewed at later stages in a qualitative way. Therefore, a more liberal criterion (minimizing false negatives, but increasing false positives) is more suitable. This criteria has the limitations of any relative index, but due to the mix of metrics included, it is also considered more appropriate.

``` {r, fig.width = 7, fig.height=5, fig.cap="Barplot displaying the number of meta-analyses labelled as numerical error under different criteria. The value used in the original design is 5%, the rest are different values of difference in absolute value between reported and reproduced result."}

figure_s1

```

### 2022-11-17 analysis/00_functions.R

@@ -15,15 +15,24 @@ pacman::p_load(tidyverse, metafor)
 # width: desired bar width
 #
 
-customized_barplot<- function(d, pal, title, legend, width=0.35){
+customized_barplot<- function(d, pal, title, legend, width=0.35, rate=TRUE){
   
   plt <- ggplot(data=d, aes(x=NA, y=perc, fill=Item)) +
     geom_bar(colour = 'black', stat="identity", width = width) +
     scale_x_discrete(breaks = NULL) +
     scale_fill_manual(values=pal,
-                      guide = guide_legend(reverse=T)) +
-    scale_y_continuous(labels=scales::percent) +
-    theme_minimal(base_size = 10) +
+                      guide = guide_legend(reverse=T))
+  if (rate == TRUE){  
+  
+    plt<- plt + scale_y_continuous(labels=scales::percent) 
+    
+  }
+    
+    else {
+      
+    plt <- plt + scale_y_continuous(limits = c(0, sum(d$n)))  
+    }
+    plt <- plt + theme_minimal(base_size = 10) +
     theme(legend.position='bottom', 
           legend.direction='horizontal',
           legend.text = element_text(size = 13),
@@ -32,12 +41,23 @@ customized_barplot<- function(d, pal, title, legend, width=0.35){
           axis.text.y=element_blank(),
           axis.ticks.y=element_blank(),
           axis.title.x=element_blank(),
-          plot.title = element_text(size = 15, face = "bold")) +
-    geom_text(aes(label=sprintf ("%i%%", round(perc*100, 0))), 
+          plot.title = element_text(size = 15, face = "bold")) 
+  
+  if (rate == TRUE) {  
+    plt<-plt +geom_text(aes(label=sprintf ("%i%%", round(perc*100, 0))), 
               size = 4, 
               position = position_stack(vjust = 0.5),
-              fontface = "bold") +
-    labs(fill=legend) +
+              fontface = "bold") 
+    }
+  
+  else {
+    plt<-plt +geom_text(aes(label=paste0(perc)), 
+                       size = 4, 
+                       position = position_stack(vjust = 0.5),
+                       fontface = "bold") 
+  }
+  
+   plt<- plt +labs(fill=legend) +
     ggtitle(sprintf("      %s", title)) +
     coord_flip(clip = 'off') +
     geom_text(
@@ -84,7 +104,9 @@ scatter_match<- function(d, x, y, shape, shape_name, shape_labels, size, title)
         legend.key.size = unit(.5,"cm"),
[…]

### 2022-11-17 analysis/01_importing_data_and_descriptives.R

@@ -1,5 +1,5 @@
 if(!require(pacman)){
-  install.packages("pacman", repos = "https://cran.rstudio.com/")
+  install.packages("pacman")
 }
 library(pacman)
 
@@ -91,9 +91,7 @@ df_reasons<- df_mas %>%
                                        ifelse(final_results == "propietary_data", "Propietary dataset", 
                                               ifelse(final_results == "again asking to supervisor and no reply", 
                                                      "The author requested more information and a written agreement including possible authorship. 
-                                                     After sending her further details on the use of the data, the author indicated that she will discuss this 
-                                                     with her former supervisor (data owner). No further news was heard until a reminder was sent. A reply was received indicating 
-                                                     that she was still waiting for a response from her former supervisor. Subsequently, no further reply was received."))))) %>% 
+                                                      Additional details were sent and after some email exchanges there was no further response."))))) %>% 
   group_by(final_results) %>% 
   tally() %>% 
   cbind(MultinomCI(.$n, conf.level = 0.95, method = "sisonglaz"))%>%
@@ -175,16 +173,16 @@ df_software<- df_mas %>%
 
 ####Figures####
 
-#Figure 1
+#Figure 2
 
 hist_primary_studies<- ggplot(df_mas, aes(x = k)) + 
   geom_histogram(alpha = 0.75, aes(y=..count..), position = "identity",
-                 bins = 20, colour = "#F4B5BD", fill = "lavenderblush") +
+                 bins = 50, colour = "#b00b13", fill = "lavenderblush") +
   labs(x="Number of primary studies included",
        y= "Count")+
-  geom_vline(aes(xintercept=k_median), colour= "#85D4E3",
+  geom_vline(aes(xintercept=k_median), colour= "#3444d9",
              linetype="dashed", size=1)+
-  geom_vline(xintercept = c(k_q1, k_q3), colour = "#85D4E3",
+  geom_vline(xintercept = c(k_q1, k_q3), colour = "#3444d9",
              linetype="dashed", size=0.75, alpha = 0.5)+
   theme_minimal(base_size = 10)+
   theme_classic()+
@@ -195,10 +193,10 @@ hist_primary_studies<- ggplot(df_mas, aes(x = k)) +
     panel.grid.major.y = element_blank(),
     panel.grid.major.x = element_blank())
 
[…]

### 2022-11-17 analysis/02_first_stage.R

@@ -289,6 +289,8 @@ df_mas<- df_mas %>%
   mutate(decision_error = ifelse(original_ci_test==rep_ci_test, "no_error", "error")) %>% 
   mutate(decision_error = factor(decision_error))
 
+save(df_mas, file = here::here("results", "first_stage", "first_stage_results.Rdata"))
+
 ####Selecting meta-analysis to be revised due to issues in reproductions####
 
 df_to_rev<- df_mas %>% 

### 2022-11-17 analysis/03_second_stage.R

@@ -18,6 +18,11 @@ df_mas_revised5<-read_xlsx(here::here("data", "second_stage", "df_to_rev_coder5.
 df_mas_revised<- rbind(df_mas_revised2, df_mas_revised3, df_mas_revised4, df_mas_revised5) %>% 
   arrange(order)
 
+df_npapers<- df_mas_revised %>% 
+  select(ID, order) %>% 
+  group_by(ID, order) %>% 
+  tally()
+
 
 df_to_reanalyse<- df_mas_revised %>% filter(qualitative_check=="re-analyse")
 
@@ -190,9 +195,6 @@ df_to_rev2<- df_mas_revised %>%
 
 write.xlsx(df_to_rev2, here::here("results", "second_stage", "df_to_rev2.xlsx"))
 
-
-####Figure 3#####
-
 df_to_scatter<- df_mas_revised %>% 
   filter(qualitative_check != "re-analyse") %>% 
   rbind(df_to_reanalyse) %>% 
@@ -207,8 +209,15 @@ df_to_scatter<- df_mas_revised %>%
   mutate(decision_error = ifelse(qualitative_check == "re-analyse", decision_error,
                                  ifelse(original_ci_test==rep_ci_test, "no_error", "error"))) %>% 
   mutate(diffi2 = ifelse(qualitative_check == "re-analyse", diffi2,
-                         I2-rep_i2))
+                         I2-rep_i2)) %>% 
+  arrange(order)
 
+
+df_stage2_results<-df_to_scatter
+save(df_stage2_results, file = here::here("results", "second_stage", "second_stage_results.Rdata"))
+
+
+####Figure 4#####
 
 df_to_scatter_original_ci<- df_to_scatter %>% 
   select(LL_CI, UL_CI, decision_error, diff_ac) %>% 
@@ -225,38 +234,39 @@ df_to_scatter_ci<- inner_join(df_to_scatter_original_ci, df_to_scatter_rep_ci, b
 
 
 scatter_g<- scatter_match(df_to_scatter, x=df_to_scatter$summary_effect, y=df_to_scatter$rep_g, 
-                          shape = df_to_scatter$decision_error, shape_name = "Decision error", shape_labels = c("Error", "No error"),
-                          size = abs(df_to_scatter$diff_g),
-                          title = "Summary effect")
+                          shape = df_to_scatter$decision_error, shape_name = "Decision error:", shape_labels = c("Error", "No error"),
+                          size = 15,
[…]

### 2022-11-17 analysis/04_third_stage.R

@@ -89,6 +89,19 @@ df_to_reanalyse<- df_to_reanalyse %>%
   mutate(numerical_error=ifelse(abs(diff_g)>=5 | abs(diff_ac)>=5, "error", "minor")) %>% 
   mutate(numerical_error=ifelse(diff_g==0 & diff_ac == 0, "no_error", numerical_error)) %>%
   mutate(decision_error = ifelse(original_ci_test==rep_ci_test, "no_error", "error")) %>% 
-  relocate(c(issues, qualitative_check), .after = last_col())
+  relocate(c(issues, qualitative_check), .after = last_col()) %>% 
+  mutate(qualitative_check2= c(rep("rep", 7), "no_rep", "rep"))
+
+df_results_stage_3<- df_to_rev2 %>% 
+  filter(clarification_request_results != "Reply") %>% 
+  mutate(qualitative_check2 = c(rep(NA, nrow(.)))) %>% 
+  rbind(df_to_reanalyse) %>% 
+  arrange(order)
+
+
+save(df_results_stage_3, file = here::here("results", "third_stage", "third_stage_results.Rdata"))
+
+
+
 
 

### 2022-11-17 analysis/05_figure6.R

@@ -1,0 +1,71 @@
+if(!require(pacman)){
+  install.packages("pacman")
+}
+
+library(pacman)
+
+pacman::p_load(tidyverse,
+               wesanderson,
+               ggpubr)
+
+
+####Importing data####
+
+load(here::here("results", "first_stage", "first_stage_results.Rdata"))
+load(here::here("results", "second_stage", "second_stage_results.Rdata"))
+load(here::here("results", "third_stage", "third_stage_results.Rdata"))
+
+
+source(here::here("analysis", "00_functions.R"))
+
+
+#####Figure S1#####
+
+stage_1<- df_mas %>% 
+  mutate(numerical_error = ifelse(numerical_error == "error", "error", "no_error")) %>% 
+  group_by(numerical_error, decision_error) %>% 
+  tally() %>% 
+  mutate(Item = paste0(numerical_error," ", decision_error)) %>% 
+  mutate(Item = factor(Item)) %>% 
+  mutate(Item = fct_recode(Item, "Numerical and decision error" = "error error", "Numerical error" = "error no_error", "No error" = "no_error no_error")) %>% 
+  mutate(perc=n)
+
+
+stage_2<- df_stage2_results %>% 
+  mutate(numerical_error = ifelse(numerical_error == "error", "error", "no_error")) %>% 
+  mutate(Item = ifelse(qualitative_check ==  "re-analyse" & numerical_error == "no_error", "Reproduced after fixing a coding error",
+                       ifelse(qualitative_check == "rep", "Reproduced after minor adjustment", "Error"))) %>% 
+  group_by(Item) %>% 
+  tally() %>% 
+  mutate(Results = factor(Item)) %>% 
+  mutate(perc=n)
+
+
+stage_3<- df_results_stage_3 %>% 
+  mutate(Item = factor(clarification_request_results)) %>% 
+  group_by(ID, Item) %>% 
+  tally() %>% 
+  group_by(Item) %>% 
+  tally() %>% 
+  mutate(perc=n)
+
+Moonrise3 <-rev(wes_palette("Moonrise3", n=5))
+
+plt_stage1<-customized_barplot(stage_1, pal = Moonrise3[3:5], title = "", legend = "Result", width = .35, rate = FALSE) +
+  theme(plot.margin = unit(c(3, 0, 3, 0), "lines"))
+
[…]

### 2022-11-17 analysis/06_supplementary.R

@@ -1,0 +1,44 @@
+if(!require(tidyverse)){
+  install.packages("tidyverse")
+}
+
+library(tidyverse)
+
+####Importing data####
+
+load(here::here("results", "first_stage", "first_stage_results.Rdata"))
+
+#####Figure S1#####
+
+
+
+df_mas <- df_mas %>% 
+  mutate(diff_g_abs = summary_effect - rep_g) %>% 
+  mutate(diff_ac_abs =  AC - rep_ac_g) %>%   
+  mutate(numerical_error1 = ifelse(abs(diff_g_abs) >= 0.01 | abs(diff_ac_abs) >= 0.02 , "error", "no_error")) %>% 
+  mutate(numerical_error2 = ifelse(abs(diff_g_abs) >= 0.02 | abs(diff_ac_abs) >= 0.04 , "error", "no_error")) %>% 
+  mutate(numerical_error3 = ifelse(abs(diff_g_abs) >= 0.03 | abs(diff_ac_abs) >= 0.06 , "error", "no_error")) %>% 
+  mutate(numerical_error4 = ifelse(abs(diff_g_abs) >= 0.04 | abs(diff_ac_abs) >= 0.08 , "error", "no_error")) %>% 
+  mutate(numerical_error5 = ifelse(abs(diff_g_abs) >= 0.05 | abs(diff_ac_abs) >= 0.10 , "error", "no_error")) %>% 
+  mutate(numerical_error =  ifelse(numerical_error == "error", "error", "no_error"))
+
+
+df_plot<- df_mas %>%
+  pivot_longer(c(numerical_error, numerical_error1, numerical_error2, numerical_error3, numerical_error4, numerical_error5), 
+               names_to = "criteria") %>% 
+  select(51, 52) %>% 
+  filter(value == "error")
+
+
+
+figure_s1<-ggplot(aes(x=criteria), data = df_plot) + 
+  geom_bar(colour = "black", fill = "#b00b13", width = .8) +
+  scale_y_continuous(name = "Meta-analyses lablled as numerical error", limits = c(0,150), expand=c(0,0),breaks = c(0, 50, 100, 146))+
+  scale_x_discrete(name = "Criteria", labels = c("5%", "0.01", "0.02", "0.03", "0.04", "0.05"))+  
+  theme_minimal(base_size = 12)+
+  theme(panel.grid.major = element_blank(),  
+        axis.line = element_line(colour = "black"),
+        axis.text = element_text(vjust = 0, size = 12),
[…]

### 2022-11-17 manuscript.Rmd
minor corrections in manuscript

@@
 Thus, their assessment focus is on this stage of the analysis pipeline of a meta-analysis, which usually involves decisions on how to select the primary outcomes and how to deal with possible dependency, and the computation of (standardized) effect sizes.
-Figure 1 displays a summary of the basic meta-analysis pipeline through a flowchart, outlining the different stages and listing previous work that has explored different facets of reproducibility of these as well as the required elements to be able to reproduce each stage.
+Figure 1 displays a summary of the basic meta-analysis pipeline through a flowchart, outlining the different stages and listing previous work that has explored different facets of reproducibility of these, as well as the required elements to be able to reproduce each stage.
 
@@
 ## Data, materials, and online resources
+
+Data and analysis script code are openly available at: https://osf.io/6cmzh/
 
@@
 This analysis scheme was programmed in the R environment [@r2022] using the *metafor* package [@viechtbauer2010].
-The scripts are available at: ….
 
@@
 Figure 2 displays the distribution of number of primary studies among the meta-analyses included in our sample.
-Original results and characteristics of these meta-analyses are available at: …
+Original results and characteristics of these meta-analyses are available at: https://osf.io/8jzbk
 
@@
 We thank the research group of the Meta-Research Centre of Tilburg University for providing feedback on an earlier version of this manuscript.
-We would also like to thank all the original authors of the included meta-analyses who enabled access to the data used in this project as well as the authors who provided clarifications in response to requests for clarification in step 3.
+We would also like to thank all the original authors of the included meta-analyses who enabled access to the data used in this project as well as the authors who provided clarifications in response to requests for clarification in the third stage.
 
@@
 
-# Supplemental Material
+## Supplemental Material
 
-# Prior versions
+## Prior versions
 

### 2022-11-17 manuscript.tex
minor corrections in manuscript

@@
 \subsection{Data, materials, and online resources}\label{data-materials-and-online-resources}}
+
+Data and analysis script code are openly available at: \url{https://osf.io/6cmzh/}
 
@@
 This analysis scheme was programmed in the R environment (R Core Team, 2022) using the \emph{metafor} package (Viechtbauer, 2010).
-The scripts are available at: \ldots.
 
@@
 Figure 2 displays the distribution of number of primary studies among the meta-analyses included in our sample.
-Original results and characteristics of these meta-analyses are available at: \ldots{}
+Original results and characteristics of these meta-analyses are available at: \url{https://osf.io/8jzbk}
 
@@
 \hypertarget{supplemental-material}{%
-\section{Supplemental Material}\label{supplemental-material}}
+\subsection{Supplemental Material}\label{supplemental-material}}
 
 \hypertarget{prior-versions}{%
-\section{Prior versions}\label{prior-versions}}
+\subsection{Prior versions}\label{prior-versions}}
 

### 2022-11-25 manuscript.Rmd
Minor changues

@@
   interventions"
-shorttitle: "Meta-analyses reproducibility"
+shorttitle: "Meta-analyses reproducibility (PRE-PRINT)"
 leftheader: "Lopez-Nicolas et al."
@@
 
-author_note: |
- All materials, data, and analysis script coded have been made publicly available on the Open Science Framework: https://osf.io/6cmzh/.
-This research has been funded with a grant from the Spanish Ministry of Science and Innovation by FEDER funds (Project nº PID2019-104080GB-I00), and by a predoctoral grant (FPU18/04805) from the Spanish Ministry of Universities.The funders had no role in study design, data collection and analysis, decision to publish, or preparation of the manuscript.
-
 abstract: |
@@
 
-class             : "jou, a4paper"
+class             : "apa7"
 output            : papaja::apa6_pdf
@@
 Given the importance of meta-analyses for evidence-based practice, these threats to their credibility need to be closely monitored.
+
 In recent years different concerns on credibility of  empirical claims have emerged.
@@
 Thus, their assessment focus is on this stage of the analysis pipeline of a meta-analysis, which usually involves decisions on how to select the primary outcomes and how to deal with possible dependency, and the computation of (standardized) effect sizes.
-Figure 1 displays a summary of the basic meta-analysis pipeline through a flowchart, outlining the different stages and listing previous work that has explored different facets of reproducibility of these, as well as the required elements to be able to reproduce each stage.
+Figure 1 displays a summary of the basic meta-analysis pipeline through a flowchart, outlining the different stages and listing previous work that has explored different facets of reproducibility of these, as well as a summary of the required elements to be able to reproduce each stage.
 
@@
 
-Reproducibility analysis typically uses the original data available from the original authors (e.g., [@artner2020; @hardwicke2021; @hardwicke2018].
+Reproducibility analysis typically uses the original data available from the original authors [e.g., @artner2020; @hardwicke2021; @hardwicke2018].
 This puts the focus of the assessment at factors such as the reusability of the available data, challenges for the reconstruction of the original analysis scheme, reporting errors, etc.
@@
 ## Preregistration
-The pre-data analysis protocol (https://osf.io/42r3p/) was pre-registered on 19 October 2021. Any deviation from this protocol is explicitly acknowledged.
+The pre-data analysis protocol (https://doi.org/10.17605/OSF.IO/79J2T) was pre-registered on 19 October 2021. Any deviation from this protocol is explicitly acknowledged.
 
@@
 If we were unable to obtain the data through the email request, the associated meta-analysis was labelled as not process reproducible.
+
 In order to be able to reproduce meta-analyses, primary effects and their associated standard errors are required.
@@
 If the software used was not reported, we inferred this information from the default settings of the most used software in the sample, which was *Comprehensive Meta-Analysis*.
+
 Additional information about the meta-analysis was collected that is not reported in this manuscript.
@@
 Finally, the label 'decision error' refers to situations where the $p_{reported}$ fell on the opposite side of the .05 boundary in relation to the $p_{reproduced}$.
+
 We focus on analytical reproducibility of summary effects, their confidence bounds and the result of the null hypothesis significance test.
@@
 This situation exemplifies the potential issues arising from having to reconstruct the original data from tables and figures and not having open access to the original data file.
+
 In the other case, the original data was retrieved from a huge table in supplementary material with all effect sizes and their confidence limits.
@@
 retrieving data from tables and figures when no data file was available), for about a third of the included meta-analyses no data was available.
-In these cases, attempts were made to obtain the data on request to the corresponding author, with little success.Authors only shared data in 12% of the requests that were made.
+In these cases, attempts were made to obtain the data on request to the corresponding author, with little success.
+Authors only shared data in 12% of the requests that were made.
 This result is in line with what was found in a recent study where data availability statements from a set of primary studies were analysed [@gabelica2022].Where 42% of primary studies in @gabelica2022 reported data was available on request (and identical percentage was found in @page2022 for meta-analyses), only 6.8% of the authors shared the underlying data when requested.
@@
 For the remaining meta-analyses (about two thirds), we were able to retrieve the data used by the original authors.
-In only 5% of these cases data was shared in a machine-readable data file (e.g., *csv*, *xlsx*, ...), while the data had to be retrieved from files in document format (e.g., *docx*, *pdf*) for the rest of cases.
+In only 5% of these cases data was shared in a machine-readable data file (e.g., *csv*, *xlsx*), while the data had to be retrieved from files in document format (e.g., *docx*, *pdf*) for the rest of cases.
 This forces people who want to re-use the data to manually recode the data, which is both inefficient and error-prone task.
@@
 Some of the problems identified could be explained by typos.
-Currently, there are tools that facilitate the production of so-called reproducible manuscripts, such as the R packages *kintr* [@xie2022] and *rmarkdown* [@allaire2022].
+Currently, there are tools that facilitate the production of so-called reproducible manuscripts, such as the R packages *kintr* [@xie2022], *rmarkdown* [@allaire2022], and *papaja* [@aust2022].
 A reproducible manuscript embeds analysis code, data and results reporting in a single document, extracting and reporting the results from the output of the computational process itself, avoiding error-prone manual transcriptions.
@@
 ## Funding 
-This research has been funded with a grant from the Spanish Ministry of Science and Innovation (Project PID2019-104080GB-I00, FEDER funds) and by the Spanish Ministry of Universities (predoctoral grant: FPU18/04805).
+This research has been funded with a grant from the Spanish Ministry of Science and Innovation (Project PID2019-104080GB-I00/AEI/10.13039/501100011033, FEDER funds) and by the Spanish Ministry of Universities (predoctoral grant: FPU18/04805).
 
@@
 
-## Prior versions
+Supplementary material available at: https://osf.io/fjhpw
 

### 2022-11-25 manuscript.tex
Minor changues

@@
 \documentclass[
-  ,jou, a4paper,floatsintext]{apa6}
+  ,apa7,floatsintext]{apa6}
 \usepackage{amsmath,amssymb}
@@
 \keywords{meta-analysis, reproducibility, data sharing, data reusability, research synthesis}
-\usepackage{dblfloatfix}
-
 \usepackage{csquotes}
@@
 
-\shorttitle{Meta-analyses reproducibility}
+\shorttitle{Meta-analyses reproducibility (PRE-PRINT)}
 
@@
 Given the importance of meta-analyses for evidence-based practice, these threats to their credibility need to be closely monitored.
+
 In recent years different concerns on credibility of empirical claims have emerged.
@@
 
-Reproducibility analysis typically uses the original data available from the original authors (e.g., (Artner et al., 2020; Hardwicke et al., 2021, 2018).
+Reproducibility analysis typically uses the original data available from the original authors (e.g., Artner et al., 2020; Hardwicke et al., 2021, 2018).
 This puts the focus of the assessment at factors such as the reusability of the available data, challenges for the reconstruction of the original analysis scheme, reporting errors, etc.
@@
 
-The pre-data analysis protocol (\url{https://osf.io/42r3p/}) was pre-registered on 19 October 2021. Any deviation from this protocol is explicitly acknowledged.
+The pre-data analysis protocol (\url{https://doi.org/10.17605/OSF.IO/79J2T}) was pre-registered on 19 October 2021. Any deviation from this protocol is explicitly acknowledged.
 
@@
 This reminder was sent to a more recent alternative email address if we were able to find one.
-If we were unable to obtain the data through the email request, the associated meta-analysis was labelled as not process reproducible.\\
+If we were unable to obtain the data through the email request, the associated meta-analysis was labelled as not process reproducible.
+
 In order to be able to reproduce meta-analyses, primary effects and their associated standard errors are required.
@@
 If the software used was not reported, we inferred this information from the default settings of the most used software in the sample, which was \emph{Comprehensive Meta-Analysis}.
+
 Additional information about the meta-analysis was collected that is not reported in this manuscript.
@@
 Finally, the label `decision error' refers to situations where the \(p_{reported}\) fell on the opposite side of the .05 boundary in relation to the \(p_{reproduced}\).
+
 We focus on analytical reproducibility of summary effects, their confidence bounds and the result of the null hypothesis significance test.
@@
 Even when we interpret data availability in the broad sense (i.e.~retrieving data from tables and figures when no data file was available), for about a third of the included meta-analyses no data was available.
-In these cases, attempts were made to obtain the data on request to the corresponding author, with little success.Authors only shared data in 12\% of the requests that were made.
+In these cases, attempts were made to obtain the data on request to the corresponding author, with little success.
+Authors only shared data in 12\% of the requests that were made.
 This result is in line with what was found in a recent study where data availability statements from a set of primary studies were analysed (Gabelica et al., 2022).Where 42\% of primary studies in Gabelica et al.
@@
 For the remaining meta-analyses (about two thirds), we were able to retrieve the data used by the original authors.
-In only 5\% of these cases data was shared in a machine-readable data file (e.g., \emph{csv}, \emph{xlsx}, \ldots), while the data had to be retrieved from files in document format (e.g., \emph{docx}, \emph{pdf}) for the rest of cases.
+In only 5\% of these cases data was shared in a machine-readable data file (e.g., \emph{csv}, \emph{xlsx}), while the data had to be retrieved from files in document format (e.g., \emph{docx}, \emph{pdf}) for the rest of cases.
 This forces people who want to re-use the data to manually recode the data, which is both inefficient and error-prone task.
@@
 Some of the problems identified could be explained by typos.
-Currently, there are tools that facilitate the production of so-called reproducible manuscripts, such as the R packages \emph{kintr} (Xie, 2022) and \emph{rmarkdown} (Allaire et al., 2022).
+Currently, there are tools that facilitate the production of so-called reproducible manuscripts, such as the R packages \emph{kintr} (Xie, 2022), \emph{rmarkdown} (Allaire et al., 2022), and \emph{papaja} (Aust \& Barth, 2022).
 A reproducible manuscript embeds analysis code, data and results reporting in a single document, extracting and reporting the results from the output of the computational process itself, avoiding error-prone manual transcriptions.
@@
 
-This research has been funded with a grant from the Spanish Ministry of Science and Innovation (Project PID2019-104080GB-I00, FEDER funds) and by the Spanish Ministry of Universities (predoctoral grant: FPU18/04805).
+This research has been funded with a grant from the Spanish Ministry of Science and Innovation (Project PID2019-104080GB-I00/AEI/10.13039/501100011033, FEDER funds) and by the Spanish Ministry of Universities (predoctoral grant: FPU18/04805).
 
@@
 
-\hypertarget{prior-versions}{%
-\subsection{Prior versions}\label{prior-versions}}
+Supplementary material available at: \url{https://osf.io/fjhpw}
 
@@
 \url{https://doi.org/10.1037/met0000365}
+
+\leavevmode\vadjust pre{\hypertarget{ref-aust2022}{}}%
+Aust, F., \& Barth, M. (2022). \emph{{papaja}: {Prepare} reproducible {APA} journal articles with {R Markdown}}. \url{https://github.com/crsh/papaja}
 

### 2022-11-25 analysis/01_importing_data_and_descriptives.R

@@ -193,7 +193,7 @@ hist_primary_studies<- ggplot(df_mas, aes(x = k)) +
     panel.grid.major.y = element_blank(),
     panel.grid.major.x = element_blank())
 
-ggsave(here::here("results", 'Figure 2.tiff'), width = 6 , height = 6 , units = "in", dpi = 600, compression = "lzw+p")
+#ggsave(here::here("results", 'Figure 2.tiff'), width = 6 , height = 6 , units = "in", dpi = 600, compression = "lzw+p")
 
 
 #Figure 3
@@ -215,7 +215,7 @@ figure3<- ggarrange(plt_process_rep,
                     labels = c("A", "B", "C"),
                     ncol = 1, nrow = 3, font.label = list(size = 14))
 
-ggsave(here::here("results", 'Figure 3.tiff'), width = 10, height = 11, units = "in", dpi = 600, compression = "lzw+p")
+#ggsave(here::here("results", 'Figure 3.tiff'), width = 10, height = 11, units = "in", dpi = 600, compression = "lzw+p")
 
 
 ####Secondary analysis####
@@ -316,5 +316,5 @@ mas_df<- flatten(mas_dat)
 
 #Saving primary data
 
-save(df_mas, mas_df,
-     file = here::here("data", "first_stage", "data.Rdata"))
+#save(df_mas, mas_df,
+#     file = here::here("data", "first_stage", "data.Rdata"))

### 2022-11-25 analysis/02_first_stage.R

@@ -289,7 +289,7 @@ df_mas<- df_mas %>%
   mutate(decision_error = ifelse(original_ci_test==rep_ci_test, "no_error", "error")) %>% 
   mutate(decision_error = factor(decision_error))
 
-save(df_mas, file = here::here("results", "first_stage", "first_stage_results.Rdata"))
+#save(df_mas, file = here::here("results", "first_stage", "first_stage_results.Rdata"))
 
 ####Selecting meta-analysis to be revised due to issues in reproductions####
 

### 2022-11-25 analysis/03_second_stage.R

@@ -214,7 +214,8 @@ df_to_scatter<- df_mas_revised %>%
 
 
 df_stage2_results<-df_to_scatter
-save(df_stage2_results, file = here::here("results", "second_stage", "second_stage_results.Rdata"))
+
+#save(df_stage2_results, file = here::here("results", "second_stage", "second_stage_results.Rdata"))
 
 
 ####Figure 4#####
@@ -255,7 +256,7 @@ figure4<- ggarrange(scatter_g,
                     ncol = 1, nrow = 2, font.label = list(size = 15),
                     common.legend = FALSE, legend = "bottom")
 
-ggsave(here::here("results","second_stage", 'Figure 4.tiff'), width = 7, height = 14, units = "in", dpi = 600, compression = "lzw+p")
+#ggsave(here::here("results","second_stage", 'Figure 4.tiff'), width = 7, height = 14, units = "in", dpi = 600, compression = "lzw+p")
 
 
 ####Secondary analysis, Figure 4####
@@ -269,4 +270,4 @@ scatter_i2<-scatter_match(df_to_scatter, x=df_to_scatter$I2, y=df_to_scatter$rep
 figure5<- ggarrange(scatter_i2,
                     legend = "bottom")
 
-ggsave(here::here("results","second_stage", 'Figure 5.tiff'), width = 7, height = 6, units = "in", dpi = 600, compression = "lzw+p")
+#ggsave(here::here("results","second_stage", 'Figure 5.tiff'), width = 7, height = 6, units = "in", dpi = 600, compression = "lzw+p")

### 2022-11-25 analysis/04_third_stage.R

@@ -99,7 +99,7 @@ df_results_stage_3<- df_to_rev2 %>%
   arrange(order)
 
 
-save(df_results_stage_3, file = here::here("results", "third_stage", "third_stage_results.Rdata"))
+#save(df_results_stage_3, file = here::here("results", "third_stage", "third_stage_results.Rdata"))
 
 
 

### 2022-11-25 analysis/05_figure6.R

@@ -68,4 +68,4 @@ figure5b<- ggarrange(plt_stage1,
                       ncol = 1, nrow = 3)
 
 
-ggsave(here::here("results", 'Figure 6b.tiff'), width = 8, height = 12, units = "in", dpi = 600, compression = "lzw+p")
+#ggsave(here::here("results", 'Figure 6b.tiff'), width = 8, height = 12, units = "in", dpi = 600, compression = "lzw+p")

### 2022-11-25 analysis/06_supplementary.R

@@ -41,4 +41,4 @@ figure_s1<-ggplot(aes(x=criteria), data = df_plot) +
         axis.text = element_text(vjust = 0, size = 12),
         axis.title = element_text(size = 14, face = "bold"))
 
-ggsave(here::here("results", 'Figure S1.tiff'), width = 7, height = 7, units = "in", dpi = 600, compression = "lzw+p")
+#ggsave(here::here("results", 'Figure S1.tiff'), width = 7, height = 7, units = "in", dpi = 600, compression = "lzw+p")

### 2022-11-25 manuscript.Rmd
Minor corrections

@@
   Meta-analysis is one of the most useful and powerful research approaches, however, this relevance relies on its credibility.
-In recent years different concerns on credibility of psychological research have emerged.
+In recent years different concerns about the credibility of psychological research have emerged.
 Analytical reproducibility of scientific results could be considered as the minimal threshold of it.
 In this study, our purpose was to assess the analytical reproducibility and data reusability of a set of published meta-analyses.
-From a random sample of 100 papers containing at least one meta-analysis on effectiveness of interventions in psychology used in a previous study, 217 meta-analyses were selected.
-We first tried to retrieve the original data by recovering a data file, recoding the data from document files (pdf, doc) or on request.
+From a random sample of 100 papers containing at least one meta-analysis on the effectiveness of interventions in psychology used in a previous study, 217 meta-analyses were selected.
+We first tried to retrieve the original data by recovering a data file, recoding the data from document files (pdf, doc), or on request.
 Second, through a multi-stage workflow, we tried to reproduce the main results of each meta-analysis using these data.
 The original data were retrieved for 146 meta-analyses from different sources.
-Of these, in a first stage 52 showed a discrepancy larger than 5% in the main results, in 25 of them this discrepancy was solved with minor adjustments, or correction of coding errors.
-In the remaining 27, different issues were identified in an in-depth review of the papers, such as: reporting inconsistencies, lack of some data or transcription errors.
+Of these, in the first stage 52 showed a discrepancy larger than 5% in the main results, in 25 of them, this discrepancy was solved with minor adjustments, or correction of coding errors.
+In the remaining 27, different issues were identified in an in-depth review of the papers, such as reporting inconsistencies, lack of some data, or transcription errors.
 Current practices of data sharing in meta-analyses hamper the reusability of meta-analytic data.
@@
 
-In recent years different concerns on credibility of  empirical claims have emerged.
+In recent years different concerns on the credibility of  empirical claims have emerged.
 Several projects have systematically attempted to assess the replicability and reproducibility of published scientific results (e.g., @artner2020; @errington2021a; @opensciencecollaboration2015).

### 2022-11-25 manuscript.tex
Minor corrections

@@
 Meta-analysis is one of the most useful and powerful research approaches, however, this relevance relies on its credibility.
-In recent years different concerns on credibility of psychological research have emerged.
+In recent years different concerns about the credibility of psychological research have emerged.
 Analytical reproducibility of scientific results could be considered as the minimal threshold of it.
 In this study, our purpose was to assess the analytical reproducibility and data reusability of a set of published meta-analyses.
-From a random sample of 100 papers containing at least one meta-analysis on effectiveness of interventions in psychology used in a previous study, 217 meta-analyses were selected.
-We first tried to retrieve the original data by recovering a data file, recoding the data from document files (pdf, doc) or on request.
+From a random sample of 100 papers containing at least one meta-analysis on the effectiveness of interventions in psychology used in a previous study, 217 meta-analyses were selected.
+We first tried to retrieve the original data by recovering a data file, recoding the data from document files (pdf, doc), or on request.
 Second, through a multi-stage workflow, we tried to reproduce the main results of each meta-analysis using these data.
 The original data were retrieved for 146 meta-analyses from different sources.
-Of these, in a first stage 52 showed a discrepancy larger than 5\% in the main results, in 25 of them this discrepancy was solved with minor adjustments, or correction of coding errors.
-In the remaining 27, different issues were identified in an in-depth review of the papers, such as: reporting inconsistencies, lack of some data or transcription errors.
+Of these, in the first stage 52 showed a discrepancy larger than 5\% in the main results, in 25 of them, this discrepancy was solved with minor adjustments, or correction of coding errors.
+In the remaining 27, different issues were identified in an in-depth review of the papers, such as reporting inconsistencies, lack of some data, or transcription errors.
 Current practices of data sharing in meta-analyses hamper the reusability of meta-analytic data.
@@
 
-In recent years different concerns on credibility of empirical claims have emerged.
+In recent years different concerns on the credibility of empirical claims have emerged.
 Several projects have systematically attempted to assess the replicability and reproducibility of published scientific results (e.g., Artner et al.

### 2022-11-28 analysis/01_importing_data_and_descriptives.R
Fixing the background of plots

@@ -215,7 +215,7 @@ figure3<- ggarrange(plt_process_rep,
                     labels = c("A", "B", "C"),
                     ncol = 1, nrow = 3, font.label = list(size = 14))
 
-#ggsave(here::here("results", 'Figure 3.tiff'), width = 10, height = 11, units = "in", dpi = 600, compression = "lzw+p")
+#ggsave(here::here("results", 'Figure 3.tiff'), width = 10, height = 11, bg = "white", units = "in", dpi = 600, compression = "lzw+p")
 
 
 ####Secondary analysis####

### 2022-11-28 analysis/05_figure6.R

@@ -68,4 +68,4 @@ figure5b<- ggarrange(plt_stage1,
                       ncol = 1, nrow = 3)
 
 
-#ggsave(here::here("results", 'Figure 6b.tiff'), width = 8, height = 12, units = "in", dpi = 600, compression = "lzw+p")
+#ggsave(here::here("results", 'Figure 6b.tiff'), width = 8, height = 12, bg = "white", units = "in", dpi = 600, compression = "lzw+p")

### 2022-11-28 analysis/06_supplementary.R

@@ -41,4 +41,4 @@ figure_s1<-ggplot(aes(x=criteria), data = df_plot) +
         axis.text = element_text(vjust = 0, size = 12),
         axis.title = element_text(size = 14, face = "bold"))
 
-#ggsave(here::here("results", 'Figure S1.tiff'), width = 7, height = 7, units = "in", dpi = 600, compression = "lzw+p")
+#ggsave(here::here("results", 'Figure S1.tiff'), width = 7, height = 7, bg = "white", units = "in", dpi = 600, compression = "lzw+p")

### 2023-04-21 response_letter.Rmd
Revised version

---
title       : "Reproducibility of published meta-analyses on clinical psychological
  interventions"
authors     : "Ruben Lopez-Nicolas et al."
journal     : "Advances in Methods and Practices in Psychological Science"
manuscript  : "AMPPS-22-0119"

class       : "draft"
output      : papaja::revision_letter_pdf
---

Dear Dr. Flake,

We are very grateful to you for offering us the opportunity of sending a revised version of our paper. We are also very grateful to all the Reviewers, as they have made interesting suggestions and good recommendations to improve the quality of our paper. 
In the revised version of the paper we have tried to address all of your suggestions. Next, we provide point by point answers to the Reviewers’ comments and specify how we have addressed them in the revised manuscript.

# Reviewer \#1

\RC {The authors present their efforts to reproduce 217 published meta-analyses from Clinical Psychology. This is done systematically and thoughtfully.

Major points:
“Each meta-analysis was labelled using the following reproducibility success scheme: (a) reproducible; (b) not process-reproducible; (c) numerical error, and (d) decision error.” This initially read to me like there were four classes that each meta-analysis can fall into. However, it’s actually a hierarchy, where c and d are necessarily also labeled a.}

In this scheme ‘(a) reproducible’ involves both, process-reproducible meta-analyses without error. We admit that it can be a bit confusing. Therefore, in the revised version we have restructured this scheme as follows (see p. 10):

> Each meta-analysis was labelled using the following \textcolor{blue}{two-level} reproducibility success scheme. \textcolor{blue}{First, each meta-analysis was labelled as: (a) process-reproducible; and (b) not process-reproducible. In our study, not process-reproducible refers to situations where we were unable to access the primary data neither through direct extraction nor upon request. Second, those labelled as process-reproducible} were labelled as: (a) reproducible; (b) numerical error; and (c) decision error...

\RC{It appears that, of the 217 meta-analyses, 146 fell into class a and 71 fell into class b. Of the 146 in class a, 52 were labelled as a numerical/decision error. 25 of these 52 were relabeled after double-checking for things like rounding errors, but the scatterplots focus on the full 52. The degree of discrepancy between the original and reproduced values is larger for the I-squared statistic than it is for the summary statistic or its associated CIs.

Overall, I found this paper interesting. I think it’s important topic, and the biggest takeaway is a call for meta-analysts to make their datasets and code available in a systematic way. As someone who has tried to reproduce published meta-analyses on many occasions, I could not agree more! I did find the reporting of the results to be a little confusing, however. I’m not sure how much of this can be avoided, since listing statistics is inherently hard to read, but there are several cases where the authors simply refer to a set of meta-analyses without enough context (e.g., line 39, p. 16). One thing that might help is the use of a Sankey plot instead of Figure 3. Perhaps also designating each set of meta-analyses with some title and then referring to them in a consistent way. Or even having Figure 6 appear earlier in the paper?}

This is a quite relevant point, thanks for the feedback and suggestions on it.

We were exploring different ways to improve the reporting of the results. First, we tried to merge Figure 3 and Figure 6 into a single Sankey plot to illustrate the whole workflow. We found that plot a bit confusing and cluttered though, mainly due to the number of different primary data sources (Figure 3c). Second, we tried Figure 3 as a barplot and plotting the results of the Figure 6 using a Sankey plot instead of a bar plot. We deemed this an improvement, and therefore are using this plot in the revised manuscript. Furthermore, we agree with you that the (old) Figure 6 is much more helpful if presented earlier in the manuscript, so we have moved this figure to the “Outcome reproducibility” section. Now it’s Figure 4 (see p. 16 in the revised manuscript).

\RC {The authors bring up an excellent point about the importance of when these meta-analyses were published and how that should affect data availability. Some degree of analysis of this would be nice to see in the paper (e.g., average years since publication for the 146 reproducible vs. the 71 not). I understand if the authors are wary about adding additional analyses that try to explain when and why a meta-analysis had errors, but I don’t think an exploration of publication date falls into that category.}

We mentioned this as limitation instead of carrying out temporal comparisons because –as it wasn’t among our primary aims– we didn’t consider our sampling design suitable for it. As an unrestricted random sample of meta-analyses published between 2000 and 2020, as expected, the publication year distribution is clearly left-skewed, so the information provided by the data at the bottom range of publication year is limited.

We agree that more information on this matter in the paper would be useful. Hence, we have extended Figure 2 including a second panel showing the publication year distribution (see p. 13).

Furthermore, we statistically compared the possibility of retrieving the data as a function of publication year. These exploratory analyses are reported in the Supplementary file, section “Data availability over years”.  This analysis has been added to the Method section (see p. 12):

> \textcolor{blue}{Finally, the association between publication year and the possibility of retrieving the data in one of the ways conducted in this project were explored by fitting binary logistic regression models with publication year as predictor and process-reproducibility as dependent variable. We quantified the strength of the association by calculating odds ratios and 95\% confidence intervals based on the profile likelihood. These exploratory analyses were  not pre-registered. Details and results are reported in Supplementary file.}

See the Supplementary file, section “Data availability over years” for full details of the exploratory analyses.

We have also briefly mentioned the results of the exploratory analysis in the Discussion section and have added some temporal expectation when discussing data sharing (see p. 22):

> \textcolor{blue}{A more positive sign comes from the positive association between publication year and the possibility of retrieving the data that was observed in an exploratory analysis in the supplementary materials. This tentatively suggests that data-availability is improving over time. This observation could be related to the existence of well-established meta-analysis reporting guidelines. For instance, the first PRISMA guideline (Moher et al., 2019)} \textcolor{blue}{encouraged meta-analyst to report results of primary studies (e.g. primary effect sizes and their confidence interval through a forest plot, as was a common scenario among the cases included in this project), and the latest PRISMA guideline (Page et al., 2021)} \textcolor{blue}{which puts more emphasis on appropriate data sharing through data files ready for reuse.} At the same time in only 5% of the cases where data were retrieved in our sample were we able to retrieve the data in a machine-readable data file that was ready for reuse (e.g., *csv*, *xlsx*). Most often the data had to be retrieved from files in document format (e.g., *docx*, *pdf*). This forces people who want to reuse the data to manually recode the data, which is an inefficient and error-prone task. Even after partial double coding was carried out, this procedure did not avoid some coding errors, which were only detected by double checking meta-analyses with discrepancies. In our experience, the data retrieval process can be difficult when results are presented in general tables, as it involves matching subsets of these primary data with different meta-analytic results, while is not always clear which studies were used in which meta-analysis reported in a paper. Furthermore, because the tables in manuscript are often generated manually in document file formats (e.g. Word), we observed examples where this introduced another source of error. \textcolor{blue}{The foregoing discussion raises a key point about how time consuming the appraisal of meta-analytic reproducibility currently is, and how efficiency would be improved by having open access to the underlying meta-analytic data in data file formats ready for reuse. The latest PRISMA guidelines, along with some initiatives that promote appropriate data sharing (e.g., Wilkinson et al., 2016)} \textcolor{blue}{have the potential to generate significant improvements in the re-use of meta-analytic data in the years ahead. In this regard, our results provide a useful baseline for future assessments.}

\RC{It strikes me that one of the main outcomes of this project is how much time and effort it must have taken to complete. Is there anyway this could be reported in some way?}

We couldn’t agree more! Unfortunately, we don’t have proper measures of this outcome as the hours invested in this project were not systematically tracked. Still, as we agree this is relevant information, we have mentioned it in the same paragraph as above (p. 22):

> \textcolor{blue}{The foregoing discussion raises a key point about how time consuming the appraisal of meta-analytic reproducibility currently is, and how efficiency would be improved by having open access to the underlying meta-analytic data in data file formats ready for reuse. The latest PRISMA guidelines, along with some initiatives that promote appropriate data sharing (e.g., Wilkinson et al., 2016)} \textcolor{blue}{have the potential to generate significant improvements in the re-use of meta-analytic data in the years ahead. In this regard, our results provide a useful baseline for future assessments.}

\RC{
Minor points:

- Why only clinical psychology? How might this impact things? Having spent a lot of time in clinical psychology research in grad school, my personal experience is that these researchers are slightly less likely to adopt advances in methods (e.g., reproducible code).}

We preferred focusing on a specific research area or subdiscipline because our prior of possible differences between different research areas. We didn’t have priors about direction of these differences. We thought it would be more informative to characterize one subdiscipline rather than to examine several research fields in one study.

We choose clinical psychology for the two main reasons:

-	It is one of the areas that produces the most meta-analyses in psychology.

-	Their direct impact on applied practice

We have also mentioned this as a limitation of the generalizability of the results in the revised manuscript (see p. 25):

> \textcolor{blue}{Finally, we only examined meta-analyses in clinical psychology as this is one of the areas that produces the most meta-analyses in psychology and these meta-analyses have a direct impact on applied practice, but it is unknown to which extent our conclusions generalize to meta-analyses in other sub-disciplines in psychology.}

\RC{-Paragraph 1 on p. 22 has several typos.}

Thanks for checking. Fixed.

\RC{-In the scatterplots, I find the use of + slightly confusing, as it could indicate 2d confidence limits. I suggest x or circles.}

Thanks for the suggestion. We have changed it to `x`.

\RC{-What’s the correlation between error in the summary statistic and error in the heterogeneity statistic?}

The Pearson’s correlation between those error was .172.

We have reported this in the revised manuscript (see p. 18):

>As shown in Figures 5 and 6, the discrepancies found in the heterogeneity statistic $I^2$ are larger than those found in the summary effects and their confidence intervals. \textcolor{blue}{The Pearson's correlation between the summary effect and $I^2$ discrepancies was .172.}

\RC{-Would it be possible to use something other than I2? It has bounding issues that might be affecting results.}

We used I2 because it’s the most reported heterogeneity statistic. Hence it allowed us to carry out a large number of comparisons between original and reproduced results.

\RC{-How is meta-analysis defined? Just when a model has been fit? How many of the meta-analyses are on the same exact data rather than from the same paper?}

Yes, here meta-analysis refers to standard pairwise meta-analytic models.  For clarification we have rephrased the following (see p. 8):

>From these 100 articles, each independent \textcolor{blue} {pairwise meta-analytic model of aggregate data fitted} on at least 10 primary studies was selected

The meta-analyses selected from the same paper were independent, that is based on different data (e.g. different outcomes, timepoints…) based on the criteria explained in the manuscript. However, we don’t have information on possible primary data overlapping between publications, because it’s beyond our research question. It is highly likely that there is some degree of overlap, but we consider it a different (and a really interesting and relevant one) research question.

Thanks again for taking your time providing very useful feedback. We appreciate how your suggestions have improved the manuscript.

# Reviewer \#2

\RC{In this manuscript, the authors assess the analytical reproducibility of a set of meta-analyses. They report obstacles in obtaining the data in a workable format and identify numerical and decision errors in a sizable portion of the meta-analyses.

I think this is an interesting paper that provides compelling arguments that we need to improve meta-analytic reporting. I also commend the authors for preregistering their research plan and sharing their data and materials.
One aspect of the paper I particularly liked was the effort to identify the causes of any identified discrepancies. The authors describe the results of this qualitative procedure on page 16 (lines 3-14). Here, I do have some questions about the procedure and the subsequent conclusions.

- P. 16, line 6: you describe that some discrepancies could be explained by rounding issues. Could you explain this in a bit more detail? Does this mean that there was incorrect rounding in the meta-analyses? And did you count that as correct because it was only a small discrepancy? If so, why? Similarly for the minor reporting errors you mention in line 7: it sounds as if minor errors are not considered issues for the reproducibility. This is a choice that needs to be justified.}

We agree that this could have been more clearly specified. In order to improve our explanation, we think that the clearest way of providing this information is by reporting each of the 15 cases. In this regard, we have added a table in the supplementary file which provides an explanation about each of these 15 cases (see Supplementary file, Qualitative assessment section).

We have added a footnote on p.15 linking to the supplementary file:

>Furthermore, 15 were labelled as \textcolor{blue}{approximately reproduced or reproduced with minor adjustment} in a qualitative check because the discrepancy was probably explained by rounding issues, inverted signs for results (when effect sizes were reported in absolute values) and primary data, minor reporting errors, or minor adjustments in the analytical scheme^[Full details in Supplementary File at (add link)].

\RC{- After the qualitative check, you relabel 15 meta-analyses as reproduced, because you were able to spot the reason for the discrepancy, right? I’d argue that having a good idea why something didn’t reproduce, doesn’t suddenly make the result reproducible. I think labelling these cases as “reproduced with issues” or “approximately reproduced” or something along those lines makes more sense, than simply calling them “reproduced”.}

We agree that these meta-analyses deserve a specific category. In this vein we have made the following change in the manuscript (see p. 15):

>Furthermore, 15 were labelled as \textcolor{blue}{approximately reproduced or reproduced with minor adjustment} in a qualitative check because the discrepancy was probably explained by rounding issues, inverted signs for results (when effect sizes were reported in absolute values) and primary data, minor reporting errors, or minor adjustments in the analytical scheme.

Furthermore, we have remade (old) Figure 6 (currently Figure 4) and now it’s a Sankey plot displaying the whole flow of the reproduction attempts. In this new figure, these 15 cases are labelled also following this recommendation (see p. 17).

\RC{- Abstract: I think it would be insightful to also report percentages of meta-analyses that could be reproduced / had errors in the abstract, instead of only the absolute numbers.}

Agreed. We have added percentages of process-reproducible meta-analyses and of meta-analyses that were still labelled as error after checking for coding errors and qualitative assessments. We just highlighted those percentages in the abstract to avoid misinterpretations of what the other values represent.

\RC{- Figure 1: I don’t really understand the arrows going up from systematic procedure to research question/aims and eligibility criteria. As a matter of fact, I think the whole top part of the figure is somewhat hard to understand. Isn’t the whole process pretty linear? So: rationale - research question/aim - eligibility criteria - systematic procedure? And what do the circles with a vertical line through them between the different systematic procedural steps mean? Shouldn’t these just be arrows? Finally, and this might be a matter of personal preference, but I would switch the columns with the previous literature and the required elements: on the left you would then have the necessary ingredients for the procedure, and on the right the examples of previous literature.}

The arrows going up from the systematic procedure was a mistake, well spotted, thanks! About the top part of the figure, we wanted to point out to the functional relationship between RQ/Aims and eligibility criteria. We agree that could be a bit confusing.

Based on your suggestions we have modified Figure 1 (see p. 6). We have made the following modifications:

-	Now the whole flow is linear.

-	Now all the steps are connected using the same symbol (arrows).

-	We have switched the side columns as you recommended.

\RC{- P. 7: why did you select 100 meta-analyses? Was this (purely) for feasibility reasons or did you also do some sort of power analysis? I think it would be good to add a short justification for this sample size to your paper. Similarly, please (briefly) justify the choice to only include meta-analyses with at least 10 primary studies.}

We tried to keep a reasonable trade-off between informativeness and feasibility. This was based on our own judgment. We agree that this should be reported, so we have added the following text (see p. 8):

>\textcolor{blue}{This sample size was based on our judgement of an acceptable trade-off between informativeness and feasibility.}

On the other hand, we just included meta-analysis with at least 10 primary studies trying to focus on the most relevant meta-analyses of each paper. We also have included a mention of it in the manuscript (see p. 8):

>\textcolor{blue}{This criterion was established to focus on the main meta-analyses of each paper, based on the assumption that the search strategies would be designed to maximise the number of primary studies included that were related to the main aims of the paper.}

\RC{- P. 8, line 50: what is the difference between primary statistics and primary effects and their standard errors?}

This differentiation was made to distinguish between the effects sizes already computed and the data used to compute them. We have specified this in the manuscript as follows (see p. 8):

>In order to be able to reproduce meta-analyses of \textcolor{blue}{aggregate data, primary-level} effects sizes and their associated standard errors are required. These are generally computed from statistics retrieved from the primary studies such as means, standard deviations or sample sizes. We attempted to retrieve the least processed data possible. First, we sought for the statistics \textcolor{blue}{used to compute primary effect sizes (e.g., means, sd)}; second, we sought for the primary effects sizes \textcolor{blue}{already computed} and their standard errors...

\RC{- P. 8, final sentence: shouldn’t this be “confidence limits” instead of confidential limits?}

Thanks, fixed.

\RC{- P. 10: what was the outcome of the reliability checks? How much consensus was there initially?}

We have added a section in the Supplementary file to report the inter-rater reliability. Consensus was high.

\RC{- Table 1: I’m not sure how informative the percentages are next to the N, mainly because you often just refer to a single case. If you choose to keep the percentages in the table, please double check the numbers: by my calculations, there are 8 authors who sent an email with a specific reason (adding up your Ns = 8), but 1 of 8 is 12.5\%, rounding to 13\%, not 12\%.}

Well spotted, thanks! This table was generated by knitr::kable(), using a data frame whose percentage values were computed by base::round(). It appears that base::round() follows the IEC 60559 standard and it uses round-to-even method. We think you pointed this out because the sum of the percentages doesn’t add up to 100. We agree that this could be weird and that the percentages, given the N, aren’t very informative. Hence, we have removed this column from the table (see p. 14).

\RC{- Figure 4A: the labelling “Decision Error: Error / No Error” is confusing. If a data point is classified as “No Error”, is it not an error at all? Or only not a decision error (but still potentially a numerical error)?}

This label only refers to decision errors. We agree that this labelling can be confusing. We have modified it to “Decision Error: Yes/No” (see p. 18).

\RC{- Figure 4A: you could consider making the crosses smaller to increase readability; because of the high overlap of the crosses, it can be hard to spot the “diamonds” of the errors.}

Thanks for the suggestions. We have reduced the size of the crosses and colored the “Decision error” label to increase readability (see p. 18).

\RC{- Figure 4B: classifying upper and lower bounds of a confidence interval as Decision Errors (y/n) is confusing. How can a bound of a confidence interval be a decision error? Please explain this. Furthermore, can it occur that only one of the two bounds of a single CI is a (decision) error? Or are they always classified as a pair? In either case, it is hard to read this plot; in the first case, you can’t see that only one of the bounds was an error (because you don’t know which other value belongs to the pair), and in the second case it gives an overly negative view of the number of errors in the confidence intervals (one error in a confidence interval would then result in two diamonds in the plot).}

They are always classified as a pair. Each pair comes from the same case, and we are classifying cases. You’re right that it could be misleading due to decision errors are displayed twice per case. We have opted for not classifying the confidence limits as decision errors, and to do so only for summary effects (which also come from the same cases, so the total is the same) (see p. 18).

\RC{- Figure 6, panel 1: I would simply call the last category “decision error”, not “numerical and decision error”, this is already implied and by labelling it so explicitly it almost sounds as if there also exist decision errors that are not also numerical errors}

We have made changes in this Figure following suggestions from another reviewer. Now, it is Figure 4 (see p. 16). As you can see, now this category is called only “Decision error” following your recommendation.

\RC{- Page 22, line 10; typo: “which is both inefficient and *an* error-prone task”
- Page 22, line 14: typo: “out” should be “our”
- Page 23, line 17: typo: “issued” should be “issues”}

Thanks for checking! Fixed.

\RC{I’m looking forward to seeing this manuscript in print.

Signed,
Michèle Nuijten}

Thanks again for your useful feedback, we really appreciate your help in improving the manuscript!

# Reviewer \#3

\RC{- I think the reporting of results in the abstract could be imrpoved. Currently it states that 52 reanlysis results showed a discrepancy larger than 5\% from the original results - I think that sounds far more concerning that it actually is given that there were very few 'decision errors' and the authors believe that the reproducibiltiy issues had "little or no effect" on the original conclusions. So I think its worth stating that in the abstract to avoid any miscommunications. The point at which the authors 'qualitative assessment' and the input from the original authors is also not clear in the abstract.}

We agree that this is something that deserves to be mentioned in the abstract. We have added two sentences to the abstract:

>Second, through a multi-stage workflow, we tried to reproduce the main results of each meta-analysis using these data. The original data were retrieved for 146 \textcolor{blue}{(67\%, 146/217)} meta-analyses from different sources. Of these, in the first stage 52 showed a discrepancy larger than 5% in the main results, \textcolor{blue}{in 10 of them, this discrepancy was solved after fixing a coding error and in 15 of them it was solved with minor adjustment or considered approximately reproduced in a qualitative assessment.} In the remaining 27 \textcolor{blue}{(18\%, 27/146)}, different issues were identified in an in-depth review of the papers, such as reporting inconsistencies, lack of some data, or transcription errors. \textcolor{blue}{Nevertheless, the numerical discrepancies produced by these issues were mostly minor, with little or no impact on the conclusions.} Current practices of data sharing in meta-analyses hamper the reusability of meta-analytic data. On the other hand, the implementation of new tools would help to avoid certain errors in the meta-analysis reporting process.

\RC{- The use of "analytic reproduciblity", "process reproducibility", and "outcome reproducibility" seems inconsistent, overlapping, and overall pretty confusing. The title and abstract refer to "analytical reproducibility", but the introduction focuses on  "process reproducibility" and "outcome reproducibility" (analytic reproducibility is not mentioned). Process reproducibility seems to be equated with data availability (or lack of), but I think it was originally intended to refer to all aspects of the analytic pipeline (original data + original code + original software environment, etc). This results in setences like "Based on the availability of primary data, either retrieved directly from the paper or upon request, 146 meta-analyses (67\%, see Fig. 3a) were labelled as process reproducible" This seems odd to me - because some of the cases labelled as "process reproducible" because the data were available, were in fact not reproducible when the authors tried to repeat the analyses. To be fair, I don't think the original sources of these terms defined them particularly helpfully, but I think the onus is on the authors to be clear about what they mean, and how they relate to each other in the present manuscript. For what its worth, I'd recommend just using "analytic reproducibility" to refer to the entire process of trying to repeat the original analyses with the original data to see if you get the same outcome (this seems an accurate description of what the authors did). If this process fails, identify the reason (if possible) which could be an early stage failure (e.g., lack of access to data or code) or a later stage failure (e.g.,  typo in original manuscript). Adding the terms "process reproducibility" and "outcome reproducibility" into the mix seems unnecessary and confusing to me.}

We see your point and agree that consistency in this matter should be improved. Indeed, as you rightly pointed out, in our study process-reproducibility is equated with data availability. As we see it, this is due to our design and the stage of the meta-analysis pipeline we focused on, not to concept itself. So, in our study it’s just a nomenclature matter.

However, we believe this distinction between process/outcome reproducibility is useful for the organization of the previous (and future) literature on meta-analysis reproducibility (as we did in Figure 1). For instance, this distinction allows us to classify studies that review the availability of required elements to reproduce a search strategy of a meta-analysis (e.g., Koffel & Rethlefsen, 2016) in a different category than those that verify the reproduction of the electronic search result (databases output) using those elements.

Regarding the organization of our own results, there would be no difference other than the label used. Therefore, we think it is a good idea to keep those labels for consistency with the terms and literature mentioned in the introduction.

We completely agree that the general consistency on this matter should be improved. To this end, we have clarified the synonymy between process-reproducibility and data-availability in our manuscript, and have made the following changes in the manuscript:

We have changed “analytical reproducibility” to “reproducibility” throughout the manuscript (also in the title and abstract) to avoid confusion and we have highlighted in the introduction (see p. 5) that:

>Figure 1 displays a summary of the basic meta-analysis pipeline through a flowchart, outlining the different stages and listing previous work that has explored different facets of reproducibility of these, as well as a summary of the required elements to be able to reproduce each stage. \textcolor{blue}{In this project we focus on the last stage, related to the statistical analysis and quantitative results of the synthesis.}

We have also restructured the reproducibility success scheme (see p. 11):

>Each meta-analysis was labelled using the following \textcolor{blue}{two-level}^[This hierarchy is a minor deviation from the pre-registered protocol. It is essentially the same and the results are identical. It was introduced to improve clarity.] reproducibility success scheme. \textcolor{blue}{First, each meta-analysis was labelled as: (a) process-reproducible; and (b) not process-reproducible. In our study, not process-reproducible refers to situations where we were unable to access the primary data neither through direct extraction nor upon request}^[Process reproducibility, as described above, could imply a different situation if more conditions need to be met to proceed with the reproduction attempt. In our study, this is equivalent to data availability due to our design and the stage of the meta-analysis pipeline we focused on.]. \textcolor{blue}{Second, those labelled as process-reproducible} were labelled as: (a) reproducible; (b) numerical error; and (c) decision error.

Furthermore, in both figures (Figure 3 and new Figure 4) that display results and mention process reproducibility, data availability was also mentioned in brackets to avoid confusion.

\RC{- In the abstract: "From a random sample of 100 papers containing at least one meta-analysis on the effectiveness of interventions in psychology" - should say "clinical psychology" I think?}

Indeed. Thanks, fixed.

\RC{- Throughout the manuscript there is often reference to stages (e.g., "following the first stage of re-analysis") but I don't recall the different stages being clearly stated anywhere. Perhaps a flow digram would be helpful? I see Figure 6, but this appears to just be about the outcome reproducibility part of the study, and comes too late in the manuscript. This figure also doesn't include the authors "qualitative assessment" - its a bit unclear where that fits into the overall timeline.}

We have remade and moved (old) Figure 6 to a new Figure 4 in response to comments by the other reviewers. The current Figure 4 is a Sankey plot displaying the flow of the reproducibility attempts and it’s presented earlier in the manuscript (see p. 16). We hope that this figure at this place will be more informative about the stages we discuss.

\RC{- "The availability of necessary primary data was checked" - it would be helpful to precisely define "necessary" and "primary" here, especially in the context of meta-analysis. Its not clear to me whether primary means all the individual-unit data from the studies included in the meta-analyses or the summary effect sizes. And its not clear which data are considered necessary or unnecessary.}

We have modified the structure of this paragraph to begin by specifying the necessary data and at what level (see p. 8):

>## Retrieval of primary data
In order to be able to reproduce meta-analyses of \textcolor{blue}{aggregate data, primary-level}^[By primary-level data we mean aggregate data from included primary studies.] effects sizes and their associated standard errors are required. These are generally computed from statistics retrieved from the primary studies such as means, standard deviations or sample sizes. We attempted to retrieve the least processed data possible...

\RC{- "confidential limits" - typo - "confidence"}

Thanks, fixed.

\RC{- Including "data reusability" in the title and abstract is superfluous given that reusing the data is a component of analytic reproducibiltiy and the authors did not try to reuse the data in any other way (the way its written implied to me that there would be some additional assessment of reusability).}

We agree that including “data reusability” could be redundant and, above all, misinterpreted as though some kind of additional reusability analysis had been done. Hence, we have removed it from title and abstract.

\RC{- Some parts of the methods section contain results (see e.g., bottom of page 8) and some parts of the results section contain commentary or opinion I would expect to be in the discussion section (e.g., "a remarkably low reponse rate").}

We have checked for this, and we have removed misplaced statements. Specifically, we have made the following changes:

-	Remove results on data types retrieved in each meta-analysis from Method section (p. 8)

-	Remove the rate of meta-analysis without analysis script code available from Method section (p. 9)

-	Remove “remarkably” from Results section (p. 15)

\RC{- Throughtout, it would be helpful if the numerator and denominator is provided as well as  percentages. The manuscript could be clearer about where the denominator comes from too. For example, "In 141 cases (97\%)" the denominator is presumably 145, but I'm not sure how we got there from the original 217 meta-analyses and I shouldn't have to do that calculation in my head. Another example is this sentence: "Only in 3% of the cases the primary data was retrieved upon request" - is that 3\% of all cases or 3\% of the cases in which data was requested?}

The two examples you mentioned are no longer in the current version. The first one was removed in the revision of results reported in method section (see previous comment). The second one was removed because it was indeed confusing. This 3% is of all cases. The rate of data retrieved from request out of the total of cases in which data was retrieved is not very informative of anything.

Furthermore, we have reviewed the text and added the numerator and denominator in cases where percentages are presented without enough context:

p. 14:

>Although attempts were made to retrieve data for 78 meta-analyses from 25 different papers by emailing the corresponding authors, data was only retrieved for 7 meta-analyses, from 3 different papers \textcolor{blue}{(12\%, 3/25, see Fig. 3c).} For the remaining 71 from 22 different papers, a reply providing some reasons not to share was received in \textcolor{blue}{32\% (8/25, see Fig. 3c)}, whereas no reply was received for the remainder of the meta-analyses.

p.15:

>Data \textcolor{blue}{were retrieved from} tables or forest plots in *pdf* or *docx* format—either in the document itself or in the supplementary materials—\textcolor{blue}{in 92\% (134/146) of the cases.}

p. 18:

>\textcolor{blue}{These examples of inconsistencies in original results or data were found in 4 cases (3\%, 4/146).} These appeared to be typos.

\RC{- Authors were contacted when data were not available, but it seems they were not asked for analysis scripts that were not available, was there a reason for this?}

Good point. There were some reasons for this:

-	Not necessarily all authors of included meta-analyses will actually have an analysis script to share, because many used point and click software.

-	We expected script availability to be very low, and requesting it would have meant sending request for virtually every paper included in our re-analysis

-	We designed an approach to reconstruct the original analysis scheme .

We have mentioned those reasons in the revised manuscript (see p. 10):

>\textcolor{blue}{We designed this procedure to reconstruct the original analytical scheme when the original analysis script was not available instead of trying to request it from the original authors due to: (a) not necessarily all authors of included meta-analyses will actually have an analysis script to share, because many might have used point and click software, and (b) we expected analysis script availability to be very low, and requesting it would have meant sending request for virtually every paper included in our re-analysis.}

\RC{- "Primary-level data and aggregate-level data described above were coded by five members of the group." - this is a bit unclear, it could that the data for each article were independely extracted five times (I dont think that's the intention).}

Thanks for spotting it. We have rephrased this as follows:

>\textcolor{blue}{Data collection procedure was carried out by five of the authors…}

\RC{- It would be interesting to get some sense of how important/influential the assessed meta-analyses are in order to gauge the impact of any reproducibility issues - perhaps include some descriptive data about citation counts?}

Great suggestion, thanks! We have added information on citation count of the papers included. See p. 12 and (new) Figure 2(c):

>\textcolor{blue}{...were cited 108.39 times on average (sd = 151.00; median = 57; interquartile range = 29-128; range = 3-1036)...}

\RC{- There are several sentences where I think its important to report the actual numbers rather than the authors verbal interpretation of the numbers e.g., "Data available in tables or forest plots shared in pdf or docx format –either in the document itself or in the supplementary materials– was found to be highly prevalent" and "This example of inconsistencies in original results was also found in other cases".}

We agree. We have added quantitative information on these cases:

p.15:

>Data \textcolor{blue}{were retrieved from} tables or forest plots in *pdf* or *docx* format—either in the document itself or in the supplementary materials—\textcolor{blue}{in 92\% (134/146) of the cases.}

p. 18:

>\textcolor{blue}{These examples of inconsistencies in original results or data were found in 4 cases (3\%, 4/146).} These appeared to be typos

\RC{- Figure 4 - the caption is cut off. Its difficult to make out error vs no error because of overlapping points, perhaps use colour here?}

Thank you for spotting it. With regards to the scatterplot, we have reduced the size of the crosses and added color to the Decision error label (see p. 18 and 19).

\RC{- "In one of them, the original authors sent back a link to an OSF repository where the original data and analysis script were stored. According to the authors, this link was not reported in the paper by mistake. The script was run on these data and the results were successfully reproduced." - Do the dates in the OSF archive indicate that the files were uploaded before the paper was published?}

Interesting point that we missed checking. It seems that the OSF repository was created just before the paper was accepted (02/06/2019 created, 13/06/2019 accepted). It seems that the OSF repo was created upon request of the journal. We think that this deserves to be mentioned in the manuscript, so we have added the following text (see p.21, footnote 7):

>\textcolor{blue}{According to the repository timeline the project was created on 02/06/2019 and according to the journal’s article history the paper was published on 13/06/2019. It seems that the repository was created as a journal requirement.}

\RC{- The authors responded "No" and "Not Applicable" to these prompts: "Does your paper rely on new or previously unpublished empirical data from your lab?", "If your paper presents new empirical work, does it include the following statement: “We report how we determined our sample size, all data exclusions, all manipulations, and all measures in the study”? It seems to me that both of these apply to the current manuscript (the nove empirical data is the results of the reproducibility assessments).}

We don’t know if it’s possible to modify the form. The most relevant point on your suggestion is related to include a statement about how we determine our sample size. We have included the following statement (see p. 8):

>Of this pool, 100 were randomly selected using a random number generator between 1 and the total number of meta-analyses identified...\textcolor{blue}{This sample size was based on our judgement of an acceptable trade-off between informativeness and feasibility.}
From these 100 articles, each independent \textcolor{blue} {pairwise meta-analytic model of aggregate data fitted} on at least 10 primary studies was selected. In case no meta-analysis reported in a paper had at least 10 studies, the meta-analysis with the highest number of primary studies was selected, which was the case for 29 of the articles included in this report. \textcolor{blue}{This criterion was established to focus on the main meta-analyses of each paper, based on the assumption that the search strategies would be designed to maximise the number of primary studies included that were related to the main aims of the paper.}

\RC{- I may have missed it, but it would be good to see data on when the target articles were published - a histogram in a supplement would do the job.}

Agree. We have added two panels to Figure 2 and one of them is a histogram of the publication year (see p. 13).

Thanks again for taking your time providing very useful feedback. We’re sure your suggestions have improved the manuscript.

### 2023-04-21 manuscript.Rmd
Fixing typos in references to fig3
Revised version

@@
 
+\textcolor{blue}{Additionally, the association between publication year and the possibility of retrieving the data in one of the ways conducted in this project were explored by fitting binary logistic regression models with publication year as predictor and process-reproducibility as dependent variable.
+We quantified the strength of the association by calculating odds ratios and 95% confidence intervals based on profile likelihood.
+These exploratory analyses were carried out a posteriori and therefore were not pre-registered.
+Details and results are reported in Supplementary file.}
+
 # Results
@@
 Based on the availability of primary data, either retrieved directly from the paper or upon request, `r df_process_rep$n[2]` meta-analyses (`r sprintf("%0.0f%%", df_process_rep$perc[2]*100)`, see Fig.
-2a) were labelled as process reproducible.
+3a) were labelled as process reproducible.
 Of these `r df_process_rep$n[2]` meta-analyses, in about half of the cases the primary data was retrieved from a forest plot in the paper itself and in about a third of the cases the primary data was retrieved from supplementary files.
 Only in `r sprintf("%0.0f%%", df_source_primary_data$perc[1]*100)` of the cases the primary data was retrieved upon request (see Fig.
-2b for further details).
+3b for further details).
 Although attempts were made to retrieve data for `r df_process_rep$n[1]+df_source_primary_data$n[1]` meta-analyses from `r sum(df_request$n)` different papers by emailing the corresponding authors, data was only retrieved for `r df_source_primary_data$n[1]` meta-analyses, from `r df_request$n[2]` different papers (`r sprintf("%0.0f%%", df_request$perc[2]*100)`, see Fig.
-2c).
+3c).
 For the remaining `r df_process_rep$n[1]` from `r df_request$n[1] + df_request$n[3]` different papers, a reply providing some reasons not to share was received in `r sprintf("%0.0f%%", df_request$perc[2]*100)` (see Fig 2c), whereas no reply was received for the remainder of the meta-analyses.
@@
 
-For the remaining meta-analyses (about two thirds), we were able to retrieve the data used by the original authors.
-In only 5% of these cases data was shared in a machine-readable data file (e.g., *csv*, *xlsx*), while the data had to be retrieved from files in document format (e.g., *docx*, *pdf*) for the rest of cases.
-This forces people who want to re-use the data to manually recode the data, which is both inefficient and error-prone task.
+\textcolor{blue}{On the other hand, an association between publication year and the possibility of retrieving the data were found in some exploratory analysis.
+This indicated that the more recent the publication of the meta-analysis, the more likely it was to retrieve the data.
+This trend points in a positive direction and could be related to the existence of well-established meta-analysis reporting guidelines.
+For instance, the first PRISMA guideline [@moher2009] encouraged meta-analyst to report results of primary studies (e.g.
+primary effect sizes and their confidence interval through a forest plot, as was a common scenario among the cases included in this project), and the latest PRISMA guideline [@page2021] which puts more emphasis on appropriate data sharing through data files ready for reuse.} However, in our sample, only 5% cases where data were retrieved, we were able to retrieve the data in a machine-readable data file ready for reuse (e.g., *csv*, *xlsx*), while the data had to be retrieved from files in document format (e.g., *docx*, *pdf*) for the rest of cases.
+This forces people who want to reuse the data to manually recode the data, which is both inefficient and error-prone task.
 Even after partial double coding was carried out, this procedure did not avoid some coding errors, which were detected by double checking meta-analyses with discrepancies.
-In out experience, the data retrieval process can be difficult when results are presented in general tables, as it involves matching subsets of these primary data with different meta-analytic results, while is not always clear which studies were used in which meta-analysis reported in a paper.
+In our experience, the data retrieval process can be difficult when results are presented in general tables, as it involves matching subsets of these primary data with different meta-analytic results, while is not always clear which studies were used in which meta-analysis reported in a paper.
 Furthermore, because the tables in manuscript are often generated manually in document file formats (e.g.
 Word), we observed examples where this introduced another source of error.
-There are good guidelines on how to share research data properly [@wilkinson2016], and authors should share data in machine-readable formats.
+\textcolor{blue}{The aforementioned latest PRISMA along with recent initiatives that promote appropriate data sharing [@wilkinson2016] could produce significant improvements the forthcoming years on this matter.
+In this regard, our results are a useful baseline for future assessments.}
 
@@
 
+## Prior versions
+
+A version of this manuscript has been posted as a preprint on PsyArxiv: https://psyarxiv.com/gvqrn/
+
 # References

### 2023-04-21 submission.Rmd
Revised version

--- 2022-11-25 manuscript.Rmd
@@
 ---
-title: "Analytical reproducibility and data reusability of published meta-analyses on clinical psychological
+title: "Reproducibility of published meta-analyses on clinical psychological
   interventions"
-shorttitle: "Meta-analyses reproducibility (PRE-PRINT)"
+shorttitle: "Meta-analyses reproducibility"
 leftheader: "Lopez-Nicolas et al."
@@
    corresponding: yes
-   adress: "Facultad de Psicología, Campus de Espinardo, Universidad de Murcia, edificio n° 31, 30100, Murcia, Spain"
+   address: "Facultad de Psicología, Campus de Espinardo, Universidad de Murcia, edificio n° 31, 30100, Murcia, Spain"
    email: "rlopez@um.es"
@@
 abstract: |
-  Meta-analysis is one of the most useful and powerful research approaches, however, this relevance relies on its credibility.
-In recent years different concerns about the credibility of psychological research have emerged.
-Analytical reproducibility of scientific results could be considered as the minimal threshold of it.
-In this study, our purpose was to assess the analytical reproducibility and data reusability of a set of published meta-analyses.
-From a random sample of 100 papers containing at least one meta-analysis on the effectiveness of interventions in psychology used in a previous study, 217 meta-analyses were selected.
-We first tried to retrieve the original data by recovering a data file, recoding the data from document files (pdf, doc), or on request.
+  Meta-analysis is one of the most useful and powerful research approaches, the relevance of which relies on its credibility.
+However, in recent years different concerns about the credibility of psychological research have emerged.
+Reproducibility of scientific results could be considered as the minimal threshold of it.
+In this study, our purpose was to assess the  reproducibility of a sample of published meta-analyses.
+From a random sample of 100 papers containing at least one meta-analysis on the effectiveness of interventions in clinical psychology, 217 meta-analyses were selected.
+We first tried to retrieve the original data by recovering a data file, recoding the data from document files (pdf, doc), or requesting it from original authors.
 Second, through a multi-stage workflow, we tried to reproduce the main results of each meta-analysis using these data.
-The original data were retrieved for 146 meta-analyses from different sources.
-Of these, in the first stage 52 showed a discrepancy larger than 5% in the main results, in 25 of them, this discrepancy was solved with minor adjustments, or correction of coding errors.
-In the remaining 27, different issues were identified in an in-depth review of the papers, such as reporting inconsistencies, lack of some data, or transcription errors.
-Current practices of data sharing in meta-analyses hamper the reusability of meta-analytic data.
-On the other hand, the implementation of new tools would help to avoid certain errors in the meta-analysis reporting process.
+The original data were retrieved for 146 \textcolor{blue}{(67\%, 146/217)} meta-analyses.
+Of these, 52 showed a discrepancy larger than 5% in the main results in the first stage.
+\textcolor{blue}{For 10 meta-analyses this discrepancy was solved after fixing a coding error and for 15 of them it was solved with minor adjustment or considered approximately reproduced in a qualitative assessment.} In the remaining 27 meta-analyses\textcolor{blue}{(18\%, 27/146)}, different issues were identified in an in-depth review of the papers, such as reporting inconsistencies, lack of data, or transcription errors.
+\textcolor{blue}{Nevertheless, the numerical discrepancies produced by these issues were mostly minor, with little or no impact on the conclusions.} Current practices of data sharing in meta-analyses hamper the reusability of meta-analytic data.
+The implementation of new tools would help to avoid certain errors in the meta-analysis reporting process.
 
@@
 
-class             : "apa7"
+class             : "man"
 output            : papaja::apa6_pdf
@@
    - \captionsetup[table]{textfont={it}, labelfont={bf}, singlelinecheck=false, labelsep=newline}
-   - \captionsetup[figure]{textfont={it}, labelfont={bf}, singlelinecheck=false, labelsep=newline}
+   - \captionsetup[figure]{textfont={footnotesize, it}, labelfont={bf}, singlelinecheck=false, labelsep=newline}
 ---
@@
 Meta-analysis is widely considered as an important approach to evaluate a body of work.
-Given the ongoing growth in the number of scientific publications [@bornmann2021], evidence synthesis approaches -such as meta-analysis- are becoming increasingly relevant for a cumulative science.
-This relevance rests on the credibility of meta-analytic results, which can be threatened by a lack of rigorous application or poor-quality reporting [@gurevitch2018].
+Given the ongoing growth in the number of scientific publications [@bornmann2021], evidence synthesis approaches—such as meta-analysis—are becoming increasingly relevant for a cumulative science.
+This relevance rests on the credibility of meta-analytic results, which can be threatened by a lack of rigorous methodology or poor-quality reporting [@gurevitch2018].
 Given the importance of meta-analyses for evidence-based practice, these threats to their credibility need to be closely monitored.
@@
 Those initiatives showed many failures to replicate or reproduce the published results.
-In this context, the empirical assessment of scientific published results credibility has become a major task for the scientific community.
+In this context, the empirical assessment of the credibility of published results has become a major task for the scientific community.
 
 There are different approaches to the empirical assessment of scientific credibility.
-Reproducibility refers to the attempt to obtain the same results as in the original publication, using the same data and the same analytical procedure.
-Robustness refers to the assessment of the sensitivity of the originally published results and conclusions to variations in the original analytical strategy using the same data.
+Reproducibility refers to the attempt to obtain the same results as in the original publication, using the same data and the same procedure.
+Robustness refers to the assessment of the sensitivity of the originally published results and conclusions to variations in the original procedure using the same data.
 Replicability is a core principle of the scientific method and refers to the fact that the same scientific evidence should be observed when independent researchers try to answer the same research question from the same approach at different moments using different data.
@@
 
-The reproducibility of all published scientific results could be considered as the minimal threshold of scientific credibility [@hardwicke2021].
+The reproducibility of published scientific results could be considered as the minimal threshold of scientific credibility [@hardwicke2021].
 Different approaches can be adopted for the empirical assessment of reproducibility.
 For example @nosek2022 make the distinction between process reproducibility and outcome reproducibility.
-Following this framework, a process reproducibility assessment could be carried out by reviewing the availability of the materials, data, and precise details of the analytical strategy in the report that are required to proceed with the reproduction attempt.
+Following this framework, a process reproducibility assessment could be carried out by reviewing the availability of the materials, data, or precise details of the analytical strategy in the report that are required to proceed with the reproduction attempt.
 An outcome reproducibility assessment can be carried out when the required elements are retrievable by actually reproducing the analyses.
@@
 For example, some process reproducibility assessments have shown an important lack of data availability in machine-readable formats, and an almost complete absence of analysis script code availability [@lopez-nicolas2021; @polanin2020].
-Furthermore, some outcome reproducibility assessments have shown a considerable number of failures when trying to reproduce the primary effect sizes of some published meta-analyses by recollecting primary data from primary studies [@gotzsche2007; @maassen2020; @tendal2009] possibly due to lack of details on how primary effect sizes were selected and computed.
+Furthermore, some outcome reproducibility assessments have shown a considerable number of failures when trying to reproduce the primary effect sizes of some published meta-analyses by recollecting primary data from primary studies [@gotzsche2007; @maassen2020; @tendal2009], possibly due to lack of details on how primary effect sizes were selected and computed.
 In these outcome reproducibility studies, the main task entails reconstructing the original data by retrieving them from the source, namely the included primary studies.
@@
 Figure 1 displays a summary of the basic meta-analysis pipeline through a flowchart, outlining the different stages and listing previous work that has explored different facets of reproducibility of these, as well as a summary of the required elements to be able to reproduce each stage.
+\textcolor{blue}{In this project we focus on the last stage, related to the statistical analysis and quantitative results of the synthesis.}
 
-\begin{figure*}
+\begin{figure}
 \begin{center}
@@
 \end{center}
-\end{figure*}
+\end{figure}
 
-Reproducibility analysis typically uses the original data available from the original authors [e.g., @artner2020; @hardwicke2021; @hardwicke2018].
+Reproducibility analysis \textcolor{blue}{of reported quantitative results} typically uses the original data available from the original authors [e.g., @artner2020; @hardwicke2021; @hardwicke2018].
 This puts the focus of the assessment at factors such as the reusability of the available data, challenges for the reconstruction of the original analysis scheme, reporting errors, etc.
@@
 Only 31% included a data availability statement and only 13% of these included a link to access the data openly, with 23% stating that all relevant data are available in the paper itself, 10% stating that data sharing is not applicable as no datasets were generated, 8% stating that data sharing is not applicable as the data is drawn from already published literature, and 42% stating that data were available upon request.
-It is surprising that, even just considering meta-analyses that included a data availability statement, the authors of these meta-analysis  assume that such practices do not apply to meta-analyses or that the data in the article itself is sufficient.
+It is surprising that, even just considering meta-analyses that included a data availability statement, the authors of these meta-analysis  assume that such practices do not apply to meta-analyses, or that the data in the article itself is sufficient.
 
@@
 Second, we verified the outcome reproducibility of the meta-analyses that were process-reproducible using the available data.
-Where previous work focussed on the reproducibility of primary effect sizes, we explored meta-analysis outcome reproducibility using the primary effects sizes already coded by the original authors.
+Where previous work focused on the reproducibility of primary effect sizes, we explored meta-analysis outcome reproducibility using the primary effects sizes already coded by the original authors.
 
@@
 The full search strategies and a summary of the screening process are available at: https://osf.io/z5vrn/, and the workflow of the random selection process is available at: https://osf.io/cp293/.
-From these 100 articles, each independent reported meta-analysis with at least 10 primary studies was selected.
+\textcolor{blue}{This sample size was based on our judgement of an acceptable trade-off between informativeness and feasibility.}
+From these 100 articles, each independent \textcolor{blue} {pairwise meta-analytic model of aggregate data fitted} on at least 10 primary studies was selected.
 In case no meta-analysis reported in a paper had at least 10 studies, the meta-analysis with the highest number of primary studies was selected, which was the case for `r n_mas_less_10` of the articles included in this report.
-Our unit of analysis was each independent meta-analysis selected under these criteria.
-A total of `r n_mas_total` independent meta-analyses were selected.
+\textcolor{blue}{This criterion was established to focus on the main meta-analyses of each paper, based on the assumption that the search strategies would be designed to maximise the number of primary studies included that were related to the main aims of the paper.}
+
+Our unit of analysis was each independent meta-analysis selected under these criteria. A total of `r n_mas_total` independent meta-analyses were selected.
 
 ## Retrieval of primary data
-The availability of necessary primary data was checked.
-First, we searched for machine-readable data files through links leading to third-party repositories or in supplementary material hosted by the journal.
+In order to be able to reproduce meta-analyses of \textcolor{blue}{aggregate data, primary-level}^[By primary-level data we mean aggregate data from included primary studies.] effects sizes and their associated standard errors are required.
+These are generally computed from statistics retrieved from the primary studies such as means, standard deviations or sample sizes.
+We attempted to retrieve the least processed data possible.
+First, we sought for the statistics \textcolor{blue}{used to compute primary effect sizes (e.g., means, sd)}; second, we sought for the primary effects sizes \textcolor{blue}{already computed} and their standard errors (or, alternatively, the sampling variances): finally, we sought for the primary effects sizes and their confidence limits, from which the standard errors were approximated as follows:
+
+$$se_i = (\frac{UB_i - LB_i}{2z_{\alpha/2}})$$
+
+with $se_i$ being the standard error of the ith effect size, $UB_i$ and $LB_i$ the upper and lower confidence limits of confidence interval for the ith effect size, and $z_{\alpha/2}$ the $(1 - {\alpha/2})\%$ percentile of the standard normal distribution (usually, $z_{\alpha/2} = 1.96$ assuming a two-sided 95% confidence interval).
+
+\textcolor{blue}{On the other hand, efforts were also made to retrieve the most reusable data possible.} First, we searched for machine-readable data files through links leading to third-party repositories or in supplementary material hosted by the journal.
 Second, we looked for available data through tables or forest plots in the meta-analytic report itself, or in supplementary material.
@@
 
-In order to be able to reproduce meta-analyses, primary effects and their associated standard errors are required.
-These are generally computed from primary statistics retrieved from the primary studies such as means, standard deviations or sample sizes.
-We attempted to retrieve the least processed data possible.
-First, we sought for the primary statistics, recovered in `r sprintf("%0.0f%%", df_type_of_data$perc[3] * 100)` of the cases.
-Second, we sought for the primary effects and their standard errors (or, alternatively, the sampling variances), recovered in `r sprintf("%0.0f%%", df_type_of_data$perc[2] * 100)` of the cases.
-Finally, we sought for the primary effects and their confidential limits, recovered in `r sprintf("%0.0f%%", df_type_of_data$perc[1] * 100)` of the cases, from which the standard errors were approximated as follows:
-
-$$se_i = (\frac{UB_i - LB_i}{2z_{\alpha/2}})$$
-
-with $se_i$ being the standard error of the ith effect size, $UB_i$ and $LB_i$ the upper and lower confidence limits of confidence interval for the ith effect size, and $z_{\alpha/2}$ the $1 - z_{\alpha/2}$ quantile of the standard normal distribution (usually, $z_{\alpha/2} = 1.96$ assuming a two-sided 95% confidence interval).
-
 ## Reconstructing the original analytical scheme
 To proceed with reproducibility attempts of the meta-analyses that were labelled as process reproducible, we first looked for the availability of the original analysis script.
-When it was available, analytical reproducibility was checked by rerunning the original script on the associated primary data.
-In `r df_process_rep$n[2] -  n_mas_w_script` cases (`r sprintf("%0.0f%%", 100-((n_mas_w_script/df_process_rep$n[2]) * 100))`), the analysis script code was not available.
-In these cases we tried to reconstruct the original analytical scheme using the technical details reported in the paper.
+When it was available, reproducibility was checked by rerunning the original script on the associated primary data.
+When it was not available, we tried to reconstruct the original analytical scheme using the technical details reported in the paper.
 Specifically, we collected information on: (a) the meta-analytic model originally assumed; (b) the weighting scheme; (c) the between-studies variance estimator; (d) the method used to compute the confidence interval; and (e) the software used to perform the meta-analysis.
@@
 If the software used was not reported, we inferred this information from the default settings of the most used software in the sample, which was *Comprehensive Meta-Analysis*.
+\textcolor{blue}{We designed this procedure to reconstruct the original analytical scheme when the original analysis script was not available instead of trying to request it from the original authors due to: (a) not necessarily all authors of included meta-analyses will actually have an analysis script to share, because many might have used point and click software, and (b) we expected analysis script availability to be very low, and requesting it would have meant sending request for virtually every paper included in our re-analysis.}
 
@@
 ## Data collection procedure 
-Primary-level data and aggregate-level data described above were coded by five members of the group.
-At a first pilot stage, a random sample of five articles of the total pool was independently coded by the five members and, subsequently, in a series of meetings, disagreements between the coders were resolved by consensus.
+\textcolor{blue}{Data collection procedure was carried out by five of the authors.} At a first pilot stage, a random sample of five articles of the total pool was independently coded by the five members and, subsequently, in a series of meetings, disagreements between the coders were resolved by consensus.
 Next, the initial pool of 100 included articles was split among four coders, 25 articles each.
@@
 Disagreements were resolved by consensus and by double-checking the original materials.
+\textcolor{blue}{Details about inter-coder agreement are reported in the Supplementary file.}
 
 ## Reproducibility outcomes
-Each meta-analysis was labelled using the following reproducibility success scheme: (a) reproducible; (b) not process-reproducible; (c) numerical error, and (d) decision error.
-Not process-reproducible refers to situations where we were unable to access the primary data neither through direct extraction nor upon request.
+Each meta-analysis was labelled using the following \textcolor{blue}{two-level}^[This hierarchy is a minor deviation from the pre-registered protocol.
+It is essentially the same and the results are identical.
+It was introduced to improve clarity.] reproducibility success scheme.
+\textcolor{blue}{First, each meta-analysis was labelled as: (a) process-reproducible; and (b) not process-reproducible.
+In our study, not process-reproducible refers to situations where we were unable to access the primary data neither through direct extraction nor upon request}^[Process reproducibility, as described above, could imply a different situation if more conditions need to be met to proceed with the reproduction attempt.
+In our study, this is equivalent to data availability due to our design and the stage of the meta-analysis pipeline we focused on.].
+\textcolor{blue}{Second, those labelled as process-reproducible} were labelled as: (a) reproducible; (b) numerical error; and (c) decision error.
 Similar to previous studies (Artner et al., 2020; Hardwicke et al., 2018, 2021) an index of numerical error was computed (see Protocol https://osf.io/tq4uf/).
@@
 
-We focus on analytical reproducibility of summary effects, their confidence bounds and the result of the null hypothesis significance test.
-Secondarily, we also assessed analytical reproducibility of other synthesis methods such as heterogeneity statistics.
+We focus on reproducibility of summary effects, their confidence bounds and the result of the null hypothesis significance test.
+Secondarily, we also assessed reproducibility of other synthesis methods such as heterogeneity statistics.
 
 ## Reproducibility checks workflow 
-Analytical reproducibility checks were carried out at different stages.
+Reproducibility checks were carried out at different stages.
 First, through reported analytic details or script code.
@@
 
-Finally, for meta-analyses that remained labelled as non-reproducible, an email was sent to the corresponding author of the associated paper explaining our aims, our approach, and our results regarding his/her meta-analysis and requesting additional information that could explain the mismatch between the original reported results and the reproduced results.
+Additionally, for meta-analyses that remained labelled as non-reproducible, an email was sent to the corresponding author of the associated paper explaining our aims, our approach, and our results regarding his/her meta-analysis and requesting additional information that could explain the mismatch between the original reported results and the reproduced results.
 We tried to solve the reproducibility issues within a month after the request and we updated the label accordingly.
+
+\textcolor{blue}{Finally, the association between publication year and the possibility of retrieving the data in one of the ways conducted in this project were explored by fitting binary logistic regression models with publication year as predictor and process-reproducibility as dependent variable.
+We quantified the strength of the association by calculating odds ratios and 95\% confidence intervals based on the profile likelihood.
+These exploratory analyses were  not pre-registered.
+Details and results are reported in Supplementary file.}
 
@@
 From the 100 included papers, `r n_mas_total` independent meta-analyses were selected following the criteria explained above.
-These meta-analyses included `r round(k_mean, 2)` primary studies on average (`r sprintf("sd = %0.2f; median = %0.0f; interquartile range = %0.0f-%0.0f; range = %0.0f-%0.0f)", k_sd, k_median, k_q1, k_q3, range[1], range[2])`).
-Figure 2 displays the distribution of number of primary studies among the meta-analyses included in our sample.
-Original results and characteristics of these meta-analyses are available at: https://osf.io/8jzbk
+These meta-analyses included `r round(k_mean, 2)` primary studies on average (`r sprintf("sd = %0.2f; median = %0.0f; interquartile range = %0.0f-%0.0f; range = %0.0f-%0.0f)", k_sd, k_median, k_q1, k_q3, range[1], range[2])`), \textcolor{blue}{and were cited `r round(cc_mean, 2)` times on average (`r sprintf("sd = %0.2f; median = %0.0f; interquartile range = %0.0f-%0.0f; range = %0.0f-%0.0f)", cc_sd, cc_median, cc_q1, cc_q3, cc_range[1], cc_range[2])`}^[Citation counts were retrieved from CrossRef API using the *rcrossref* package [@rcrossref].
+For two cases in which CrossRef did not return data, citation counts were consulted in Google Scholar.
+Both queries were done on 20/03/2023.].
+Figure 2 displays the distribution of number of primary studies among the meta-analyses included in our sample \textcolor{blue}{(panel A), the publication year distribution among the papers included in our sample (panel B) as well as the citation count distribution of those papers (panel C).} Original results and characteristics of these meta-analyses are available at: https://osf.io/8jzbk
 
-``` {r, fig.width = 6, fig.height=6, fig.cap="Distribution of the number of primary studies included in each of the meta-analyses.
+``` {r, fig.width = 12, fig.height=4, fig.cap="Distribution of (a) the number of primary studies included in each of the meta-analyses; (b) the publication year of the included papers; (c) citation count of the included papers.
 Vertical blue dotted lines represent the first quartile, median, and third quartile, respectively."}
 
-hist_primary_studies
+figure2
 
@@
 Based on the availability of primary data, either retrieved directly from the paper or upon request, `r df_process_rep$n[2]` meta-analyses (`r sprintf("%0.0f%%", df_process_rep$perc[2]*100)`, see Fig.
-2a) were labelled as process reproducible.
-Of these `r df_process_rep$n[2]` meta-analyses, in about half of the cases the primary data was retrieved from a forest plot in the paper itself and in about a third of the cases the primary data was retrieved from supplementary files.
-Only in `r sprintf("%0.0f%%", df_source_primary_data$perc[1]*100)` of the cases the primary data was retrieved upon request (see Fig.
-2b for further details).
-Although attempts were made to retrieve data for `r df_process_rep$n[1]+df_source_primary_data$n[1]` meta-analyses from `r sum(df_request$n)` different papers by emailing the corresponding authors, data was only retrieved for `r df_source_primary_data$n[1]` meta-analyses, from `r df_request$n[2]` different papers (`r sprintf("%0.0f%%", df_request$perc[2]*100)`, see Fig.
-2c).
-For the remaining `r df_process_rep$n[1]` from `r df_request$n[1] + df_request$n[3]` different papers, a reply providing some reasons not to share was received in `r sprintf("%0.0f%%", df_request$perc[2]*100)` (see Fig 2c), whereas no reply was received for the remainder of the meta-analyses.
+3a) were labelled as process reproducible.
+Of these `r df_process_rep$n[2]` meta-analyses, in about half of the cases the primary data was retrieved from a forest plot in the paper itself and in about a third of the cases the primary data was retrieved from supplementary files (see Fig.
+3b for further details).
+Although attempts were made to retrieve data for `r df_process_rep$n[1]+df_source_primary_data$n[1]` meta-analyses from `r sum(df_request$n)` different papers by emailing the corresponding authors, data was only retrieved for `r df_source_primary_data$n[1]` meta-analyses, from `r df_request$n[2]` different papers (`r sprintf("%0.0f%%, %0.0f/%0.0f", df_request$perc[2]*100, df_request$n[2], sum(df_request$n))`, see Fig.
+3c).
+For the remaining `r df_process_rep$n[1]` from `r df_request$n[1] + df_request$n[3]` different papers, a reply providing some reasons not to share was received in `r sprintf("%0.0f%% (%0.0f/%0.0f,  see Fig 3c)", df_request$perc[3]*100, df_request$n[3], sum(df_request$n))`, whereas no reply was received for the remainder of the meta-analyses.
 Table 1 summarises the different reasons corresponding authors given when data was not provided upon request.
@@
   booktabs = TRUE,
-  col.names = c("Reason", "N", "%"),
-  align = c("l", "c", "c"),
+  col.names = c("Reason", "N"),
+  align = c("l", "c"),
   caption = "Reasons given when data was not received upon request."
   ) %>% 
-    column_spec(1, width = "7cm")
+    column_spec(1, width = "16cm")
 
@@
 ## Challenges faced retrieving primary data
-In most cases, when the meta-analytic data was available, it was shared in document formats, as previously reported.
-Data available in tables or forest plots shared in *pdf* or *docx* format –either in the document itself or in the supplementary materials– was found to be highly prevalent.
+In most cases, when the meta-analytic data was available, it was shared in document formats.
+Data \textcolor{blue}{were retrieved from} tables or forest plots in *pdf* or *docx* format—either in the document itself or in the supplementary materials—\textcolor{blue}{in} `r sprintf("%0.0f%% (%0.0f/%0.0f)", (df_source_primary_data$perc[3]+df_source_primary_data$perc[4]+df_source_primary_data$perc[6])*100, df_source_primary_data$n[3]+df_source_primary_data$n[4]+df_source_primary_data$n[6], sum(df_source_primary_data$n))` \textcolor{blue}{of the cases}.
 This required a manual recoding of the primary data to be able to reuse them.
@@
 There were only `r df_source_primary_data$n[2]` meta-analyses (from `r words(sum(df_data_downloaded$Item))` different papers) of the `r df_process_rep$n[2]` meta-analyses labelled as process reproducible (`r sprintf("%0.0f%%", df_source_primary_data$perc[2]*100)`), where the task of retrieving the data required simply downloading the data in an machine-readable data file format.
-On the other hand, as shown in Figure 3c, when the necessary data was not available, retrieving it upon request to the original authors led to a remarkably low reponse rate.
+On the other hand, as shown in Figure 3c, when the necessary data was not available, retrieving it upon request to the original authors led to a low response rate.
 
-``` {r, fig.env = "figure*", fig.width = 10, fig.height=11, fig.cap="Percentage of (a) process-reproducible meta-analyses; (b) different types of sources of original data; and (c) data request results.", out.width = "100%"}
+``` {r, fig.width = 10, fig.height=11, fig.cap="Percentage of (a) process-reproducible meta-analyses; (b) different types of sources of original data; (c) data request results."}
 
@@
 As mentioned above, in `r filter(df_script, script == 1)$n` of these meta-analyses (`r sprintf("%0.0f%%", filter(df_script, script == 1)$n/sum(df_script$n)*100)`), all from the same published article, the original script code was available.
-Therefore, in these five cases, analytical reproducibility was checked running the original analysis script on the original primary data.
+Therefore, in these five cases, outcome reproducibility was checked running the original analysis script on the original primary data.
 In the remaining cases, the original analytical framework was reconstructed as explained in the method section.
+Figure 4 summarises the results of the whole process of outcome reproducibility assessment.
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=\textwidth]{results/Figure 4.png}
+
+\caption{Results of the different stages carried out in the evaluation of the outcome reproducibility. 
+}
+
+\label{fig:fig4}
+\end{center}
+\end{figure}
+
 ```{r first_stage, include=FALSE}
@@
 After this, `r nrow(filter(df_to_reanalyse, numerical_error != "error"))` were re-labelled as reproduced and `r nrow(filter(df_to_reanalyse, numerical_error == "error"))` still had relevant discrepancies.
-Furthermore, `r nrow(filter(df_mas_revised, qualitative_check == "rep"))` were labelled as reproduced in the qualitative check because the discrepancy was probably explained by rounding issues, inverted signs for results (where effect sizes were reported in absolute values) and primary data, minor reporting errors, or minor adjustments in the analytical scheme.
+Furthermore, `r nrow(filter(df_mas_revised, qualitative_check == "rep"))` were labelled as \textcolor{blue}{approximately reproduced or reproduced with minor adjustment} in a qualitative check because the discrepancy was probably explained by rounding issues, inverted signs for results (when effect sizes were reported in absolute values) and primary data, minor reporting errors, or minor adjustments in the analytical scheme^[Full details in Supplementary File].
 In the remaining `r nrow(filter(df_mas_revised, qualitative_check == "request_information"))`, and in the `r nrow(filter(df_to_reanalyse, numerical_error == "error"))` re-analysed again without success, some issues or relevant discrepancies without apparent explanation were found.
+Figure 5 displays a scatterplot showing the consistency between the original and reproduced summary effect size and their confidence bounds of these `r nrow(df_to_scatter)` meta-analyses. 
+Additionally, as a secondary analysis, the reproducibility of the $I^2$ heterogeneity statistic was explored.
+Figure 6 displays a scatterplot showing the consistency between the original and reproduced $I^2$ statistics.
+As shown in Figures 5 and 6, the discrepancies found in the heterogeneity statistic $I^2$ are larger than those found in the summary effects and their confidence intervals.
+\textcolor{blue}{The Pearson's correlation between the summary effect and $I^2$ discrepancies was .172.} The lack of precision of the available data (rounded data) or incomplete information on aspects such as the tau-squared estimator applied seem to have a substantial impact on the reproducibility of this result.
 
-Figure 4 displays a scatterplot showing the consistency between the original and reproduced summary effect size and their confidence bounds of these `r nrow(df_to_scatter)` meta-analyses. 
-Additionally, as a secondary analysis, the reproducibility of the $I^2$ heterogeneity statistic was explored.
-Figure 5 displays a scatterplot showing the consistency between the original and reproduced $I^2$ statistics.
-As shown in Figures 4 and 5, the discrepancies found in the heterogeneity statistic $I^2$ are larger than those found in the summary effects and their confidence intervals.
-The lack of precision of the available data (rounded data) or incomplete information on aspects such as the tau-squared estimator applied seem to have a substantial impact on the reproducibility of this result.
-
-``` {r, fig.width = 7, fig.height=14, fig.cap="Scatterplot displaying the reproduced values as a function of the original values classified by whether or not decision error was found.
+``` {r, fig.width = 4, fig.height=8, fig.cap="Scatterplot displaying the reproduced values as a function of the original values classified by whether or not decision error was found.
 Only the results of the 52 meta-analyses with a discrepancy of more than 5% identified in the first stage are displayed, but with the corrections made in the second stage.
@@
 For (b) the colours represent lower or upper bound of the confidence interval."}
-figure4
+figure5
 
@@
 
-``` {r, fig.width = 7, fig.height=7, fig.cap="Scatterplot displaying the reproduced values as a function of the original values classified by whether or not decision error was found.
+``` {r, fig.width = 4.5, fig.height=4.5, fig.cap="Scatterplot displaying the reproduced values as a function of the original values classified by whether or not decision error was found.
 Only the results of the 52 meta-analyses with a discrepancy of more than 5% identified in the first stage are displayed, but with the corrections made in the second stage.
-The values displayed are $I^2$ hetorogeneity statistics.
-The size of the crosses is function of the discrepancy in the summary effect."}
-figure5
+The values displayed are $I^2$ heterogeneity statistics.
+The size of the crosses is a function of the discrepancy in the summary effect."}
+figure6
 
@@
 Furthermore, inconsistencies in the original summary effect reported were found between the results reported in abstract and the results reported in the main text and the forest plot.
-This example of inconsistencies in original results was also found in other cases.
 Also, in a paper where primary data were available in both a table and a forest plot, minor inconsistencies were found between the primary data of the table and the forest plot.
-These appeared to be typos.
+\textcolor{blue}{These examples of inconsistencies in original results or data were found in 4 cases (3\%, 4/146).} These appeared to be typos.
 Furthermore, some inconsistencies were found with respect to the number of primary studies included in each meta-analysis.
@@
 These `r nrow(df_to_rev2)` meta-analyses were from `r sum(df_success_request$n)` different papers.
-Therefore, `r sum(df_success_request$n)` clarification requests with information about the study aims, methods and preliminary results were sent to the corresponding authors of the original articles.
+Therefore, `r sum(df_success_request$n)` clarification requests with information about the study aims, methods, and preliminary results were sent to the corresponding authors of the original articles.
 A reply was received in only `r df_success_request$n[2]`  of the `r sum(df_success_request$n)` cases.
-In one of them, the original authors sent back a link to an OSF repository where the original data and analysis script were stored.
+In one of them, the original authors sent back a link to an OSF repository^[According to the repository timeline the project was created on 02/06/2019 and according to the journal's article history the paper was published on 13/06/2019.
+It seems that the repository was created as a journal requirement] where the original data and analysis script were stored.
 According to the authors, this link was not reported in the paper by mistake.
@@
 
-Figure 6 summarises the results of the whole process of outcome reproducibility assessment.
-
-\begin{figure*}
-\begin{center}
-\includegraphics[width=\textwidth]{results/Figure 6.png}
-
-\caption{Results of the different stages carried out in the evaluation of the outcome reproducibility. 
-}
-
-\label{fig:fig6}
-\end{center}
-\end{figure*}
-
 # Discussion 
-The main aim of this study was to examine the analytical reproducibility of a sample of published meta-analyses on the effectiveness of clinical psychology interventions.
+The main aim of this study was to examine the reproducibility of a sample of published meta-analyses on the effectiveness of clinical psychology interventions.
 We analyzed the availability and reusability of original data and, assessed the reproducibility of the published results using these retrieved original data, and tried to reconstruct the original analysis plan.
@@
 Even when we interpret data availability in the broad sense (i.e.
-retrieving data from tables and figures when no data file was available), for about a third of the included meta-analyses no data was available.
+retrieving data from tables and figures when no data file was available), for about a third of the included meta-analyses no data were available.
 In these cases, attempts were made to obtain the data on request to the corresponding author, with little success.
 Authors only shared data in 12% of the requests that were made.
-This result is in line with what was found in a recent study where data availability statements from a set of primary studies were analysed [@gabelica2022].Where 42% of primary studies in @gabelica2022 reported data was available on request (and identical percentage was found in @page2022 for meta-analyses), only 6.8% of the authors shared the underlying data when requested.
+This result is in line with what was found in a recent study where data availability statements from a set of primary studies were analysed [@gabelica2022].
+Although 42% of primary studies in @gabelica2022 reported data were available on request (an identical percentage was found in @page2022 for meta-analyses), only 6.8% of the authors shared the underlying data when requested.
 Even though it is common to see authors state data is available on request, actually obtaining the data on request seems highly challenging.
@@
 Several repositories (e.g., OSF, GitHub, Zenodo, Figshare) are available for researchers to openly share the data associated with published results.
-On-request availability has proven to be inadequate, and with the availability of data repositories is no longer necessary.
+On-request availability has proven to be inadequate, and with the availability of data repositories it is no longer necessary.
 Journals publishing meta-analyses should require that authors share the underlying data in a public data repository.
 
-For the remaining meta-analyses (about two thirds), we were able to retrieve the data used by the original authors.
-In only 5% of these cases data was shared in a machine-readable data file (e.g., *csv*, *xlsx*), while the data had to be retrieved from files in document format (e.g., *docx*, *pdf*) for the rest of cases.
-This forces people who want to re-use the data to manually recode the data, which is both inefficient and error-prone task.
-Even after partial double coding was carried out, this procedure did not avoid some coding errors, which were detected by double checking meta-analyses with discrepancies.
-In out experience, the data retrieval process can be difficult when results are presented in general tables, as it involves matching subsets of these primary data with different meta-analytic results, while is not always clear which studies were used in which meta-analysis reported in a paper.
+\textcolor{blue}{A more positive sign comes from the positive association between publication year and the possibility of retrieving the data that was observed in an exploratory analysis in the supplementary materials.
+This tentatively suggests that data-availability is improving over time.
+This observation could be related to the existence of well-established meta-analysis reporting guidelines.
+For instance, the first PRISMA guideline} [@moher2009] \textcolor{blue}{encouraged meta-analyst to report results of primary studies (e.g.
+primary effect sizes and their confidence interval through a forest plot, as was a common scenario among the cases included in this project), and the latest PRISMA guideline} [@page2021] \textcolor{blue}{which puts more emphasis on appropriate data sharing through data files ready for reuse.} At the same time in only 5% of the cases where data were retrieved in our sample were we able to retrieve the data in a machine-readable data file that was ready for reuse (e.g., *csv*, *xlsx*).
+Most often the data had to be retrieved from files in document format (e.g., *docx*, *pdf*).
+This forces people who want to reuse the data to manually recode the data, which is an inefficient and error-prone task.
+Even after partial double coding was carried out, this procedure did not avoid some coding errors, which were only detected by double checking meta-analyses with discrepancies.
+In our experience, the data retrieval process can be difficult when results are presented in general tables, as it involves matching subsets of these primary data with different meta-analytic results, while is not always clear which studies were used in which meta-analysis reported in a paper.
 Furthermore, because the tables in manuscript are often generated manually in document file formats (e.g.
 Word), we observed examples where this introduced another source of error.
-There are good guidelines on how to share research data properly [@wilkinson2016], and authors should share data in machine-readable formats.
+\textcolor{blue}{The foregoing discussion raises a key point about how time consuming the appraisal of meta-analytic reproducibility currently is, and how efficiency would be improved by having open access to the underlying meta-analytic data in data file formats ready for reuse.
+The latest PRISMA guidelines, along with some initiatives that promote appropriate data sharing} [e.g.
+@wilkinson2016] \textcolor{blue}{have the potential to generate significant improvements in the re-use of meta-analytic data in the years ahead.
+In this regard, our results provide a useful baseline for future assessments.}
 
@@
 Only in five meta-analyses (3%, all from the same paper), was the original script openly available.
-In most cases, the original analyses were reconstructed from the description provided in the paper itself, which was not always rich in detail, so that many of these computational details had to be inferred from the default settings of the software authors used.
+In most cases, the original analyses were reconstructed from the description provided in the paper itself, which was not always rich in detail, so many of these computational details had to be inferred from the default settings of the software authors used.
 The availability of analysis scripts often shows similar rates, both in meta-analyses [@page2022; @polanin2020] and in primary research [@hardwicke2020; @hardwicke2022].
@@
 
-Despite these difficulties, we were able to recover the original data and reconstruct the original analysis approach, for 146 meta-analyses, for which the analytical reproducibility of the results was assessed.
-These attempts at analytical reproduction went through several stages as explained above, trying to minimize the impact of possible coding errors, and requesting clarifications from the original authors.
+Despite these difficulties, we were able to recover the original data and reconstruct the original analysis approach, for 146 meta-analyses, for which the reproducibility of the results was assessed.
+These attempts went through several stages as explained above, trying to minimize the impact of possible coding errors, and requesting clarifications from the original authors.
 Nevertheless, even with these efforts, some discrepancies remained in the results.
-We identified different issued that hindered our reproducibility attempts.
+We identified different issues that hindered our reproducibility attempts.
 For example, in some cases internal discrepancies were found in the paper itself (e.g., text-figure discrepancies, text-abstract, or text-table discrepancies).
@@
 Some of the problems identified could be explained by typos.
-Currently, there are tools that facilitate the production of so-called reproducible manuscripts, such as the R packages *kintr* [@xie2022], *rmarkdown* [@allaire2022], and *papaja* [@aust2022].
+Currently, there are tools that facilitate the production of so-called reproducible manuscripts, such as the R packages *knitr* [@xie2022], *rmarkdown* [@allaire2022], and *papaja* [@aust2022].
 A reproducible manuscript embeds analysis code, data and results reporting in a single document, extracting and reporting the results from the output of the computational process itself, avoiding error-prone manual transcriptions.
@@
 Because this cut-off is arbitrary, we have tried to focus more on possible issues in the results that fell above this margin, than on establishing a exact ratio of non-reproduced meta-analyses based on this arbitrary cut-off.
+\textcolor{blue}{Finally, we only examined meta-analyses in clinical psychology as this is one of the areas that produces the most meta-analyses in psychology and these meta-analyses have a direct impact on applied practice, but it is unknown to which extent our conclusions generalize to meta-analyses in other sub-disciplines in psychology.}
 

### 2023-04-21 submission.tex
Revised version

--- 2022-11-25 manuscript.tex
@@
 \documentclass[
-  ,apa7,floatsintext]{apa6}
+  ,man,floatsintext]{apa6}
 \usepackage{amsmath,amssymb}
@@
 \captionsetup[table]{textfont={it}, labelfont={bf}, singlelinecheck=false, labelsep=newline}
-\captionsetup[figure]{textfont={it}, labelfont={bf}, singlelinecheck=false, labelsep=newline}
+\captionsetup[figure]{textfont={footnotesize, it}, labelfont={bf}, singlelinecheck=false, labelsep=newline}
 \ifLuaTeX
@@
 \hypersetup{
-  pdftitle={Analytical reproducibility and data reusability of published meta-analyses on clinical psychological interventions},
+  pdftitle={Reproducibility of published meta-analyses on clinical psychological interventions},
   pdfauthor={Rubén López-Nicolás1, Daniel Lakens2, Jose A. López-López1, Maria Rubio-Aparicio3, Alejandro Sandoval-Lentisco1, Carmen López-Ibáñez1, Desirée Blázquez-Rincón1, \& Julio Sánchez-Meca1},
@@
 
-\title{Analytical reproducibility and data reusability of published meta-analyses on clinical psychological interventions}
+\title{Reproducibility of published meta-analyses on clinical psychological interventions}
 \author{Rubén López-Nicolás\textsuperscript{1}, Daniel Lakens\textsuperscript{2}, Jose A.
@@
 
-\shorttitle{Meta-analyses reproducibility (PRE-PRINT)}
+\shorttitle{Meta-analyses reproducibility}
 
@@
 
-Correspondence concerning this article should be addressed to Rubén López-Nicolás. E-mail: \href{mailto:rlopez@um.es}{\nolinkurl{rlopez@um.es}}
+Correspondence concerning this article should be addressed to Rubén López-Nicolás, Facultad de Psicología, Campus de Espinardo, Universidad de Murcia, edificio n° 31, 30100, Murcia, Spain.
+E-mail: \href{mailto:rlopez@um.es}{\nolinkurl{rlopez@um.es}}
 
@@
 \abstract{%
-Meta-analysis is one of the most useful and powerful research approaches, however, this relevance relies on its credibility.
-In recent years different concerns about the credibility of psychological research have emerged.
-Analytical reproducibility of scientific results could be considered as the minimal threshold of it.
-In this study, our purpose was to assess the analytical reproducibility and data reusability of a set of published meta-analyses.
-From a random sample of 100 papers containing at least one meta-analysis on the effectiveness of interventions in psychology used in a previous study, 217 meta-analyses were selected.
-We first tried to retrieve the original data by recovering a data file, recoding the data from document files (pdf, doc), or on request.
+Meta-analysis is one of the most useful and powerful research approaches, the relevance of which relies on its credibility.
+However, in recent years different concerns about the credibility of psychological research have emerged.
+Reproducibility of scientific results could be considered as the minimal threshold of it.
+In this study, our purpose was to assess the reproducibility of a sample of published meta-analyses.
+From a random sample of 100 papers containing at least one meta-analysis on the effectiveness of interventions in clinical psychology, 217 meta-analyses were selected.
+We first tried to retrieve the original data by recovering a data file, recoding the data from document files (pdf, doc), or requesting original data from authors.
 Second, through a multi-stage workflow, we tried to reproduce the main results of each meta-analysis using these data.
-The original data were retrieved for 146 meta-analyses from different sources.
-Of these, in the first stage 52 showed a discrepancy larger than 5\% in the main results, in 25 of them, this discrepancy was solved with minor adjustments, or correction of coding errors.
-In the remaining 27, different issues were identified in an in-depth review of the papers, such as reporting inconsistencies, lack of some data, or transcription errors.
-Current practices of data sharing in meta-analyses hamper the reusability of meta-analytic data.
-On the other hand, the implementation of new tools would help to avoid certain errors in the meta-analysis reporting process.
+The original data were retrieved for 146 \textcolor{blue}{(67\%, 146/217)} meta-analyses.
+Of these, 52 showed a discrepancy larger than 5\% in the main results in the first stage.
+\textcolor{blue}{For 10 meta-analyses this discrepancy was solved after fixing a coding error and for 15 of them it was solved with minor adjustment or considered approximately reproduced in a qualitative assessment.} In the remaining 27 meta-analyses\textcolor{blue}{(18\%, 27/146)}, different issues were identified in an in-depth review of the papers, such as reporting inconsistencies, lack of data, or transcription errors.
+\textcolor{blue}{Nevertheless, the numerical discrepancies produced by these issues were mostly minor, with little or no impact on the conclusions.} Current practices of data sharing in meta-analyses hamper the reusability of meta-analytic data.
+The implementation of new tools would help to avoid certain errors in the meta-analysis reporting process.
 }
@@
 Meta-analysis is widely considered as an important approach to evaluate a body of work.
-Given the ongoing growth in the number of scientific publications (Bornmann et al., 2021), evidence synthesis approaches -such as meta-analysis- are becoming increasingly relevant for a cumulative science.
-This relevance rests on the credibility of meta-analytic results, which can be threatened by a lack of rigorous application or poor-quality reporting (Gurevitch et al., 2018).
+Given the ongoing growth in the number of scientific publications (Bornmann et al., 2021), evidence synthesis approaches---such as meta-analysis---are becoming increasingly relevant for a cumulative science.
+This relevance rests on the credibility of meta-analytic results, which can be threatened by a lack of rigorous methodology or poor-quality reporting (Gurevitch et al., 2018).
 Given the importance of meta-analyses for evidence-based practice, these threats to their credibility need to be closely monitored.
@@
 
-The reproducibility of all published scientific results could be considered as the minimal threshold of scientific credibility (Hardwicke et al., 2021).
+The reproducibility of published scientific results could be considered as the minimal threshold of scientific credibility (Hardwicke et al., 2021).
 Different approaches can be adopted for the empirical assessment of reproducibility.
@@
 (2022) make the distinction between process reproducibility and outcome reproducibility.
-Following this framework, a process reproducibility assessment could be carried out by reviewing the availability of the materials, data, and precise details of the analytical strategy in the report that are required to proceed with the reproduction attempt.
+Following this framework, a process reproducibility assessment could be carried out by reviewing the availability of the materials, data, or precise details of the analytical strategy in the report that are required to proceed with the reproduction attempt.
 An outcome reproducibility assessment can be carried out when the required elements are retrievable by actually reproducing the analyses.
@@
 For example, some process reproducibility assessments have shown an important lack of data availability in machine-readable formats, and an almost complete absence of analysis script code availability (López-Nicolás et al., 2022; Polanin et al., 2020).
-Furthermore, some outcome reproducibility assessments have shown a considerable number of failures when trying to reproduce the primary effect sizes of some published meta-analyses by recollecting primary data from primary studies (Gøtzsche et al., 2007; Maassen et al., 2020; Tendal et al., 2009) possibly due to lack of details on how primary effect sizes were selected and computed.
+Furthermore, some outcome reproducibility assessments have shown a considerable number of failures when trying to reproduce the primary effect sizes of some published meta-analyses by recollecting primary data from primary studies (Gøtzsche et al., 2007; Maassen et al., 2020; Tendal et al., 2009), possibly due to lack of details on how primary effect sizes were selected and computed.
 In these outcome reproducibility studies, the main task entails reconstructing the original data by retrieving them from the source, namely the included primary studies.
@@
 \end{center}
-\end{figure*}
+\end{figure}
 
-Reproducibility analysis typically uses the original data available from the original authors (e.g., Artner et al., 2020; Hardwicke et al., 2021, 2018).
+Reproducibility analysis \textcolor{blue}{of reported quantitative results} typically uses the original data available from the original authors (e.g., Artner et al., 2020; Hardwicke et al., 2021, 2018).
 This puts the focus of the assessment at factors such as the reusability of the available data, challenges for the reconstruction of the original analysis scheme, reporting errors, etc.
@@
 Only 31\% included a data availability statement and only 13\% of these included a link to access the data openly, with 23\% stating that all relevant data are available in the paper itself, 10\% stating that data sharing is not applicable as no datasets were generated, 8\% stating that data sharing is not applicable as the data is drawn from already published literature, and 42\% stating that data were available upon request.
-It is surprising that, even just considering meta-analyses that included a data availability statement, the authors of these meta-analysis assume that such practices do not apply to meta-analyses or that the data in the article itself is sufficient.
+It is surprising that, even just considering meta-analyses that included a data availability statement, the authors of these meta-analysis assume that such practices do not apply to meta-analyses, or that the data in the article itself is sufficient.
 
@@
 The full search strategies and a summary of the screening process are available at: \url{https://osf.io/z5vrn/}, and the workflow of the random selection process is available at: \url{https://osf.io/cp293/}.
-From these 100 articles, each independent reported meta-analysis with at least 10 primary studies was selected.
+\textcolor{blue}{This sample size was based on our judgement of an acceptable trade-off between informativeness and feasibility.}
+From these 100 articles, each independent \textcolor{blue} {pairwise meta-analytic model of aggregate data fitted} on at least 10 primary studies was selected.
 In case no meta-analysis reported in a paper had at least 10 studies, the meta-analysis with the highest number of primary studies was selected, which was the case for 29 of the articles included in this report.
-Our unit of analysis was each independent meta-analysis selected under these criteria.
-A total of 217 independent meta-analyses were selected.
+\textcolor{blue}{This criterion was established to focus on the main meta-analyses of each paper, based on the assumption that the search strategies would be designed to maximise the number of primary studies included that were related to the main aims of the paper.}
+
+Our unit of analysis was each independent meta-analysis selected under these criteria. A total of 217 independent meta-analyses were selected.
 
@@
 
-The availability of necessary primary data was checked.
-First, we searched for machine-readable data files through links leading to third-party repositories or in supplementary material hosted by the journal.
+In order to be able to reproduce meta-analyses of \textcolor{blue}{aggregate data, primary-level}\footnote{By primary-level data we mean aggregate data from included primary studies.} effects sizes and their associated standard errors are required.
+These are generally computed from statistics retrieved from the primary studies such as means, standard deviations or sample sizes.
+We attempted to retrieve the least processed data possible.
+First, we sought for the statistics \textcolor{blue}{used to compute primary effect sizes (e.g., means, sd)}; second, we sought for the primary effects sizes \textcolor{blue}{already computed} and their standard errors (or, alternatively, the sampling variances): finally, we sought for the primary effects sizes and their confidence limits, from which the standard errors were approximated as follows:
+
+\[se_i = (\frac{UB_i - LB_i}{2z_{\alpha/2}})\]
+
+with \(se_i\) being the standard error of the ith effect size, \(UB_i\) and \(LB_i\) the upper and lower confidence limits of confidence interval for the ith effect size, and \(z_{\alpha/2}\) the \((1 - {\alpha/2})\%\) percentile of the standard normal distribution (usually, \(z_{\alpha/2} = 1.96\) assuming a two-sided 95\% confidence interval).
+
+\textcolor{blue}{On the other hand, efforts were also made to retrieve the most reusable data possible.} First, we searched for machine-readable data files through links leading to third-party repositories or in supplementary material hosted by the journal.
 Second, we looked for available data through tables or forest plots in the meta-analytic report itself, or in supplementary material.
@@
 
-In order to be able to reproduce meta-analyses, primary effects and their associated standard errors are required.
-These are generally computed from primary statistics retrieved from the primary studies such as means, standard deviations or sample sizes.
-We attempted to retrieve the least processed data possible.
-First, we sought for the primary statistics, recovered in 26\% of the cases.
-Second, we sought for the primary effects and their standard errors (or, alternatively, the sampling variances), recovered in 5\% of the cases.
-Finally, we sought for the primary effects and their confidential limits, recovered in 69\% of the cases, from which the standard errors were approximated as follows:
-
-\[se_i = (\frac{UB_i - LB_i}{2z_{\alpha/2}})\]
-
-with \(se_i\) being the standard error of the ith effect size, \(UB_i\) and \(LB_i\) the upper and lower confidence limits of confidence interval for the ith effect size, and \(z_{\alpha/2}\) the \(1 - z_{\alpha/2}\) quantile of the standard normal distribution (usually, \(z_{\alpha/2} = 1.96\) assuming a two-sided 95\% confidence interval).
-
 \hypertarget{reconstructing-the-original-analytical-scheme}{%
@@
 To proceed with reproducibility attempts of the meta-analyses that were labelled as process reproducible, we first looked for the availability of the original analysis script.
-When it was available, analytical reproducibility was checked by rerunning the original script on the associated primary data.
-In 141 cases (97\%), the analysis script code was not available.
-In these cases we tried to reconstruct the original analytical scheme using the technical details reported in the paper.
+When it was available, reproducibility was checked by rerunning the original script on the associated primary data.
+When it was not available, we tried to reconstruct the original analytical scheme using the technical details reported in the paper.
 Specifically, we collected information on: (a) the meta-analytic model originally assumed; (b) the weighting scheme; (c) the between-studies variance estimator; (d) the method used to compute the confidence interval; and (e) the software used to perform the meta-analysis.
@@
 If the software used was not reported, we inferred this information from the default settings of the most used software in the sample, which was \emph{Comprehensive Meta-Analysis}.
+\textcolor{blue}{We designed this procedure to reconstruct the original analytical scheme when the original analysis script was not available instead of trying to request it from the original authors due to: (a) not necessarily all authors of included meta-analyses will actually have an analysis script to share, because many might have used point and click software, and (b) we expected analysis script availability to be very low, and requesting it would have meant sending request for virtually every paper included in our re-analysis.}
 
@@
 
-Primary-level data and aggregate-level data described above were coded by five members of the group.
-At a first pilot stage, a random sample of five articles of the total pool was independently coded by the five members and, subsequently, in a series of meetings, disagreements between the coders were resolved by consensus.
+\textcolor{blue}{Data collection procedure was carried out by five of the authors.} At a first pilot stage, a random sample of five articles of the total pool was independently coded by the five members and, subsequently, in a series of meetings, disagreements between the coders were resolved by consensus.
 Next, the initial pool of 100 included articles was split among four coders, 25 articles each.
@@
 Disagreements were resolved by consensus and by double-checking the original materials.
+\textcolor{blue}{Details about inter-coder agreement are reported in the Supplementary file.}
 
@@
 
-Each meta-analysis was labelled using the following reproducibility success scheme: (a) reproducible; (b) not process-reproducible; (c) numerical error, and (d) decision error.
-Not process-reproducible refers to situations where we were unable to access the primary data neither through direct extraction nor upon request.
+Each meta-analysis was labelled using the following \textcolor{blue}{two-level}\footnote{This hierarchy is a minor deviation from the pre-registered protocol.
+It is essentially the same and the results are identical.
+It was introduced to improve clarity.} reproducibility success scheme.
+\textcolor{blue}{First, each meta-analysis was labelled as: (a) process-reproducible; and (b) not process-reproducible.
+In our study, not process-reproducible refers to situations where we were unable to access the primary data neither through direct extraction nor upon request}\footnote{Process reproducibility, as described above, could imply a different situation if more conditions need to be met to proceed with the reproduction attempt.
+In our study, this is equivalent to data availability due to our design and the stage of the meta-analysis pipeline we focused on.}.
+\textcolor{blue}{Second, those labelled as process-reproducible} were labelled as: (a) reproducible; (b) numerical error; and (c) decision error.
 Similar to previous studies (Artner et al., 2020; Hardwicke et al., 2018, 2021) an index of numerical error was computed (see Protocol \url{https://osf.io/tq4uf/}).
@@
 
-We focus on analytical reproducibility of summary effects, their confidence bounds and the result of the null hypothesis significance test.
-Secondarily, we also assessed analytical reproducibility of other synthesis methods such as heterogeneity statistics.
+We focus on reproducibility of summary effects, their confidence bounds and the result of the null hypothesis significance test.
+Secondarily, we also assessed reproducibility of other synthesis methods such as heterogeneity statistics.
 
@@
 
-Analytical reproducibility checks were carried out at different stages.
+Reproducibility checks were carried out at different stages.
 First, through reported analytic details or script code.
@@
 From the 100 included papers, 217 independent meta-analyses were selected following the criteria explained above.
-These meta-analyses included 18.35 primary studies on average (sd = 17.25; median = 13; interquartile range = 10-19; range = 3-134)).
-Figure 2 displays the distribution of number of primary studies among the meta-analyses included in our sample.
-Original results and characteristics of these meta-analyses are available at: \url{https://osf.io/8jzbk}
+These meta-analyses included 18.35 primary studies on average (sd = 17.25; median = 13; interquartile range = 10-19; range = 3-134)), \textcolor{blue}{and were cited 108.39 times on average (sd = 151.00; median = 57; interquartile range = 29-128; range = 3-1036)}\footnote{Citation counts were retrieved from CrossRef API using the \emph{rcrossref} package (Chamberlain et al., 2023).
+For two cases in which CrossRef did not return data, citation counts were consulted in Google Scholar.
+Both queries were done on 20/03/2023.}.
+Figure 2 displays the distribution of number of primary studies among the meta-analyses included in our sample \textcolor{blue}{(panel A), the publication year distribution among the papers included in our sample (panel B) as well as the citation count distribution of those papers (panel C).} Original results and characteristics of these meta-analyses are available at: \url{https://osf.io/8jzbk}
 
@@
 \centering
-\includegraphics{manuscript_files/figure-latex/unnamed-chunk-1-1.pdf}
-\caption{\label{fig:unnamed-chunk-1}Distribution of the number of primary studies included in each of the meta-analyses.
+\includegraphics{submission_files/figure-latex/unnamed-chunk-1-1.pdf}
+\caption{\label{fig:unnamed-chunk-1}Distribution of (a) the number of primary studies included in each of the meta-analyses; (b) the publication year of the included papers; (c) citation count of the included papers.
 Vertical blue dotted lines represent the first quartile, median, and third quartile, respectively.}
@@
 Based on the availability of primary data, either retrieved directly from the paper or upon request, 146 meta-analyses (67\%, see Fig.
-2a) were labelled as process reproducible.
-Of these 146 meta-analyses, in about half of the cases the primary data was retrieved from a forest plot in the paper itself and in about a third of the cases the primary data was retrieved from supplementary files.
-Only in 3\% of the cases the primary data was retrieved upon request (see Fig.
-2b for further details).
-Although attempts were made to retrieve data for 75 meta-analyses from 25 different papers by emailing the corresponding authors, data was only retrieved for 4 meta-analyses, from 3 different papers (12\%, see Fig.
-2c).
-For the remaining 71 from 22 different papers, a reply providing some reasons not to share was received in 12\% (see Fig 2c), whereas no reply was received for the remainder of the meta-analyses.
+3a) were labelled as process reproducible.
+Of these 146 meta-analyses, in about half of the cases the primary data was retrieved from a forest plot in the paper itself and in about a third of the cases the primary data was retrieved from supplementary files (see Fig.
+3b for further details).
+Although attempts were made to retrieve data for 78 meta-analyses from 25 different papers by emailing the corresponding authors, data was only retrieved for 7 meta-analyses, from 3 different papers (12\%, 3/25, see Fig.
+3c).
+For the remaining 71 from 22 different papers, a reply providing some reasons not to share was received in 32\% (8/25, see Fig 3c), whereas no reply was received for the remainder of the meta-analyses.
 Table 1 summarises the different reasons corresponding authors given when data was not provided upon request.
@@
 \centering
-\begin{tabular}[t]{>{\raggedright\arraybackslash}p{7cm}cc}
+\begin{tabular}[t]{>{\raggedright\arraybackslash}p{16cm}c}
 \toprule
-Reason & N & \%\\
+Reason & N\\
 \midrule
-Data held by a co-author, and do not have his contact details & 1 & 12\%\\
-Propietary dataset & 1 & 12\%\\
-The author no longer has the data. & 5 & 62\%\\
+Data held by a co-author, and do not have his contact details & 1\\
+Propietary dataset & 1\\
+The author no longer has the data. & 5\\
 The author requested more information and a written agreement including possible authorship. 
-                                                      Additional details were sent and after some email exchanges there was no further response. & 1 & 12\%\\
+                                                      Additional details were sent and after some email exchanges there was no further response. & 1\\
 \bottomrule
@@
 
-In most cases, when the meta-analytic data was available, it was shared in document formats, as previously reported.
-Data available in tables or forest plots shared in \emph{pdf} or \emph{docx} format --either in the document itself or in the supplementary materials-- was found to be highly prevalent.
+In most cases, when the meta-analytic data was available, it was shared in document formats.
+Data \textcolor{blue}{were retrieved from} tables or forest plots in \emph{pdf} or \emph{docx} format---either in the document itself or in the supplementary materials---\textcolor{blue}{in} 92\% (134/146) \textcolor{blue}{of the cases}.
 This required a manual recoding of the primary data to be able to reuse them.
 Furthermore, when data was reported through general tables (i.e.~tables listing all the primary studies included with their characteristics), the meta-analysis associated with each data entry was not always obvious, leading to the time-consuming task of matching each data entry with each independent meta-analytic result reported in the paper.
-There were only 7 meta-analyses (from three different papers) of the 146 meta-analyses labelled as process reproducible (5\%), where the task of retrieving the data required simply downloading the data in an machine-readable data file format.
-On the other hand, as shown in Figure 3c, when the necessary data was not available, retrieving it upon request to the original authors led to a remarkably low reponse rate.
+There were only 4 meta-analyses (from three different papers) of the 146 meta-analyses labelled as process reproducible (3\%), where the task of retrieving the data required simply downloading the data in an machine-readable data file format.
+On the other hand, as shown in Figure 3c, when the necessary data was not available, retrieving it upon request to the original authors led to a low response rate.
 
-\begin{figure*}
-\includegraphics[width=1\linewidth]{manuscript_files/figure-latex/unnamed-chunk-3-1} \caption{Percentage of (a) process-reproducible meta-analyses; (b) different types of sources of original data; and (c) data request results.}\label{fig:unnamed-chunk-3}
-\end{figure*}
+\begin{figure}
+\centering
+\includegraphics{submission_files/figure-latex/unnamed-chunk-3-1.pdf}
+\caption{\label{fig:unnamed-chunk-3}Percentage of (a) process-reproducible meta-analyses; (b) different types of sources of original data; (c) data request results.}
+\end{figure}
 
@@
 As mentioned above, in 5 of these meta-analyses (3\%), all from the same published article, the original script code was available.
-Therefore, in these five cases, analytical reproducibility was checked running the original analysis script on the original primary data.
+Therefore, in these five cases, outcome reproducibility was checked running the original analysis script on the original primary data.
 In the remaining cases, the original analytical framework was reconstructed as explained in the method section.
+Figure 4 summarises the results of the whole process of outcome reproducibility assessment.
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=\textwidth]{results/Figure 4.png}
+
+\caption{Results of the different stages carried out in the evaluation of the outcome reproducibility. 
+}
+
+\label{fig:fig4}
+\end{center}
+\end{figure}
 
@@
 After this, 10 were re-labelled as reproduced and 7 still had relevant discrepancies.
-Furthermore, 15 were labelled as reproduced in the qualitative check because the discrepancy was probably explained by rounding issues, inverted signs for results (where effect sizes were reported in absolute values) and primary data, minor reporting errors, or minor adjustments in the analytical scheme.
+Furthermore, 15 were labelled as \textcolor{blue}{approximately reproduced or reproduced with minor adjustment} in a qualitative check because the discrepancy was probably explained by rounding issues, inverted signs for results (when effect sizes were reported in absolute values) and primary data, minor reporting errors, or minor adjustments in the analytical scheme\footnote{Full details in Supplementary File}.
 In the remaining 20, and in the 7 re-analysed again without success, some issues or relevant discrepancies without apparent explanation were found.
-
-Figure 4 displays a scatterplot showing the consistency between the original and reproduced summary effect size and their confidence bounds of these 52 meta-analyses.
+Figure 5 displays a scatterplot showing the consistency between the original and reproduced summary effect size and their confidence bounds of these 52 meta-analyses.
 Additionally, as a secondary analysis, the reproducibility of the \(I^2\) heterogeneity statistic was explored.
-Figure 5 displays a scatterplot showing the consistency between the original and reproduced \(I^2\) statistics.
-As shown in Figures 4 and 5, the discrepancies found in the heterogeneity statistic \(I^2\) are larger than those found in the summary effects and their confidence intervals.
-The lack of precision of the available data (rounded data) or incomplete information on aspects such as the tau-squared estimator applied seem to have a substantial impact on the reproducibility of this result.
+Figure 6 displays a scatterplot showing the consistency between the original and reproduced \(I^2\) statistics.
+As shown in Figures 5 and 6, the discrepancies found in the heterogeneity statistic \(I^2\) are larger than those found in the summary effects and their confidence intervals.
+\textcolor{blue}{The Pearson's correlation between the summary effect and $I^2$ discrepancies was .172.} The lack of precision of the available data (rounded data) or incomplete information on aspects such as the tau-squared estimator applied seem to have a substantial impact on the reproducibility of this result.
 
@@
 \centering
-\includegraphics{manuscript_files/figure-latex/unnamed-chunk-4-1.pdf}
+\includegraphics{submission_files/figure-latex/unnamed-chunk-4-1.pdf}
 \caption{\label{fig:unnamed-chunk-4}Scatterplot displaying the reproduced values as a function of the original values classified by whether or not decision error was found.
@@
 \centering
-\includegraphics{manuscript_files/figure-latex/unnamed-chunk-5-1.pdf}
+\includegraphics{submission_files/figure-latex/unnamed-chunk-5-1.pdf}
 \caption{\label{fig:unnamed-chunk-5}Scatterplot displaying the reproduced values as a function of the original values classified by whether or not decision error was found.
 Only the results of the 52 meta-analyses with a discrepancy of more than 5\% identified in the first stage are displayed, but with the corrections made in the second stage.
-The values displayed are \(I^2\) hetorogeneity statistics.
-The size of the crosses is function of the discrepancy in the summary effect.}
+The values displayed are \(I^2\) heterogeneity statistics.
+The size of the crosses is a function of the discrepancy in the summary effect.}
 \end{figure}
@@
 These 27 meta-analyses were from 10 different papers.
-Therefore, 10 clarification requests with information about the study aims, methods and preliminary results were sent to the corresponding authors of the original articles.
+Therefore, 10 clarification requests with information about the study aims, methods, and preliminary results were sent to the corresponding authors of the original articles.
 A reply was received in only 2 of the 10 cases.
-In one of them, the original authors sent back a link to an OSF repository where the original data and analysis script were stored.
+In one of them, the original authors sent back a link to an OSF repository\footnote{According to the repository timeline the project was created on 02/06/2019 and according to the journal's article history the paper was published on 13/06/2019.
+It seems that the repository was created as a journal requirement} where the original data and analysis script were stored.
 According to the authors, this link was not reported in the paper by mistake.
@@
 
-Figure 6 summarises the results of the whole process of outcome reproducibility assessment.
-
-\begin{figure*}
-\begin{center}
-\includegraphics[width=\textwidth]{results/Figure 6.png}
-
-\caption{Results of the different stages carried out in the evaluation of the outcome reproducibility. 
-}
-
-\label{fig:fig6}
-\end{center}
-\end{figure*}
-
 \hypertarget{discussion}{%
@@
 
-The main aim of this study was to examine the analytical reproducibility of a sample of published meta-analyses on the effectiveness of clinical psychology interventions.
+The main aim of this study was to examine the reproducibility of a sample of published meta-analyses on the effectiveness of clinical psychology interventions.
 We analyzed the availability and reusability of original data and, assessed the reproducibility of the published results using these retrieved original data, and tried to reconstruct the original analysis plan.
@@
 
-Even when we interpret data availability in the broad sense (i.e.~retrieving data from tables and figures when no data file was available), for about a third of the included meta-analyses no data was available.
+Even when we interpret data availability in the broad sense (i.e.~retrieving data from tables and figures when no data file was available), for about a third of the included meta-analyses no data were available.
 In these cases, attempts were made to obtain the data on request to the corresponding author, with little success.
 Authors only shared data in 12\% of the requests that were made.
-This result is in line with what was found in a recent study where data availability statements from a set of primary studies were analysed (Gabelica et al., 2022).Where 42\% of primary studies in Gabelica et al.
-(2022) reported data was available on request (and identical percentage was found in Page et al.
+This result is in line with what was found in a recent study where data availability statements from a set of primary studies were analysed (Gabelica et al., 2022).
+Although 42\% of primary studies in Gabelica et al.
+(2022) reported data were available on request (an identical percentage was found in Page et al.
 (2022) for meta-analyses), only 6.8\% of the authors shared the underlying data when requested.
@@
 Several repositories (e.g., OSF, GitHub, Zenodo, Figshare) are available for researchers to openly share the data associated with published results.
-On-request availability has proven to be inadequate, and with the availability of data repositories is no longer necessary.
+On-request availability has proven to be inadequate, and with the availability of data repositories it is no longer necessary.
 Journals publishing meta-analyses should require that authors share the underlying data in a public data repository.
 
-For the remaining meta-analyses (about two thirds), we were able to retrieve the data used by the original authors.
-In only 5\% of these cases data was shared in a machine-readable data file (e.g., \emph{csv}, \emph{xlsx}), while the data had to be retrieved from files in document format (e.g., \emph{docx}, \emph{pdf}) for the rest of cases.
-This forces people who want to re-use the data to manually recode the data, which is both inefficient and error-prone task.
-Even after partial double coding was carried out, this procedure did not avoid some coding errors, which were detected by double checking meta-analyses with discrepancies.
-In out experience, the data retrieval process can be difficult when results are presented in general tables, as it involves matching subsets of these primary data with different meta-analytic results, while is not always clear which studies were used in which meta-analysis reported in a paper.
+\textcolor{blue}{A more positive sign comes from the positive association between publication year and the possibility of retrieving the data that was observed in an exploratory analysis in the supplementary materials.
+This tentatively suggests that data-availability is improving over time.
+This observation could be related to the existence of well-established meta-analysis reporting guidelines.
+For instance, the first PRISMA guideline} (Moher et al., 2009) \textcolor{blue}{encouraged meta-analyst to report results of primary studies (e.g.
+primary effect sizes and their confidence interval through a forest plot, as was a common scenario among the cases included in this project), and the latest PRISMA guideline} (Page et al., 2021) \textcolor{blue}{which puts more emphasis on appropriate data sharing through data files ready for reuse.} At the same time in only 5\% of the cases where data were retrieved in our sample were we able to retrieve the data in a machine-readable data file that was ready for reuse (e.g., \emph{csv}, \emph{xlsx}).
+Most often the data had to be retrieved from files in document format (e.g., \emph{docx}, \emph{pdf}).
+This forces people who want to reuse the data to manually recode the data, which is an inefficient and error-prone task.
+Even after partial double coding was carried out, this procedure did not avoid some coding errors, which were only detected by double checking meta-analyses with discrepancies.
+In our experience, the data retrieval process can be difficult when results are presented in general tables, as it involves matching subsets of these primary data with different meta-analytic results, while is not always clear which studies were used in which meta-analysis reported in a paper.
 Furthermore, because the tables in manuscript are often generated manually in document file formats (e.g.~Word), we observed examples where this introduced another source of error.
-There are good guidelines on how to share research data properly (Wilkinson et al., 2016), and authors should share data in machine-readable formats.
+\textcolor{blue}{The foregoing discussion raises a key point about how time consuming the appraisal of meta-analytic reproducibility currently is, and how efficiency would be improved by having open access to the underlying meta-analytic data in data file formats ready for reuse.
+The latest PRISMA guidelines, along with some initiatives that promote appropriate data sharing} (e.g.
+Wilkinson et al., 2016) \textcolor{blue}{have the potential to generate significant improvements in the re-use of meta-analytic data in the years ahead.
+In this regard, our results provide a useful baseline for future assessments.}
 
@@
 Only in five meta-analyses (3\%, all from the same paper), was the original script openly available.
-In most cases, the original analyses were reconstructed from the description provided in the paper itself, which was not always rich in detail, so that many of these computational details had to be inferred from the default settings of the software authors used.
+In most cases, the original analyses were reconstructed from the description provided in the paper itself, which was not always rich in detail, so many of these computational details had to be inferred from the default settings of the software authors used.
 The availability of analysis scripts often shows similar rates, both in meta-analyses (Page et al., 2022; Polanin et al., 2020) and in primary research (Hardwicke et al., 2022, 2020).
@@
 Some of the problems identified could be explained by typos.
-Currently, there are tools that facilitate the production of so-called reproducible manuscripts, such as the R packages \emph{kintr} (Xie, 2022), \emph{rmarkdown} (Allaire et al., 2022), and \emph{papaja} (Aust \& Barth, 2022).
+Currently, there are tools that facilitate the production of so-called reproducible manuscripts, such as the R packages \emph{knitr} (Xie, 2022), \emph{rmarkdown} (Allaire et al., 2022), and \emph{papaja} (Aust \& Barth, 2022).
 A reproducible manuscript embeds analysis code, data and results reporting in a single document, extracting and reporting the results from the output of the computational process itself, avoiding error-prone manual transcriptions.
@@
 
+\hypertarget{prior-versions}{%
+\subsection{Prior versions}\label{prior-versions}}
+
+A version of this manuscript has been posted as a preprint on PsyArxiv: \url{https://psyarxiv.com/gvqrn/}
+
 \hypertarget{references}{%
@@
 \url{https://doi.org/10.1057/s41599-021-00903-w}
+
+\leavevmode\vadjust pre{\hypertarget{ref-rcrossref}{}}%
+Chamberlain, S., Zhu, H., Jahn, N., Boettiger, C., \& Ram, K. (2023). \emph{Rcrossref: Client for various 'CrossRef' 'APIs'}.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-moher2009}{}}%
+Moher, D., Liberati, A., Tetzlaff, J., Altman, D.
+G., \& PRISMA Group.
+(2009).
+Preferred reporting items for systematic reviews and meta-analyses: The {PRISMA} statement.
+\emph{PLoS Medicine}, \emph{6}(7), e1000097.
+\url{https://doi.org/10.1371/journal.pmed.1000097}
+
 \leavevmode\vadjust pre{\hypertarget{ref-moreau2020}{}}%
@@
 \url{https://doi.org/10.1016/j.jclinepi.2017.10.017}
+
+\leavevmode\vadjust pre{\hypertarget{ref-page2021}{}}%
+Page, M.
+J., Moher, D., Bossuyt, P.
+M., Boutron, I., Hoffmann, T.
+C., Mulrow, C.
+D., Shamseer, L., Tetzlaff, J.
+M., Akl, E.
+A., Brennan, S.
+E., Chou, R., Glanville, J., Grimshaw, J.
+M., Hróbjartsson, A., Lalu, M.
+M., Li, T., Loder, E.
+W., Mayo-Wilson, E., McDonald, S., \ldots{} McKenzie, J.
+E.
+(2021).
+{PRISMA} 2020 explanation and elaboration: Updated guidance and exemplars for reporting systematic reviews.
+\emph{BMJ}, \emph{372}, n160.
+\url{https://doi.org/10.1136/bmj.n160}
 

### 2023-04-21 supplementary_file.Rmd
Revised version

@@
 output: pdf_document
+linestretch: 2
+fontsize: 12pt
+header-includes:
+   - \usepackage{caption}
+   - \captionsetup[table]{textfont={it}, labelfont={bf}, singlelinecheck=false, labelsep=newline}
+   - \captionsetup[figure]{textfont={it}, labelfont={bf}, singlelinecheck=false, labelsep=newline}
 ---
@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE)
+knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
 ```
@@
 source(here::here("analysis", "06_supplementary.R"))
+
+```
+
+# Inter-coder agreement
+
+Out of the 25 papers selected to carry out independent double-coding, 21 had primary data available for one or more meta-analyses selected under the criteria explained in the main manuscript.
+Some disagreements or coding errors in the primary data were found in `r length(datasets_wo_error) - sum(datasets_wo_error)` (`r sprintf("%0.0f%%", round((1-mean(datasets_wo_error))*100,2))`) cases.
+The intraclass correlation coefficient between the values coded by each coder was computed for each of those 21 datasets.
+The ICC values varied between `r round(min(icc_table$ICC), 3)` and `r max(icc_table$ICC)` (mean = `r round(mean(icc_table$ICC), 3)`).
+Full results of the inter-coder agreement are presented in Table S1.
+
+```{r}
+
+kbl(
+  icc_table,
+  format = "latex",
+  booktabs = TRUE,
+  linesep = '\\addlinespace',
+  col.names = c("Paper", "ICC", "Full agreement"),
+  align = c("l", "l", "l"),
+  caption = "Full results of the inter-coder agreement"
+  ) %>% 
+  kable_styling(full_width = T, latex_options = "hold_position")
 
@@
 ``` {r, fig.width = 7, fig.height=5, fig.cap="Barplot displaying the number of meta-analyses labelled as numerical error under different criteria.
-The value used in the original design is 5%, the rest are different values of difference in absolute value between reported and reproduced result."}
+The value used in the original design is 5%, the other bars correspond to alternative criteria of the difference in absolute value between reported and reproduced result."}
 
@@
 ```
+
+# Data availability over years
+
+The association between data availability and publication year was explored by fitting binary logistic regression models with publication year as predictor and process-reproducibility as dependent variable.
+We quantified the strength of the association by calculating odds ratios and 95% confidence intervals based on the profile likelihood.
+The analyses of the main manuscripts were mostly carried out at meta-analysis level.
+However, our dataset has a nested structure with meta-analyses nested within papers, which could compromise the assumption of independence of the regression model.
+Hence, we fitted the regression model at both meta-analysis and paper levels.
+Since we selected more than one meta-analysis from some of the papers, in `r sum(df_mas_pyear2$process_rep2==2)` cases primary data only could be retrieved for certain of the meta-analyses in that paper, but not for all the selected meta-analyses in that paper.
+To avoid misclassifications, these cases were excluded from the paper-level analyses.
+Futhermore, as we work on an unrestricted random sample, the publication year distribution of the sample is clearly left-skewed.
+Therefore, the information provided by the data at the bottom range of the predictor is limited.
+For this reason, the analyses were complemented by fitting logistic regression models on a subset of the data excluding the papers published before 2010.
+In summary, we fitted four binary logistic regression model at both meta-analysis and paper levels and using the full dataset or a subset of meta-analyses published after 2010.
+Despite multiple contrasts performed, we did not introduce any corrections for multiple comparisons due to the exploratory nature of our analyses.
+Table S2 summarises the results of the models.
+
+```{r}
+
+kbl(
+  log_reg_results,
+  format = "latex",
+  booktabs = TRUE,
+  linesep = '\\addlinespace',
+  col.names = c("Level", "Before 10s exclusion", "Slope", "OR", "OR LL", "OR UL", "$p$"),
+  align = c("l", "l", "l","l", "l", "l","l"),
+  caption = "Binary logistic regression models results",
+  escape = FALSE
+  ) %>% 
+  kable_styling(full_width = T, latex_options = "hold_position") %>% 
+  column_spec(2, width = "2cm")
+
+```
+\pagebreak
+Based on the results of the four models, there seems to be an association between the publication year and the possibility of retrieving primary data from a meta-analysis.
+We found that all 4 ORs computed were > 1, indicating a higher probability of retrieving data the more recent the publication year of the meta-analysis.
+Additionally, in only one of the cases (paper-level model without excluding cases published before 2010) did the 95%CI of the OR include a value < 1.
+\pagebreak
+
+# Qualitative check results 
+```{r}
+kbl(
+  table_qual,
+  format = "latex",
+  booktabs = TRUE,
+  #linesep = '\\addlinespace',
+  col.names = c("Case", "Reason"),
+  align = c("l", "l"),
+  caption = "Reasons found during the qualitative assessment"
+  ) %>% 
+  kable_styling(full_width = T, latex_options = "hold_position") %>% 
+  column_spec(2, width = "14cm")
+
+```

### 2023-04-21 analysis/00_functions.R

@@ -92,13 +92,24 @@ customized_barplot<- function(d, pal, title, legend, width=0.35, rate=TRUE){
 # title: desired plot title
 #
 
-scatter_match<- function(d, x, y, shape, shape_name, shape_labels, size, title)
+scatter_match<- function(d, x, y, shape, shape_name, shape_labels, size, title, size_constant = T){ 
+  if (size_constant == TRUE) {
+    
+  plt<-ggplot(d, aes(x=x, y=y, shape = shape)) +
+  geom_point(aes(col = shape), stroke = 1, size = size)  
+  } 
+
+else {
   
-  ggplot(d, aes(x=x, y=y, shape = shape, size = size)) +
-  geom_point(stroke = 1) + 
-  geom_abline(intercept = 0, slope = 1, colour = "#000000", size = 0.65) + 
-  scale_shape_manual(name = shape_name, labels = shape_labels, values = c(18, 3)) +
+  plt<-ggplot(d, aes(x=x, y=y, shape = shape, size = size)) +
+    geom_point(aes(col = shape), stroke = 1)  
+  
+}
+
+plt<- plt +  geom_abline(intercept = 0, slope = 1, colour = "#000000", size = 0.65) + 
+  scale_shape_manual(name = shape_name, labels = shape_labels, values = c(17, 4)) +
   scale_size_continuous(range = c(1, 6), guide = "none") + 
+  scale_color_manual(name = shape_name, labels = shape_labels, values = c("red", "black"))+
   theme_classic(base_size = 10) + 
   theme(legend.text = element_text(size = 13),
         legend.key.size = unit(.5,"cm"),
@@ -112,14 +123,14 @@ scatter_match<- function(d, x, y, shape, shape_name, shape_labels, size, title)
        x= "Original value"
   )
 
+}
 
-
-scatter_match2<- function(d, x, y, shape, color, color_name, color_labels, size, shape_name, shape_labels, title)
+scatter_match2<- function(d, x, y, color, color_name, color_labels, size, title)
   
-  ggplot(d, aes(x=x, y=y, shape = shape, color = color, size = size)) +
-  geom_point(stroke = 1) + 
+  ggplot(d, aes(x=x, y=y, color = color, size = size)) +
+  geom_point(stroke = 1, size = size, shape = 4) + 
   geom_abline(intercept = 0, slope = 1, colour = "#000000", size = 0.65) + 
[…]

### 2023-04-21 analysis/01_importing_data_and_descriptives.R

@@ -3,7 +3,7 @@ if(!require(pacman)){
 }
 library(pacman)
 
-pacman::p_load(readxl, tidyverse, papaja, kableExtra, english, knitr, here, DescTools, wesanderson, ggpubr)
+pacman::p_load(readxl, tidyverse, papaja, kableExtra, english, knitr, here, DescTools, wesanderson, ggpubr, rcrossref)
 
 source(here::here("analysis", "00_functions.R"))
 
@@ -13,7 +13,10 @@ source(here::here("analysis", "00_functions.R"))
 
 df_mas<- read_xlsx(here::here("data", 
                               "mas_original_results.xlsx"),
-                   col_names = TRUE)
+                   col_names = TRUE) %>% 
+  mutate(publication_year = as.double(str_sub(ID, -4))) %>% 
+  mutate(publication_year = ifelse(is.na(publication_year), 2017, publication_year)) %>% 
+  mutate(ma_x = seq(1:nrow(.)))
 
 
 ####Descriptives####
@@ -94,10 +97,8 @@ df_reasons<- df_mas %>%
                                                       Additional details were sent and after some email exchanges there was no further response."))))) %>% 
   group_by(final_results) %>% 
   tally() %>% 
-  cbind(MultinomCI(.$n, conf.level = 0.95, method = "sisonglaz"))%>%
-  mutate(porc = sprintf("%0.0f%%", est * 100)) %>% 
-  rename("Reason" = final_results, "N" = n, "%" = porc) %>% 
-  select(Reason, N, "%")
+  rename("Reason" = final_results, "N" = n) %>% 
+  select(Reason, N)
   
 
 
@@ -171,19 +172,51 @@ df_software<- df_mas %>%
   group_by(software) %>% 
   tally()
 
+#Citation count
+
+df_paper<- df_mas %>% 
+  group_by(order) %>% 
+  slice(1)
+
+#citation_count<- cr_citation_count(doi = df_paper$doi)
+
+#Adding missing counts from Google Scholar
+
+#citation_count$count[25]<- 445
+#citation_count$count[40]<- 6
+
+#Both Crossref and Google Scholar retrieved on 20/03/2023
+
+#save(citation_count, file = here::here("results", "citation_count.Rdata"))
+
+#Loading citation count retrieved on 20/03/2023
+
+load(here::here("results", "citation_count.Rdata"))
+
+#Descriptives citation count
+
+cc_mean<- round(mean(citation_count$count),3)
[…]

### 2023-04-21 analysis/02_first_stage.R

@@ -272,7 +272,7 @@ for (j in 1:nrow(df_mas)) {
 
 #Merge the original results and reproduced results
 
-df_mas<- df_mas %>% 
+df_mas2<- df_mas %>% 
   cbind(rep_k, rep_g,
         rep_ll_g, rep_ul_g, rep_ac_g,
         rep_z, rep_q, rep_i2) %>% 
@@ -289,11 +289,11 @@ df_mas<- df_mas %>%
   mutate(decision_error = ifelse(original_ci_test==rep_ci_test, "no_error", "error")) %>% 
   mutate(decision_error = factor(decision_error))
 
-#save(df_mas, file = here::here("results", "first_stage", "first_stage_results.Rdata"))
+#save(df_mas2, file = here::here("results", "first_stage", "first_stage_results.Rdata"))
 
 ####Selecting meta-analysis to be revised due to issues in reproductions####
 
-df_to_rev<- df_mas %>% 
+df_to_rev<- df_mas2 %>% 
   filter(numerical_error == "error" | decision_error =="error") 
 
 

### 2023-04-21 analysis/03_second_stage.R

@@ -193,7 +193,7 @@ df_to_rev2<- df_mas_revised %>%
   rbind(re_analyzed_w_error) %>% 
   arrange(order)
 
-write.xlsx(df_to_rev2, here::here("results", "second_stage", "df_to_rev2.xlsx"))
+#write.xlsx(df_to_rev2, here::here("results", "second_stage", "df_to_rev2.xlsx"))
 
 df_to_scatter<- df_mas_revised %>% 
   filter(qualitative_check != "re-analyse") %>% 
@@ -218,7 +218,7 @@ df_stage2_results<-df_to_scatter
 #save(df_stage2_results, file = here::here("results", "second_stage", "second_stage_results.Rdata"))
 
 
-####Figure 4#####
+####Figure 5#####
 
 df_to_scatter_original_ci<- df_to_scatter %>% 
   select(LL_CI, UL_CI, decision_error, diff_ac) %>% 
@@ -235,39 +235,38 @@ df_to_scatter_ci<- inner_join(df_to_scatter_original_ci, df_to_scatter_rep_ci, b
 
 
 scatter_g<- scatter_match(df_to_scatter, x=df_to_scatter$summary_effect, y=df_to_scatter$rep_g, 
-                          shape = df_to_scatter$decision_error, shape_name = "Decision error:", shape_labels = c("Error", "No error"),
-                          size = 15,
+                          shape = df_to_scatter$decision_error, shape_name = "Decision error:", shape_labels = c("Yes", "No"),
+                          size = 2.3,size_constant = T,
                           title = "Summary effect") + 
-  theme(plot.margin = unit(c(0, 0, 3, 0), "lines"))
+  theme(plot.margin = unit(c(0, 0, 1.5, 0), "lines"))
 
 
 
 
 scatter_ci<- scatter_match2(df_to_scatter_ci, x=df_to_scatter_ci$value.x, y=df_to_scatter_ci$value.y, 
-                           shape = df_to_scatter_ci$decision_error.x, shape_name = "Decision error:", shape_labels = c("Error", "No error"), 
                            color = df_to_scatter_ci$original_bound, color_name = "Bound", color_labels = c("Lower", "Upper"),
-                           size = 15,
+                           size = 2.3, 
                            title = "Confidence Interval") +
   theme(plot.margin = unit(c(0, 0, 0, 0), "lines"))
 
-figure4<- ggarrange(scatter_g,
+figure5<- ggarrange(scatter_g,
                     scatter_ci,
                     labels = c("A", "B"),
[…]

### 2023-04-21 analysis/04_third_stage.R

@@ -92,14 +92,14 @@ df_to_reanalyse<- df_to_reanalyse %>%
   relocate(c(issues, qualitative_check), .after = last_col()) %>% 
   mutate(qualitative_check2= c(rep("rep", 7), "no_rep", "rep"))
 
-df_results_stage_3<- df_to_rev2 %>% 
+df_stage3_results<- df_to_rev2 %>% 
   filter(clarification_request_results != "Reply") %>% 
   mutate(qualitative_check2 = c(rep(NA, nrow(.)))) %>% 
   rbind(df_to_reanalyse) %>% 
   arrange(order)
 
 
-#save(df_results_stage_3, file = here::here("results", "third_stage", "third_stage_results.Rdata"))
+#save(df_stage3_results, file = here::here("results", "third_stage", "third_stage_results.Rdata"))
 
 
 

### 2023-04-21 analysis/05_figure4.R

@@ -1,0 +1,110 @@
+if(!require(pacman)){
+  install.packages("pacman")
+}
+
+library(pacman)
+
+if(!require(ggsankey)){
+  devtools::install_github("davidsjoberg/ggsankey")
+}
+
+library(pacman)
+
+
+pacman::p_load(tidyverse,
+               ggsankey)
+
+
+####Importing data####
+
+load(here::here("data", "first_stage", "data.Rdata"))
+load(here::here("results", "first_stage", "first_stage_results.Rdata"))
+load(here::here("results", "second_stage", "second_stage_results.Rdata"))
+load(here::here("results", "third_stage", "third_stage_results.Rdata"))
+
+#####Figure 4#####
+
+stage_0 <- df_mas %>% 
+  mutate("Process-reproduciblity (Data availability)" = ifelse(orign_data != "not_available", "Yes", "No")) %>% 
+  select(order, ID, ma_x, "Process-reproduciblity (Data availability)")
+
+
+stage_1<- df_mas2 %>% 
+  mutate(numerical_error = ifelse(numerical_error == "error", "Numerical error", "No error")) %>% 
+  mutate("Numerical and decision errors" = ifelse(decision_error == "error", "Decision error", numerical_error)) %>% 
+  select(order, ID, ma_x, "Numerical and decision errors")
+
+
+stage_2<- df_stage2_results %>% 
+  mutate(numerical_error = ifelse(numerical_error == "error", "Numerical error", "No error")) %>% 
+  mutate("Coding error and qualitative assessment" = ifelse(qualitative_check ==  "re-analyse" & numerical_error == "No error", "Reproduced after fixing a coding error",
+                       ifelse(qualitative_check == "rep", "Minor adjustment or approximately reproduced", 
+                              ifelse(decision_error == "error", "Decision error ", "Numerical error ")))) %>% 
+  select(order, ID, ma_x, "Coding error and qualitative assessment")
+
+
+stage_3<- df_stage3_results %>% 
+  select(order, ID, ma_x, clarification_request_results) %>% 
+  rename("Clarification request" = clarification_request_results)
+
+
+sankey_df<- left_join(stage_0, stage_1) %>% 
+  left_join(stage_2) %>% 
+  left_join(stage_3)
+
+# Select stage variables and make it long format
+sankey_df <- sankey_df %>%
+  select(`Process-reproduciblity (Data availability)`, `Numerical and decision errors`, 
[…]

### 2023-04-21 analysis/05_figure6.R

@@ -1,71 +1,0 @@
-if(!require(pacman)){
-  install.packages("pacman")
-}
-
-library(pacman)
-
-pacman::p_load(tidyverse,
-               wesanderson,
-               ggpubr)
-
-
-####Importing data####
-
-load(here::here("results", "first_stage", "first_stage_results.Rdata"))
-load(here::here("results", "second_stage", "second_stage_results.Rdata"))
-load(here::here("results", "third_stage", "third_stage_results.Rdata"))
-
-
-source(here::here("analysis", "00_functions.R"))
-
-
-#####Figure S1#####
-
-stage_1<- df_mas %>% 
-  mutate(numerical_error = ifelse(numerical_error == "error", "error", "no_error")) %>% 
-  group_by(numerical_error, decision_error) %>% 
-  tally() %>% 
-  mutate(Item = paste0(numerical_error," ", decision_error)) %>% 
-  mutate(Item = factor(Item)) %>% 
-  mutate(Item = fct_recode(Item, "Numerical and decision error" = "error error", "Numerical error" = "error no_error", "No error" = "no_error no_error")) %>% 
-  mutate(perc=n)
-
-
-stage_2<- df_stage2_results %>% 
-  mutate(numerical_error = ifelse(numerical_error == "error", "error", "no_error")) %>% 
-  mutate(Item = ifelse(qualitative_check ==  "re-analyse" & numerical_error == "no_error", "Reproduced after fixing a coding error",
-                       ifelse(qualitative_check == "rep", "Reproduced after minor adjustment", "Error"))) %>% 
-  group_by(Item) %>% 
-  tally() %>% 
-  mutate(Results = factor(Item)) %>% 
-  mutate(perc=n)
-
-
-stage_3<- df_results_stage_3 %>% 
-  mutate(Item = factor(clarification_request_results)) %>% 
-  group_by(ID, Item) %>% 
-  tally() %>% 
-  group_by(Item) %>% 
-  tally() %>% 
-  mutate(perc=n)
-
-Moonrise3 <-rev(wes_palette("Moonrise3", n=5))
-
-plt_stage1<-customized_barplot(stage_1, pal = Moonrise3[3:5], title = "", legend = "Result", width = .35, rate = FALSE) +
-  theme(plot.margin = unit(c(3, 0, 3, 0), "lines"))
-
[…]

### 2023-04-21 analysis/06_supplementary.R

@@ -1,18 +1,41 @@
 if(!require(tidyverse)){
-  install.packages("tidyverse")
+  install.packages("pacman")
 }
+library(pacman)
 
-library(tidyverse)
+pacman::p_load(readxl, tidyverse, kableExtra, here, questionr, pscl, irr)
 
-####Importing data####
+
+#####Inter-coder agreement#####
+
+#Importing data
+
+path<-here::here("data", "double_coding", "check_primary_data.xlsx") 
+
+dat<- lapply(excel_sheets(path), function(x) read_xlsx(path, sheet = x, col_names = F))
+
+dat_4_irr<- lapply(dat, function(x) data.frame(A = unlist(c(x[, 1:as.integer(ncol(x)/2 - 0.5)]), use.names = F), 
+                                               B = unlist(c(x[, as.integer(ncol(x)/2 + 1.5):ncol(x)]), use.names = F)))
+
+datasets_wo_error<- sapply(dat_4_irr, function(x) all(x$A == x$B, na.rm = T)) 
+
+icc_results<- lapply(dat_4_irr, function(x) icc(x, model = "twoway", type = "consistency", unit = "single"))
+
+icc_table<- data.frame(Paper = seq(1:21),
+                       ICC = round(unlist(lapply(icc_results, function (x) x$value)), 3),
+                       "Full agreement" = datasets_wo_error)
+
+
+####Sensibility analysis####
+
+#Importing data
 
 load(here::here("results", "first_stage", "first_stage_results.Rdata"))
 
-#####Figure S1#####
 
+#Figure S1
 
-
-df_mas <- df_mas %>% 
+df_mas2 <- df_mas2 %>% 
   mutate(diff_g_abs = summary_effect - rep_g) %>% 
   mutate(diff_ac_abs =  AC - rep_ac_g) %>%   
   mutate(numerical_error1 = ifelse(abs(diff_g_abs) >= 0.01 | abs(diff_ac_abs) >= 0.02 , "error", "no_error")) %>% 
@@ -23,17 +46,17 @@ df_mas <- df_mas %>%
   mutate(numerical_error =  ifelse(numerical_error == "error", "error", "no_error"))
 
 
-df_plot<- df_mas %>%
+df_plot<- df_mas2 %>%
   pivot_longer(c(numerical_error, numerical_error1, numerical_error2, numerical_error3, numerical_error4, numerical_error5), 
                names_to = "criteria") %>% 
-  select(51, 52) %>% 
[…]

### 2023-04-21 response_letter.Rmd
Revised version

@@
 Next, we provide point by point answers to the Reviewers’ comments and specify how we have addressed them in the revised manuscript.
+
+\newpage
 
@@
 
+\newpage
+
 # Reviewer \#2
@@
 
->Furthermore, 15 were labelled as \textcolor{blue}{approximately reproduced or reproduced with minor adjustment} in a qualitative check because the discrepancy was probably explained by rounding issues, inverted signs for results (when effect sizes were reported in absolute values) and primary data, minor reporting errors, or minor adjustments in the analytical scheme^[Full details in Supplementary File at (add link)].
+>Furthermore, 15 were labelled as \textcolor{blue}{approximately reproduced or reproduced with minor adjustment} in a qualitative check because the discrepancy was probably explained by rounding issues, inverted signs for results (when effect sizes were reported in absolute values) and primary data, minor reporting errors, or minor adjustments in the analytical scheme^[Full details in Supplementary File at https://osf.io/fjhpw].
 
@@
 Thanks again for your useful feedback, we really appreciate your help in improving the manuscript!
+
+\newpage
 

### 2023-04-21 submission.Rmd
Revised version

@@
 After this, `r nrow(filter(df_to_reanalyse, numerical_error != "error"))` were re-labelled as reproduced and `r nrow(filter(df_to_reanalyse, numerical_error == "error"))` still had relevant discrepancies.
-Furthermore, `r nrow(filter(df_mas_revised, qualitative_check == "rep"))` were labelled as \textcolor{blue}{approximately reproduced or reproduced with minor adjustment} in a qualitative check because the discrepancy was probably explained by rounding issues, inverted signs for results (when effect sizes were reported in absolute values) and primary data, minor reporting errors, or minor adjustments in the analytical scheme^[Full details in Supplementary File].
+Furthermore, `r nrow(filter(df_mas_revised, qualitative_check == "rep"))` were labelled as \textcolor{blue}{approximately reproduced or reproduced with minor adjustment} in a qualitative check because the discrepancy was probably explained by rounding issues, inverted signs for results (when effect sizes were reported in absolute values) and primary data, minor reporting errors, or minor adjustments in the analytical scheme^[Full details in Supplementary File at: https://osf.io/fjhpw].
 In the remaining `r nrow(filter(df_mas_revised, qualitative_check == "request_information"))`, and in the `r nrow(filter(df_to_reanalyse, numerical_error == "error"))` re-analysed again without success, some issues or relevant discrepancies without apparent explanation were found.

### 2023-04-21 submission.tex
Revised version

@@
 From a random sample of 100 papers containing at least one meta-analysis on the effectiveness of interventions in clinical psychology, 217 meta-analyses were selected.
-We first tried to retrieve the original data by recovering a data file, recoding the data from document files (pdf, doc), or requesting original data from authors.
+We first tried to retrieve the original data by recovering a data file, recoding the data from document files (pdf, doc), or requesting it from original authors.
 Second, through a multi-stage workflow, we tried to reproduce the main results of each meta-analysis using these data.
@@
 After this, 10 were re-labelled as reproduced and 7 still had relevant discrepancies.
-Furthermore, 15 were labelled as \textcolor{blue}{approximately reproduced or reproduced with minor adjustment} in a qualitative check because the discrepancy was probably explained by rounding issues, inverted signs for results (when effect sizes were reported in absolute values) and primary data, minor reporting errors, or minor adjustments in the analytical scheme\footnote{Full details in Supplementary File}.
+Furthermore, 15 were labelled as \textcolor{blue}{approximately reproduced or reproduced with minor adjustment} in a qualitative check because the discrepancy was probably explained by rounding issues, inverted signs for results (when effect sizes were reported in absolute values) and primary data, minor reporting errors, or minor adjustments in the analytical scheme\footnote{Full details in Supplementary File at: \url{https://osf.io/fjhpw}}.
 In the remaining 20, and in the 7 re-analysed again without success, some issues or relevant discrepancies without apparent explanation were found.

### 2023-04-21 response_letter.Rmd
Revised version

@@
 >Second, through a multi-stage workflow, we tried to reproduce the main results of each meta-analysis using these data.
-The original data were retrieved for 146 \textcolor{blue}{(67\%, 146/217)} meta-analyses from different sources.
-Of these, in the first stage 52 showed a discrepancy larger than 5% in the main results, \textcolor{blue}{in 10 of them, this discrepancy was solved after fixing a coding error and in 15 of them it was solved with minor adjustment or considered approximately reproduced in a qualitative assessment.} In the remaining 27 \textcolor{blue}{(18\%, 27/146)}, different issues were identified in an in-depth review of the papers, such as reporting inconsistencies, lack of some data, or transcription errors.
-\textcolor{blue}{Nevertheless, the numerical discrepancies produced by these issues were mostly minor, with little or no impact on the conclusions.} Current practices of data sharing in meta-analyses hamper the reusability of meta-analytic data.
-On the other hand, the implementation of new tools would help to avoid certain errors in the meta-analysis reporting process.
+The original data were retrieved for 146 \textcolor{blue}{(67\%, 146/217)} meta-analyses.
+Of these, 52 showed a discrepancy larger than 5% in the main results in the first stage.
+\textcolor{blue}{For 10 meta-analyses this discrepancy was solved after fixing a coding error and for 15 of them it was considered approximately reproduced in a qualitative assessment.} In the remaining 27 meta-analyses \textcolor{blue}{(18\%, 27/146)}, different issues were identified in an in-depth review of the papers, such as reporting inconsistencies, lack of data, or transcription errors.
+\textcolor{blue}{Nevertheless, the numerical discrepancies were mostly minor, with little or no impact on the conclusions.} Current practices of data sharing in meta-analyses hamper the reusability of meta-analytic data.
+The implementation of new tools would help to avoid certain errors in the meta-analysis reporting process.
 

### 2023-04-21 submission.Rmd
Revised version

@@
 abstract: |
-  Meta-analysis is one of the most useful and powerful research approaches, the relevance of which relies on its credibility.
+  Meta-analysis is one of the most useful research approaches, the relevance of which relies on its credibility.
 However, in recent years different concerns about the credibility of psychological research have emerged.
 Reproducibility of scientific results could be considered as the minimal threshold of it.
-In this study, our purpose was to assess the  reproducibility of a sample of published meta-analyses.
+Our purpose was to assess the reproducibility of a sample of published meta-analyses.
 From a random sample of 100 papers containing at least one meta-analysis on the effectiveness of interventions in clinical psychology, 217 meta-analyses were selected.
-We first tried to retrieve the original data by recovering a data file, recoding the data from document files (pdf, doc), or requesting it from original authors.
+We first tried to retrieve the original data by recovering a data file, recoding the data from document files, or requesting it from original authors.
 Second, through a multi-stage workflow, we tried to reproduce the main results of each meta-analysis using these data.
@@
 Of these, 52 showed a discrepancy larger than 5% in the main results in the first stage.
-\textcolor{blue}{For 10 meta-analyses this discrepancy was solved after fixing a coding error and for 15 of them it was solved with minor adjustment or considered approximately reproduced in a qualitative assessment.} In the remaining 27 meta-analyses\textcolor{blue}{(18\%, 27/146)}, different issues were identified in an in-depth review of the papers, such as reporting inconsistencies, lack of data, or transcription errors.
-\textcolor{blue}{Nevertheless, the numerical discrepancies produced by these issues were mostly minor, with little or no impact on the conclusions.} Current practices of data sharing in meta-analyses hamper the reusability of meta-analytic data.
+\textcolor{blue}{For 10 meta-analyses this discrepancy was solved after fixing a coding error and for 15 of them it was considered approximately reproduced in a qualitative assessment.} In the remaining 27 meta-analyses \textcolor{blue}{(18\%, 27/146)}, different issues were identified in an in-depth review of the papers, such as reporting inconsistencies, lack of data, or transcription errors.
+\textcolor{blue}{Nevertheless, the numerical discrepancies were mostly minor, with little or no impact on the conclusions.} Current practices of data sharing in meta-analyses hamper the reusability of meta-analytic data.
 The implementation of new tools would help to avoid certain errors in the meta-analysis reporting process.

### 2023-04-21 submission.tex
Revised version

@@
 \abstract{%
-Meta-analysis is one of the most useful and powerful research approaches, the relevance of which relies on its credibility.
+Meta-analysis is one of the most useful research approaches, the relevance of which relies on its credibility.
 However, in recent years different concerns about the credibility of psychological research have emerged.
 Reproducibility of scientific results could be considered as the minimal threshold of it.
-In this study, our purpose was to assess the reproducibility of a sample of published meta-analyses.
+Our purpose was to assess the reproducibility of a sample of published meta-analyses.
 From a random sample of 100 papers containing at least one meta-analysis on the effectiveness of interventions in clinical psychology, 217 meta-analyses were selected.
-We first tried to retrieve the original data by recovering a data file, recoding the data from document files (pdf, doc), or requesting it from original authors.
+We first tried to retrieve the original data by recovering a data file, recoding the data from document files, or requesting it from original authors.
 Second, through a multi-stage workflow, we tried to reproduce the main results of each meta-analysis using these data.
@@
 Of these, 52 showed a discrepancy larger than 5\% in the main results in the first stage.
-\textcolor{blue}{For 10 meta-analyses this discrepancy was solved after fixing a coding error and for 15 of them it was solved with minor adjustment or considered approximately reproduced in a qualitative assessment.} In the remaining 27 meta-analyses\textcolor{blue}{(18\%, 27/146)}, different issues were identified in an in-depth review of the papers, such as reporting inconsistencies, lack of data, or transcription errors.
-\textcolor{blue}{Nevertheless, the numerical discrepancies produced by these issues were mostly minor, with little or no impact on the conclusions.} Current practices of data sharing in meta-analyses hamper the reusability of meta-analytic data.
+\textcolor{blue}{For 10 meta-analyses this discrepancy was solved after fixing a coding error and for 15 of them it was considered approximately reproduced in a qualitative assessment.} In the remaining 27 meta-analyses \textcolor{blue}{(18\%, 27/146)}, different issues were identified in an in-depth review of the papers, such as reporting inconsistencies, lack of data, or transcription errors.
+\textcolor{blue}{Nevertheless, the numerical discrepancies were mostly minor, with little or no impact on the conclusions.} Current practices of data sharing in meta-analyses hamper the reusability of meta-analytic data.
 The implementation of new tools would help to avoid certain errors in the meta-analysis reporting process.

### 2023-04-24 response_letter.Rmd
Revised version

@@
 
-We don’t know if it’s possible to modify the form.
-The most relevant point on your suggestion is related to include a statement about how we determine our sample size.
-We have included the following statement (see p.
-8):
+We have modified in the resubmission form the answers to these prompts. Therefore, we have also included the “Reporting” subsection in the “Disclosures” section (see p. 7):
+
+>## Reporting
+\textcolor{blue}{Below we report how we determined our sample size, all data exclusions, all manipulations, and all measures in the study.}
+
+Accordingly, we have included information on how we determine our sample size. We have included the following statements (see p. 8):
 

### 2023-04-24 submission.Rmd
Revised version

@@
 
-# Method
+# Disclosures
 ## Preregistration
@@
 
+## Reporting
+
+\textcolor{blue}{Below we report how we determined our sample size, all data exclusions, all manipulations, and all measures in the study.}
+
+# Method
 ## Identification and selection of articles and meta-analyses 
@@
 First, we sought for the statistics \textcolor{blue}{used to compute primary effect sizes (e.g., means, sd)}; second, we sought for the primary effects sizes \textcolor{blue}{already computed} and their standard errors (or, alternatively, the sampling variances): finally, we sought for the primary effects sizes and their confidence limits, from which the standard errors were approximated as follows:
-
 $$se_i = (\frac{UB_i - LB_i}{2z_{\alpha/2}})$$
-
 with $se_i$ being the standard error of the ith effect size, $UB_i$ and $LB_i$ the upper and lower confidence limits of confidence interval for the ith effect size, and $z_{\alpha/2}$ the $(1 - {\alpha/2})\%$ percentile of the standard normal distribution (usually, $z_{\alpha/2} = 1.96$ assuming a two-sided 95% confidence interval).

### 2023-04-24 submission.tex
Revised version

@@
 
+\hypertarget{disclosures}{%
+\section{Disclosures}\label{disclosures}}
+
+\hypertarget{preregistration}{%
+\subsection{Preregistration}\label{preregistration}}
+
+The pre-data analysis protocol (\url{https://doi.org/10.17605/OSF.IO/79J2T}) was pre-registered on 19 October 2021. Any deviation from this protocol is explicitly acknowledged.
+
+\hypertarget{data-materials-and-online-resources}{%
+\subsection{Data, materials, and online resources}\label{data-materials-and-online-resources}}
+
+Data and analysis script code are openly available at: \url{https://osf.io/6cmzh/}
+
+\hypertarget{reporting}{%
+\subsection{Reporting}\label{reporting}}
+
+\textcolor{blue}{Below we report how we determined our sample size, all data exclusions, all manipulations, and all measures in the study.}
+
 \hypertarget{method}{%
 \section{Method}\label{method}}
-
-\hypertarget{preregistration}{%
-\subsection{Preregistration}\label{preregistration}}
-
-The pre-data analysis protocol (\url{https://doi.org/10.17605/OSF.IO/79J2T}) was pre-registered on 19 October 2021. Any deviation from this protocol is explicitly acknowledged.
-
-\hypertarget{data-materials-and-online-resources}{%
-\subsection{Data, materials, and online resources}\label{data-materials-and-online-resources}}
-
-Data and analysis script code are openly available at: \url{https://osf.io/6cmzh/}
 
@@
 First, we sought for the statistics \textcolor{blue}{used to compute primary effect sizes (e.g., means, sd)}; second, we sought for the primary effects sizes \textcolor{blue}{already computed} and their standard errors (or, alternatively, the sampling variances): finally, we sought for the primary effects sizes and their confidence limits, from which the standard errors were approximated as follows:
-
 \[se_i = (\frac{UB_i - LB_i}{2z_{\alpha/2}})\]
-
 with \(se_i\) being the standard error of the ith effect size, \(UB_i\) and \(LB_i\) the upper and lower confidence limits of confidence interval for the ith effect size, and \(z_{\alpha/2}\) the \((1 - {\alpha/2})\%\) percentile of the standard normal distribution (usually, \(z_{\alpha/2} = 1.96\) assuming a two-sided 95\% confidence interval).

### 2023-06-21 revision/response_letter2.Rmd
Second revision

---
title       : "Reproducibility of published meta-analyses on clinical psychological
  interventions"
authors     : "Ruben Lopez-Nicolas et al."
journal     : "Advances in Methods and Practices in Psychological Science"
manuscript  : "AMPPS-22-0119"

class       : "draft"
output      : papaja::revision_letter_pdf
---

Dear Dr. Flake,

Thank you again for taking your time reviewing and handling our manuscript. Next, we provide point by point answers to your comments and specify how we have addressed them in the revised manuscript.

# Comments

\RC {The Abstract:

Thank you for clarifying the results in the abstract. I think it is an improvement, but I'm concerned the take-aways are unclear and would clarify a few points in the abstract.

 -Your revised text says that 10 discrepancies were resolved  "after fixing a coding error" -- made by who, the authors of the meta-analysis or are these ones where you found your own error?}

Here, we are referring to coding errors made by ourselves when we retrieved data from document formats. We agree that it could be a bit confusing. We have added the following clarification (see Abstract):

>For 10 meta-analyses this discrepancy was solved after fixing a coding error \textcolor{blue}{of our data retrieval process}...

\RC{-A summary sentence that clarifies the major takeaway in connection to data availability and then reproduction would be helpful. From my reading of the results it seems that at the end, there were 27 that were never resolved, meaning that the biggest threat to reproduction is data can't be located, once you can get the data the majority of studies can be reproduced (though not perfectly, which is important).}

We have added a few additional sentences in the abstract related to data availability to highlight this issue, mention changes over time, and point out the type of data availability (see Abstract):

>The original data were retrieved for 67% (146/217) meta-analyses. \textcolor{blue}{While this rate showed an improvement over the years, in only 5\% of these cases was it possible to retrieve a data file ready for reuse.} Of these 146, 52 showed a discrepancy larger than 5% in the main results in the first stage. For 10 meta-analyses this discrepancy was solved after fixing a coding error \textcolor{blue}{of our data retrieval process} and for 15 of them it was considered approximately reproduced in a qualitative assessment. In the remaining meta-analyses (18%, 27/146), different issues were identified in an in-depth review, such as reporting inconsistencies, lack of data, or transcription errors. Nevertheless, the numerical discrepancies were mostly minor, with little or no impact on the conclusions. \textcolor{blue}{Overall, one of the biggest threats to the reproducibility of meta-analysis is related to data availability and current data sharing practices in meta-analysis.}

\RC{Main text:

-The last sentence on page 7 isn't clear, reproducing primary effect sizes versus the ones already coded by the original authors – the distinction is more clear on page 9, but please revise this sentence to be very direct as to what you are referring to a bit earlier in the paper.}

Indeed, this sentence isn’t accurate. We have rephrased it (see p. 7):

>...Where previous work focused on the reproducibility of primary effect sizes \textcolor{blue}{by recoding data from primary studies}, we explored meta-analysis outcome reproducibility using the primary \textcolor{blue}{data} already coded by the original authors. \textcolor{blue}{Therefore, we attempted to retrieve the data shared by the authors of the meta-analysis.}

\RC{-Even on page 9, I still think a bit more could be clarified on page 9 to make very obvious what was in the primary original study, in the meta-analysis done by the meta analytic authors, and then what you sought to do.}

In the same vein, we have added a clarification in this section (see p. 9):

>In order to be able to reproduce meta-analyses of aggregate data, primary-level^[By primary-level data we mean aggregate data from included primary studies.] effects sizes and their associated standard errors are required. These are generally computed from statistics retrieved from the primary studies such as means, standard deviations or sample sizes. We attempted to retrieve the least processed data \textcolor{blue}{shared by the authors of the meta-analysis...}

\RC{Main Text, Supplement, and discussion:

 I didn't find the logistic regression without any descriptive information in the supplement to be very helpful. I would like to see more descriptive information in the main text and the supplement and for the discussion to be updated accordingly.

 -In the main manuscript I think it would be best to provide some descriptive information about the publication year of the MA and data retrieval. Given you mention this in the discussion, having some results in the main paper is helpful, but I do not think a full statistical analysis is needed.  The year and data availability would be more useful with descriptive statistics – I'm thinking a crosstabs or a graph that shows the rate of availability by year and the sample size. We cannot make strong inferences here given the limited data, but you can cautiously note a trend.}

Following your recommendation, we have complemented Figure 3a by adding three new bars displaying rates for different time periods (see Figure 3, p. 16).

Additionally, we have mentioned that in the results section (see p. 13 and 14):

>Figure 3 summarizes the primary data retrieval results. Based on the availability of primary data, either retrieved directly from the paper or upon request, 146 meta-analyses 146 meta-analyses (67%, see Fig. 3a) were labelled as process reproducible. \textcolor{blue}{Additionally, as the time span covered is fairly wide, the process reproducible rate was also computed for different time periods. The meta-analyses were grouped into five-year periods, except for the initial period, which was grouped into a ten-year period due to the limited number of meta-analyses available during the first five-year period, which consisted of only five meta-analyses. The process reproducibility rate was 41\%, (12/29), 59\%, (44/75), and 80\%, (90/113) for meta-analyses published between 2000 and 2010, 2011 and 2015, and 2016 and 2020, respectively (see Fig. 3a). This trend is further explored in the Supplementary file available at: https://osf.io/fjhpw.}

Furthermore, we have slightly modified the discussion by mentioning the new results reported in the main text (see p. 22):

>Nevertheless, a more positive sign comes from the positive association between publication year and the possibility of retrieving the data. \textcolor{blue}{The results tentatively suggest a trend of improving data availability over the years, with a notable rate of 80\% observed in meta-analyses published between 2016 and 2020...}

\RC{-You can keep the logistic regression if you'd like, but without sample size info by year and basic descriptive statistics, it isn't very interpretable, so this needs included with some detail in the supplement as well. Converting the coefficients into odds and then percentages would also help.}

We have also added more information in this regard in the supplementary file (see p. 4 in Supplementary file):

>\textcolor{blue}{The publication year range of the included meta-analyses in our study is quite extensive. The initial pool, from which we randomly selected a sample, comprised meta-analytic reports published between 2000 and 2020, encompassing a span of two decades. For our analysis, we focused on a random sample of 100 of these meta-analytic reports.  From the 100 included reports, 217 independent meta-analyses were selected following the criteria explained in the ‘Identification and selection of articles and meta-analyses’ section of the main paper. These meta-analyses were published between 2001 and 2020 (mean = 2015.04; sd = 4.05; median =
2016; interquartile range = 2012-2016). As an unrestricted random sample, the publication year distribution is clearly left-skewed, with 92.2\% of the included meta-analyses published between 2010 and 2020 (see Figure 2 of the main paper for the full distribution).}

>\textcolor{blue}{As shown in the main paper (see Figure 3a), there appears to be an improvement in the rate of data availability over the years. The overall data availability rate for the full sample was found to be 67\%. However, when examining meta-analyses published within specific time periods, the rates varied. For meta-analyses published between 2000 and 2010, the data availability rate was 41\%. For those published between 2011 and 2015, the rate increased to 59\%. Notably, meta-analyses published between 2016 and 2020 exhibited the highest data availability rate of 80\%. These findings suggest a positive trend of improved data availability in more recent years.}

Moreover, a new column reporting the percentage change associated with the ORs has been added to Table 2 of the Supplementary file:

>Based on the results of the four models, there seems to be an association between the publication year and the possibility of retrieving primary data from a meta-analysis. We found that all 4 ORs computed were > 1, indicating a higher probability of retrieving data the more recent the publication year of the meta-analysis. \textcolor{blue}{Specifically, the odds increased from 11.85\% to 34.46\% per year...}

### 2023-06-21 submission.Rmd
Second revision

@@
   Meta-analysis is one of the most useful research approaches, the relevance of which relies on its credibility.
-However, in recent years different concerns about the credibility of psychological research have emerged.
-Reproducibility of scientific results could be considered as the minimal threshold of it.
-Our purpose was to assess the reproducibility of a sample of published meta-analyses.
-From a random sample of 100 papers containing at least one meta-analysis on the effectiveness of interventions in clinical psychology, 217 meta-analyses were selected.
+Reproducibility of scientific results could be considered as the minimal threshold of this credibility.
+We assessed the reproducibility of a sample of meta-analyses published between 2000-2020.
+From a random sample of 100 papers reporting results of meta-analyses of interventions in clinical psychology, 217 meta-analyses were selected.
 We first tried to retrieve the original data by recovering a data file, recoding the data from document files, or requesting it from original authors.
-Second, through a multi-stage workflow, we tried to reproduce the main results of each meta-analysis using these data.
-The original data were retrieved for 146 \textcolor{blue}{(67\%, 146/217)} meta-analyses.
-Of these, 52 showed a discrepancy larger than 5% in the main results in the first stage.
-\textcolor{blue}{For 10 meta-analyses this discrepancy was solved after fixing a coding error and for 15 of them it was considered approximately reproduced in a qualitative assessment.} In the remaining 27 meta-analyses \textcolor{blue}{(18\%, 27/146)}, different issues were identified in an in-depth review of the papers, such as reporting inconsistencies, lack of data, or transcription errors.
-\textcolor{blue}{Nevertheless, the numerical discrepancies were mostly minor, with little or no impact on the conclusions.} Current practices of data sharing in meta-analyses hamper the reusability of meta-analytic data.
-The implementation of new tools would help to avoid certain errors in the meta-analysis reporting process.
+Second, through a multi-stage workflow, we tried to reproduce the main results of each meta-analysis.
+The original data were retrieved for 67% (146/217) meta-analyses.
+\textcolor{blue}{While this rate showed an improvement over the years, in only 5\% of these cases was it possible to retrieve a data file ready for reuse.} Of these 146, 52 showed a discrepancy larger than 5% in the main results in the first stage.
+For 10 meta-analyses this discrepancy was solved after fixing a coding error \textcolor{blue}{of our data retrieval process} and for 15 of them it was considered approximately reproduced in a qualitative assessment.
+In the remaining meta-analyses (18%, 27/146), different issues were identified in an in-depth review, such as reporting inconsistencies, lack of data, or transcription errors.
+Nevertheless, the numerical discrepancies were mostly minor, with little or no impact on the conclusions.
+\textcolor{blue}{Overall, one of the biggest threats to the reproducibility of meta-analysis is related to data availability and current data sharing practices in meta-analysis.}
 
@@
 Figure 1 displays a summary of the basic meta-analysis pipeline through a flowchart, outlining the different stages and listing previous work that has explored different facets of reproducibility of these, as well as a summary of the required elements to be able to reproduce each stage.
-\textcolor{blue}{In this project we focus on the last stage, related to the statistical analysis and quantitative results of the synthesis.}
+In this project we focus on the last stage, related to the statistical analysis and quantitative results of the synthesis.
 
@@
 
-Reproducibility analysis \textcolor{blue}{of reported quantitative results} typically uses the original data available from the original authors [e.g., @artner2020; @hardwicke2021; @hardwicke2018].
+Reproducibility analysis of reported quantitative results typically uses the original data available from the original authors [e.g., @artner2020; @hardwicke2021; @hardwicke2018].
 This puts the focus of the assessment at factors such as the reusability of the available data, challenges for the reconstruction of the original analysis scheme, reporting errors, etc.
@@
 Second, we verified the outcome reproducibility of the meta-analyses that were process-reproducible using the available data.
-Where previous work focused on the reproducibility of primary effect sizes, we explored meta-analysis outcome reproducibility using the primary effects sizes already coded by the original authors.
+Where previous work focused on the reproducibility of primary effect sizes \textcolor{blue}{by recoding data from primary studies}, we explored meta-analysis outcome reproducibility using the primary \textcolor{blue}{data} already coded by the original authors.
+\textcolor{blue}{Therefore, we attempted to retrieve the data shared by the authors of the meta-analysis.}
 
@@
 
-\textcolor{blue}{Below we report how we determined our sample size, all data exclusions, all manipulations, and all measures in the study.}
+Below we report how we determined our sample size, all data exclusions, all manipulations, and all measures in the study.
 
@@
 The full search strategies and a summary of the screening process are available at: https://osf.io/z5vrn/, and the workflow of the random selection process is available at: https://osf.io/cp293/.
-\textcolor{blue}{This sample size was based on our judgement of an acceptable trade-off between informativeness and feasibility.}
-From these 100 articles, each independent \textcolor{blue} {pairwise meta-analytic model of aggregate data fitted} on at least 10 primary studies was selected.
+This sample size was based on our judgement of an acceptable trade-off between informativeness and feasibility.
+From these 100 articles, each independent pairwise meta-analytic model of aggregate data fitted on at least 10 primary studies was selected.
 In case no meta-analysis reported in a paper had at least 10 studies, the meta-analysis with the highest number of primary studies was selected, which was the case for `r n_mas_less_10` of the articles included in this report.
-\textcolor{blue}{This criterion was established to focus on the main meta-analyses of each paper, based on the assumption that the search strategies would be designed to maximise the number of primary studies included that were related to the main aims of the paper.}
+This criterion was established to focus on the main meta-analyses of each paper, based on the assumption that the search strategies would be designed to maximise the number of primary studies included that were related to the main aims of the paper.
 
@@
 ## Retrieval of primary data
-In order to be able to reproduce meta-analyses of \textcolor{blue}{aggregate data, primary-level}^[By primary-level data we mean aggregate data from included primary studies.] effects sizes and their associated standard errors are required.
+In order to be able to reproduce meta-analyses of aggregate data, primary-level^[By primary-level data we mean aggregate data from included primary studies.] effects sizes and their associated standard errors are required.
 These are generally computed from statistics retrieved from the primary studies such as means, standard deviations or sample sizes.
-We attempted to retrieve the least processed data possible.
-First, we sought for the statistics \textcolor{blue}{used to compute primary effect sizes (e.g., means, sd)}; second, we sought for the primary effects sizes \textcolor{blue}{already computed} and their standard errors (or, alternatively, the sampling variances): finally, we sought for the primary effects sizes and their confidence limits, from which the standard errors were approximated as follows:
+We attempted to retrieve the least processed data \textcolor{blue}{shared by the authors of the meta-analysis.} First, we sought for the statistics used to compute primary effect sizes (e.g., means, sd); second, we sought for the primary effects sizes already computed and their standard errors (or, alternatively, the sampling variances): finally, we sought for the primary effects sizes and their confidence limits, from which the standard errors were approximated as follows:
 $$se_i = (\frac{UB_i - LB_i}{2z_{\alpha/2}})$$
@@
 
-\textcolor{blue}{On the other hand, efforts were also made to retrieve the most reusable data possible.} First, we searched for machine-readable data files through links leading to third-party repositories or in supplementary material hosted by the journal.
+On the other hand, efforts were also made to retrieve the most reusable data possible.
+First, we searched for machine-readable data files through links leading to third-party repositories or in supplementary material hosted by the journal.
 Second, we looked for available data through tables or forest plots in the meta-analytic report itself, or in supplementary material.
@@
 If the software used was not reported, we inferred this information from the default settings of the most used software in the sample, which was *Comprehensive Meta-Analysis*.
-\textcolor{blue}{We designed this procedure to reconstruct the original analytical scheme when the original analysis script was not available instead of trying to request it from the original authors due to: (a) not necessarily all authors of included meta-analyses will actually have an analysis script to share, because many might have used point and click software, and (b) we expected analysis script availability to be very low, and requesting it would have meant sending request for virtually every paper included in our re-analysis.}
+We designed this procedure to reconstruct the original analytical scheme when the original analysis script was not available instead of trying to request it from the original authors due to: (a) not necessarily all authors of included meta-analyses will actually have an analysis script to share, because many might have used point and click software, and (b) we expected analysis script availability to be very low, and requesting it would have meant sending request for virtually every paper included in our re-analysis.
 
@@
 ## Data collection procedure 
-\textcolor{blue}{Data collection procedure was carried out by five of the authors.} At a first pilot stage, a random sample of five articles of the total pool was independently coded by the five members and, subsequently, in a series of meetings, disagreements between the coders were resolved by consensus.
+Data collection procedure was carried out by five of the authors.
+At a first pilot stage, a random sample of five articles of the total pool was independently coded by the five members and, subsequently, in a series of meetings, disagreements between the coders were resolved by consensus.
 Next, the initial pool of 100 included articles was split among four coders, 25 articles each.
@@
 Disagreements were resolved by consensus and by double-checking the original materials.
-\textcolor{blue}{Details about inter-coder agreement are reported in the Supplementary file.}
+Details about inter-coder agreement are reported in the Supplementary file.
 
 ## Reproducibility outcomes
-Each meta-analysis was labelled using the following \textcolor{blue}{two-level}^[This hierarchy is a minor deviation from the pre-registered protocol.
+Each meta-analysis was labelled using the following two-level^[This hierarchy is a minor deviation from the pre-registered protocol.
 It is essentially the same and the results are identical.
 It was introduced to improve clarity.] reproducibility success scheme.
-\textcolor{blue}{First, each meta-analysis was labelled as: (a) process-reproducible; and (b) not process-reproducible.
-In our study, not process-reproducible refers to situations where we were unable to access the primary data neither through direct extraction nor upon request}^[Process reproducibility, as described above, could imply a different situation if more conditions need to be met to proceed with the reproduction attempt.
+First, each meta-analysis was labelled as: (a) process-reproducible; and (b) not process-reproducible.
+In our study, not process-reproducible refers to situations where we were unable to access the primary data neither through direct extraction nor upon request^[Process reproducibility, as described above, could imply a different situation if more conditions need to be met to proceed with the reproduction attempt.
 In our study, this is equivalent to data availability due to our design and the stage of the meta-analysis pipeline we focused on.].
-\textcolor{blue}{Second, those labelled as process-reproducible} were labelled as: (a) reproducible; (b) numerical error; and (c) decision error.
+Second, those labelled as process-reproducible were labelled as: (a) reproducible; (b) numerical error; and (c) decision error.
 Similar to previous studies (Artner et al., 2020; Hardwicke et al., 2018, 2021) an index of numerical error was computed (see Protocol https://osf.io/tq4uf/).
@@
 
-\textcolor{blue}{Finally, the association between publication year and the possibility of retrieving the data in one of the ways conducted in this project were explored by fitting binary logistic regression models with publication year as predictor and process-reproducibility as dependent variable.
+Finally, the association between publication year and the possibility of retrieving the data in one of the ways conducted in this project were explored by fitting binary logistic regression models with publication year as predictor and process-reproducibility as dependent variable.
 We quantified the strength of the association by calculating odds ratios and 95\% confidence intervals based on the profile likelihood.
 These exploratory analyses were  not pre-registered.
-Details and results are reported in Supplementary file.}
+Details and results are reported in Supplementary file.
 
@@
 From the 100 included papers, `r n_mas_total` independent meta-analyses were selected following the criteria explained above.
-These meta-analyses included `r round(k_mean, 2)` primary studies on average (`r sprintf("sd = %0.2f; median = %0.0f; interquartile range = %0.0f-%0.0f; range = %0.0f-%0.0f)", k_sd, k_median, k_q1, k_q3, range[1], range[2])`), \textcolor{blue}{and were cited `r round(cc_mean, 2)` times on average (`r sprintf("sd = %0.2f; median = %0.0f; interquartile range = %0.0f-%0.0f; range = %0.0f-%0.0f)", cc_sd, cc_median, cc_q1, cc_q3, cc_range[1], cc_range[2])`}^[Citation counts were retrieved from CrossRef API using the *rcrossref* package [@rcrossref].
+These meta-analyses included `r round(k_mean, 2)` primary studies on average (`r sprintf("sd = %0.2f; median = %0.0f; interquartile range = %0.0f-%0.0f; range = %0.0f-%0.0f)", k_sd, k_median, k_q1, k_q3, range[1], range[2])`, and were cited `r round(cc_mean, 2)` times on average (`r sprintf("sd = %0.2f; median = %0.0f; interquartile range = %0.0f-%0.0f; range = %0.0f-%0.0f)", cc_sd, cc_median, cc_q1, cc_q3, cc_range[1], cc_range[2])`^[Citation counts were retrieved from CrossRef API using the *rcrossref* package [@rcrossref].
 For two cases in which CrossRef did not return data, citation counts were consulted in Google Scholar.
 Both queries were done on 20/03/2023.].
-Figure 2 displays the distribution of number of primary studies among the meta-analyses included in our sample \textcolor{blue}{(panel A), the publication year distribution among the papers included in our sample (panel B) as well as the citation count distribution of those papers (panel C).} Original results and characteristics of these meta-analyses are available at: https://osf.io/8jzbk
+Figure 2 displays the distribution of number of primary studies among the meta-analyses included in our sample (panel A), the publication year distribution among the papers included in our sample (panel B) as well as the citation count distribution of those papers (panel C).
+Original results and characteristics of these meta-analyses are available at: https://osf.io/8jzbk
 
@@
 3a) were labelled as process reproducible.
+\textcolor{blue}{Additionally, as the time span covered is fairly wide, the process reproducible rate was also computed for different time periods.
+The meta-analyses were grouped into five-year periods, except for the initial period, which was grouped into a ten-year period due to the limited number of meta-analyses available during the first five-year period, which consisted of only five meta-analyses.
+The process reproducibility rate was }`r sprintf("%0.0f%%, (%0.0f/%0.0f)", df_process_rep2$perc[2]*100, df_process_rep2$n[2], sum(df_process_rep2$n))`, `r sprintf("%0.0f%%, (%0.0f/%0.0f)", df_process_rep3$perc[2]*100, df_process_rep3$n[2], sum(df_process_rep3$n))`, and `r sprintf("%0.0f%%, (%0.0f/%0.0f)", df_process_rep4$perc[2]*100, df_process_rep4$n[2], sum(df_process_rep4$n))` \textcolor{blue}{for meta-analyses published between 2000 and 2010, 2011 and 2015, and 2016 and 2020, respectively (see Fig.
+3a).
+This trend is further explored in the Supplementary file available at: https://osf.io/fjhpw.}
+
 Of these `r df_process_rep$n[2]` meta-analyses, in about half of the cases the primary data was retrieved from a forest plot in the paper itself and in about a third of the cases the primary data was retrieved from supplementary files (see Fig.
@@
 In most cases, when the meta-analytic data was available, it was shared in document formats.
-Data \textcolor{blue}{were retrieved from} tables or forest plots in *pdf* or *docx* format—either in the document itself or in the supplementary materials—\textcolor{blue}{in} `r sprintf("%0.0f%% (%0.0f/%0.0f)", (df_source_primary_data$perc[3]+df_source_primary_data$perc[4]+df_source_primary_data$perc[6])*100, df_source_primary_data$n[3]+df_source_primary_data$n[4]+df_source_primary_data$n[6], sum(df_source_primary_data$n))` \textcolor{blue}{of the cases}.
+Data were retrieved from tables or forest plots in *pdf* or *docx* format—either in the document itself or in the supplementary materials—in `r sprintf("%0.0f%% (%0.0f/%0.0f)", (df_source_primary_data$perc[3]+df_source_primary_data$perc[4]+df_source_primary_data$perc[6])*100, df_source_primary_data$n[3]+df_source_primary_data$n[4]+df_source_primary_data$n[6], sum(df_source_primary_data$n))` of the cases.
 This required a manual recoding of the primary data to be able to reuse them.
@@
 tables listing all the primary studies included with their characteristics), the meta-analysis associated with each data entry was not always obvious, leading to the time-consuming task of matching each data entry with each independent meta-analytic result reported in the paper.
-There were only `r df_source_primary_data$n[2]` meta-analyses (from `r words(sum(df_data_downloaded$Item))` different papers) of the `r df_process_rep$n[2]` meta-analyses labelled as process reproducible (`r sprintf("%0.0f%%", df_source_primary_data$perc[2]*100)`), where the task of retrieving the data required simply downloading the data in an machine-readable data file format.
+There were only `r df_source_primary_data$n[1]` meta-analyses (from `r words(sum(df_data_downloaded$Item))` different papers) of the `r df_process_rep$n[2]` meta-analyses labelled as process reproducible (`r sprintf("%0.0f%%", df_source_primary_data$perc[1]*100)`), where the task of retrieving the data required simply downloading the data in an machine-readable data file format.
 On the other hand, as shown in Figure 3c, when the necessary data was not available, retrieving it upon request to the original authors led to a low response rate.
 
-``` {r, fig.width = 10, fig.height=11, fig.cap="Percentage of (a) process-reproducible meta-analyses; (b) different types of sources of original data; (c) data request results."}
+``` {r, fig.width = 10, fig.height=13, fig.cap="Percentage of (a) process-reproducible meta-analyses; (b) different types of sources of original data; (c) data request results."}
 
@@
 After this, `r nrow(filter(df_to_reanalyse, numerical_error != "error"))` were re-labelled as reproduced and `r nrow(filter(df_to_reanalyse, numerical_error == "error"))` still had relevant discrepancies.
-Furthermore, `r nrow(filter(df_mas_revised, qualitative_check == "rep"))` were labelled as \textcolor{blue}{approximately reproduced or reproduced with minor adjustment} in a qualitative check because the discrepancy was probably explained by rounding issues, inverted signs for results (when effect sizes were reported in absolute values) and primary data, minor reporting errors, or minor adjustments in the analytical scheme^[Full details in Supplementary File at: https://osf.io/fjhpw].
+Furthermore, `r nrow(filter(df_mas_revised, qualitative_check == "rep"))` were labelled as approximately reproduced or reproduced with minor adjustment in a qualitative check because the discrepancy was probably explained by rounding issues, inverted signs for results (when effect sizes were reported in absolute values) and primary data, minor reporting errors, or minor adjustments in the analytical scheme^[Full details in Supplementary File at: https://osf.io/fjhpw].
 In the remaining `r nrow(filter(df_mas_revised, qualitative_check == "request_information"))`, and in the `r nrow(filter(df_to_reanalyse, numerical_error == "error"))` re-analysed again without success, some issues or relevant discrepancies without apparent explanation were found.
@@
 As shown in Figures 5 and 6, the discrepancies found in the heterogeneity statistic $I^2$ are larger than those found in the summary effects and their confidence intervals.
-\textcolor{blue}{The Pearson's correlation between the summary effect and $I^2$ discrepancies was .172.} The lack of precision of the available data (rounded data) or incomplete information on aspects such as the tau-squared estimator applied seem to have a substantial impact on the reproducibility of this result.
+The Pearson's correlation between the summary effect and $I^2$ discrepancies was .172.
+The lack of precision of the available data (rounded data) or incomplete information on aspects such as the tau-squared estimator applied seem to have a substantial impact on the reproducibility of this result.
 
@@
 Also, in a paper where primary data were available in both a table and a forest plot, minor inconsistencies were found between the primary data of the table and the forest plot.
-\textcolor{blue}{These examples of inconsistencies in original results or data were found in 4 cases (3\%, 4/146).} These appeared to be typos.
+These examples of inconsistencies in original results or data were found in 4 cases (3%, 4/146).
+These appeared to be typos.
 Furthermore, some inconsistencies were found with respect to the number of primary studies included in each meta-analysis.
@@
 
-\textcolor{blue}{A more positive sign comes from the positive association between publication year and the possibility of retrieving the data that was observed in an exploratory analysis in the supplementary materials.
-This tentatively suggests that data-availability is improving over time.
-This observation could be related to the existence of well-established meta-analysis reporting guidelines.
-For instance, the first PRISMA guideline} [@moher2009] \textcolor{blue}{encouraged meta-analyst to report results of primary studies (e.g.
-primary effect sizes and their confidence interval through a forest plot, as was a common scenario among the cases included in this project), and the latest PRISMA guideline} [@page2021] \textcolor{blue}{which puts more emphasis on appropriate data sharing through data files ready for reuse.} At the same time in only 5% of the cases where data were retrieved in our sample were we able to retrieve the data in a machine-readable data file that was ready for reuse (e.g., *csv*, *xlsx*).
+Nevertheless, a more positive sign comes from the positive association between publication year and the possibility of retrieving the data.
+\textcolor{blue}{The results tentatively suggest a trend of improving data availability over the years, with a notable rate of 80\% observed in meta-analyses published between 2016 and 2020.} This observation could be related to the existence of well-established meta-analysis reporting guidelines.
+For instance, the first PRISMA guideline [@moher2009] encouraged meta-analyst to report results of primary studies (e.g.
+primary effect sizes and their confidence interval through a forest plot, as was a common scenario among the cases included in this project), and the latest PRISMA guideline [@page2021] which puts more emphasis on appropriate data sharing through data files ready for reuse.
+At the same time in only 5% of the cases where data were retrieved in our sample were we able to retrieve the data in a machine-readable data file that was ready for reuse (e.g., *csv*, *xlsx*).
 Most often the data had to be retrieved from files in document format (e.g., *docx*, *pdf*).
@@
 Word), we observed examples where this introduced another source of error.
-\textcolor{blue}{The foregoing discussion raises a key point about how time consuming the appraisal of meta-analytic reproducibility currently is, and how efficiency would be improved by having open access to the underlying meta-analytic data in data file formats ready for reuse.
-The latest PRISMA guidelines, along with some initiatives that promote appropriate data sharing} [e.g.
-@wilkinson2016] \textcolor{blue}{have the potential to generate significant improvements in the re-use of meta-analytic data in the years ahead.
-In this regard, our results provide a useful baseline for future assessments.}
+The foregoing discussion raises a key point about how time consuming the appraisal of meta-analytic reproducibility currently is, and how efficiency would be improved by having open access to the underlying meta-analytic data in data file formats ready for reuse.
+The latest PRISMA guidelines, along with some initiatives that promote appropriate data sharing [e.g.
+@wilkinson2016] have the potential to generate significant improvements in the re-use of meta-analytic data in the years ahead.
+In this regard, our results provide a useful baseline for future assessments.
 
@@
 Because this cut-off is arbitrary, we have tried to focus more on possible issues in the results that fell above this margin, than on establishing a exact ratio of non-reproduced meta-analyses based on this arbitrary cut-off.
-\textcolor{blue}{Finally, we only examined meta-analyses in clinical psychology as this is one of the areas that produces the most meta-analyses in psychology and these meta-analyses have a direct impact on applied practice, but it is unknown to which extent our conclusions generalize to meta-analyses in other sub-disciplines in psychology.}
+Finally, we only examined meta-analyses in clinical psychology as this is one of the areas that produces the most meta-analyses in psychology and these meta-analyses have a direct impact on applied practice, but it is unknown to which extent our conclusions generalize to meta-analyses in other sub-disciplines in psychology.
 
@@
 ## Funding 
-This research has been funded with a grant from the Spanish Ministry of Science and Innovation (Project PID2019-104080GB-I00/AEI/10.13039/501100011033, FEDER funds) and by the Spanish Ministry of Universities (predoctoral grant: FPU18/04805).
+This research has been funded with a grant from the Spanish Ministry of Science and Innovation (Project PID2019-104080GB-I00/AEI/10.13039/501100011033, and PID2019-104033GA-I00/MCIN/AEI/10.13039/501100011033, FEDER funds) and by the Spanish Ministry of Universities (predoctoral grant: FPU18/04805).
 

### 2023-06-21 submission.tex
Second revision

@@
 \usepackage{amsmath,amssymb}
-\usepackage{lmodern}
 \usepackage{iftex}
@@
 \else % if luatex or xetex
-  \usepackage{unicode-math}
+  \usepackage{unicode-math} % this also loads fontspec
   \defaultfontfeatures{Scale=MatchLowercase}
   \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
+\fi
+\usepackage{lmodern}
+\ifPDFTeX\else
+  % xetex/luatex font selection
 \fi
@@
 \IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\urlstyle{same} % disable monospaced font for URLs
+\urlstyle{same}
 \hypersetup{
@@
 Meta-analysis is one of the most useful research approaches, the relevance of which relies on its credibility.
-However, in recent years different concerns about the credibility of psychological research have emerged.
-Reproducibility of scientific results could be considered as the minimal threshold of it.
-Our purpose was to assess the reproducibility of a sample of published meta-analyses.
-From a random sample of 100 papers containing at least one meta-analysis on the effectiveness of interventions in clinical psychology, 217 meta-analyses were selected.
+Reproducibility of scientific results could be considered as the minimal threshold of this credibility.
+We assessed the reproducibility of a sample of meta-analyses published between 2000-2020.
+From a random sample of 100 papers reporting results of meta-analyses of interventions in clinical psychology, 217 meta-analyses were selected.
 We first tried to retrieve the original data by recovering a data file, recoding the data from document files, or requesting it from original authors.
-Second, through a multi-stage workflow, we tried to reproduce the main results of each meta-analysis using these data.
-The original data were retrieved for 146 \textcolor{blue}{(67\%, 146/217)} meta-analyses.
-Of these, 52 showed a discrepancy larger than 5\% in the main results in the first stage.
-\textcolor{blue}{For 10 meta-analyses this discrepancy was solved after fixing a coding error and for 15 of them it was considered approximately reproduced in a qualitative assessment.} In the remaining 27 meta-analyses \textcolor{blue}{(18\%, 27/146)}, different issues were identified in an in-depth review of the papers, such as reporting inconsistencies, lack of data, or transcription errors.
-\textcolor{blue}{Nevertheless, the numerical discrepancies were mostly minor, with little or no impact on the conclusions.} Current practices of data sharing in meta-analyses hamper the reusability of meta-analytic data.
-The implementation of new tools would help to avoid certain errors in the meta-analysis reporting process.
+Second, through a multi-stage workflow, we tried to reproduce the main results of each meta-analysis.
+The original data were retrieved for 67\% (146/217) meta-analyses.
+\textcolor{blue}{While this rate showed an improvement over the years, in only 5\% of these cases was it possible to retrieve a data file ready for reuse.} Of these 146, 52 showed a discrepancy larger than 5\% in the main results in the first stage.
+For 10 meta-analyses this discrepancy was solved after fixing a coding error \textcolor{blue}{of our data retrieval process} and for 15 of them it was considered approximately reproduced in a qualitative assessment.
+In the remaining meta-analyses (18\%, 27/146), different issues were identified in an in-depth review, such as reporting inconsistencies, lack of data, or transcription errors.
+Nevertheless, the numerical discrepancies were mostly minor, with little or no impact on the conclusions.
+\textcolor{blue}{Overall, one of the biggest threats to the reproducibility of meta-analysis is related to data availability and current data sharing practices in meta-analysis.}
 }
@@
 The availability of the original analysis code (i.e., the original computational instructions in a programming language) facilitates reproducibility analysis by enabling simply re-running the code on the data.
-Regrettably, the analysis code is currently seldom available (Hardwicke et al., 2022, 2020; López-Nicolás et al., 2022).
+Regrettably, the analysis code is currently seldom available (Hardwicke et al., 2020, 2022; López-Nicolás et al., 2022).
 When only a verbal summary of the performed analyses is available in the research report (which is the most common scenario in practice), the original analysis needs to be reconstructed.
@@
 
-Reproducibility analysis \textcolor{blue}{of reported quantitative results} typically uses the original data available from the original authors (e.g., Artner et al., 2020; Hardwicke et al., 2021, 2018).
+Reproducibility analysis of reported quantitative results typically uses the original data available from the original authors (e.g., Artner et al., 2020; Hardwicke et al., 2018, 2021).
 This puts the focus of the assessment at factors such as the reusability of the available data, challenges for the reconstruction of the original analysis scheme, reporting errors, etc.
@@
 The full search strategies and a summary of the screening process are available at: \url{https://osf.io/z5vrn/}, and the workflow of the random selection process is available at: \url{https://osf.io/cp293/}.
-\textcolor{blue}{This sample size was based on our judgement of an acceptable trade-off between informativeness and feasibility.}
-From these 100 articles, each independent \textcolor{blue} {pairwise meta-analytic model of aggregate data fitted} on at least 10 primary studies was selected.
+This sample size was based on our judgement of an acceptable trade-off between informativeness and feasibility.
+From these 100 articles, each independent pairwise meta-analytic model of aggregate data fitted on at least 10 primary studies was selected.
 In case no meta-analysis reported in a paper had at least 10 studies, the meta-analysis with the highest number of primary studies was selected, which was the case for 29 of the articles included in this report.
-\textcolor{blue}{This criterion was established to focus on the main meta-analyses of each paper, based on the assumption that the search strategies would be designed to maximise the number of primary studies included that were related to the main aims of the paper.}
+This criterion was established to focus on the main meta-analyses of each paper, based on the assumption that the search strategies would be designed to maximise the number of primary studies included that were related to the main aims of the paper.
 
@@
 
-In order to be able to reproduce meta-analyses of \textcolor{blue}{aggregate data, primary-level}\footnote{By primary-level data we mean aggregate data from included primary studies.} effects sizes and their associated standard errors are required.
+In order to be able to reproduce meta-analyses of aggregate data, primary-level\footnote{By primary-level data we mean aggregate data from included primary studies.} effects sizes and their associated standard errors are required.
 These are generally computed from statistics retrieved from the primary studies such as means, standard deviations or sample sizes.
-We attempted to retrieve the least processed data possible.
-First, we sought for the statistics \textcolor{blue}{used to compute primary effect sizes (e.g., means, sd)}; second, we sought for the primary effects sizes \textcolor{blue}{already computed} and their standard errors (or, alternatively, the sampling variances): finally, we sought for the primary effects sizes and their confidence limits, from which the standard errors were approximated as follows:
+We attempted to retrieve the least processed data \textcolor{blue}{shared by the authors of the meta-analysis.} First, we sought for the statistics used to compute primary effect sizes (e.g., means, sd); second, we sought for the primary effects sizes already computed and their standard errors (or, alternatively, the sampling variances): finally, we sought for the primary effects sizes and their confidence limits, from which the standard errors were approximated as follows:
 \[se_i = (\frac{UB_i - LB_i}{2z_{\alpha/2}})\]
@@
 If the software used was not reported, we inferred this information from the default settings of the most used software in the sample, which was \emph{Comprehensive Meta-Analysis}.
-\textcolor{blue}{We designed this procedure to reconstruct the original analytical scheme when the original analysis script was not available instead of trying to request it from the original authors due to: (a) not necessarily all authors of included meta-analyses will actually have an analysis script to share, because many might have used point and click software, and (b) we expected analysis script availability to be very low, and requesting it would have meant sending request for virtually every paper included in our re-analysis.}
+We designed this procedure to reconstruct the original analytical scheme when the original analysis script was not available instead of trying to request it from the original authors due to: (a) not necessarily all authors of included meta-analyses will actually have an analysis script to share, because many might have used point and click software, and (b) we expected analysis script availability to be very low, and requesting it would have meant sending request for virtually every paper included in our re-analysis.
 
@@
 
-\textcolor{blue}{Data collection procedure was carried out by five of the authors.} At a first pilot stage, a random sample of five articles of the total pool was independently coded by the five members and, subsequently, in a series of meetings, disagreements between the coders were resolved by consensus.
+Data collection procedure was carried out by five of the authors.
+At a first pilot stage, a random sample of five articles of the total pool was independently coded by the five members and, subsequently, in a series of meetings, disagreements between the coders were resolved by consensus.
 Next, the initial pool of 100 included articles was split among four coders, 25 articles each.
@@
 Disagreements were resolved by consensus and by double-checking the original materials.
-\textcolor{blue}{Details about inter-coder agreement are reported in the Supplementary file.}
+Details about inter-coder agreement are reported in the Supplementary file.
 
@@
 
-Each meta-analysis was labelled using the following \textcolor{blue}{two-level}\footnote{This hierarchy is a minor deviation from the pre-registered protocol.
+Each meta-analysis was labelled using the following two-level\footnote{This hierarchy is a minor deviation from the pre-registered protocol.
 It is essentially the same and the results are identical.
 It was introduced to improve clarity.} reproducibility success scheme.
-\textcolor{blue}{First, each meta-analysis was labelled as: (a) process-reproducible; and (b) not process-reproducible.
-In our study, not process-reproducible refers to situations where we were unable to access the primary data neither through direct extraction nor upon request}\footnote{Process reproducibility, as described above, could imply a different situation if more conditions need to be met to proceed with the reproduction attempt.
+First, each meta-analysis was labelled as: (a) process-reproducible; and (b) not process-reproducible.
+In our study, not process-reproducible refers to situations where we were unable to access the primary data neither through direct extraction nor upon request\footnote{Process reproducibility, as described above, could imply a different situation if more conditions need to be met to proceed with the reproduction attempt.
 In our study, this is equivalent to data availability due to our design and the stage of the meta-analysis pipeline we focused on.}.
-\textcolor{blue}{Second, those labelled as process-reproducible} were labelled as: (a) reproducible; (b) numerical error; and (c) decision error.
+Second, those labelled as process-reproducible were labelled as: (a) reproducible; (b) numerical error; and (c) decision error.
 Similar to previous studies (Artner et al., 2020; Hardwicke et al., 2018, 2021) an index of numerical error was computed (see Protocol \url{https://osf.io/tq4uf/}).
@@
 
-\textcolor{blue}{Finally, the association between publication year and the possibility of retrieving the data in one of the ways conducted in this project were explored by fitting binary logistic regression models with publication year as predictor and process-reproducibility as dependent variable.
+Finally, the association between publication year and the possibility of retrieving the data in one of the ways conducted in this project were explored by fitting binary logistic regression models with publication year as predictor and process-reproducibility as dependent variable.
 We quantified the strength of the association by calculating odds ratios and 95\% confidence intervals based on the profile likelihood.
 These exploratory analyses were not pre-registered.
-Details and results are reported in Supplementary file.}
+Details and results are reported in Supplementary file.
 
@@
 From the 100 included papers, 217 independent meta-analyses were selected following the criteria explained above.
-These meta-analyses included 18.35 primary studies on average (sd = 17.25; median = 13; interquartile range = 10-19; range = 3-134)), \textcolor{blue}{and were cited 108.39 times on average (sd = 151.00; median = 57; interquartile range = 29-128; range = 3-1036)}\footnote{Citation counts were retrieved from CrossRef API using the \emph{rcrossref} package (Chamberlain et al., 2023).
+These meta-analyses included 18.35 primary studies on average (sd = 17.25; median = 13; interquartile range = 10-19; range = 3-134), and were cited 108.39 times on average (sd = 151.00; median = 57; interquartile range = 29-128; range = 3-1036)\footnote{Citation counts were retrieved from CrossRef API using the \emph{rcrossref} package (Chamberlain et al., 2023).
 For two cases in which CrossRef did not return data, citation counts were consulted in Google Scholar.
 Both queries were done on 20/03/2023.}.
-Figure 2 displays the distribution of number of primary studies among the meta-analyses included in our sample \textcolor{blue}{(panel A), the publication year distribution among the papers included in our sample (panel B) as well as the citation count distribution of those papers (panel C).} Original results and characteristics of these meta-analyses are available at: \url{https://osf.io/8jzbk}
+Figure 2 displays the distribution of number of primary studies among the meta-analyses included in our sample (panel A), the publication year distribution among the papers included in our sample (panel B) as well as the citation count distribution of those papers (panel C).
+Original results and characteristics of these meta-analyses are available at: \url{https://osf.io/8jzbk}
 
@@
 3a) were labelled as process reproducible.
+\textcolor{blue}{Additionally, as the time span covered is fairly wide, the process reproducible rate was also computed for different time periods.
+The meta-analyses were grouped into five-year periods, except for the initial period, which was grouped into a ten-year period due to the limited number of meta-analyses available during the first five-year period, which consisted of only five meta-analyses.
+The process reproducibility rate was }41\%, (12/29), 59\%, (44/75), and 80\%, (90/113) \textcolor{blue}{for meta-analyses published between 2000 and 2010, 2011 and 2015, and 2016 and 2020, respectively (see Fig.
+3a).
+This trend is further explored in the Supplementary file available at: https://osf.io/fjhpw.}
+
 Of these 146 meta-analyses, in about half of the cases the primary data was retrieved from a forest plot in the paper itself and in about a third of the cases the primary data was retrieved from supplementary files (see Fig.
 3b for further details).
-Although attempts were made to retrieve data for 78 meta-analyses from 25 different papers by emailing the corresponding authors, data was only retrieved for 7 meta-analyses, from 3 different papers (12\%, 3/25, see Fig.
+Although attempts were made to retrieve data for 75 meta-analyses from 25 different papers by emailing the corresponding authors, data was only retrieved for 4 meta-analyses, from 3 different papers (12\%, 3/25, see Fig.
 3c).
@@
 In most cases, when the meta-analytic data was available, it was shared in document formats.
-Data \textcolor{blue}{were retrieved from} tables or forest plots in \emph{pdf} or \emph{docx} format---either in the document itself or in the supplementary materials---\textcolor{blue}{in} 92\% (134/146) \textcolor{blue}{of the cases}.
+Data were retrieved from tables or forest plots in \emph{pdf} or \emph{docx} format---either in the document itself or in the supplementary materials---in 92\% (134/146) of the cases.
 This required a manual recoding of the primary data to be able to reuse them.
@@
 After this, 10 were re-labelled as reproduced and 7 still had relevant discrepancies.
-Furthermore, 15 were labelled as \textcolor{blue}{approximately reproduced or reproduced with minor adjustment} in a qualitative check because the discrepancy was probably explained by rounding issues, inverted signs for results (when effect sizes were reported in absolute values) and primary data, minor reporting errors, or minor adjustments in the analytical scheme\footnote{Full details in Supplementary File at: \url{https://osf.io/fjhpw}}.
+Furthermore, 15 were labelled as approximately reproduced or reproduced with minor adjustment in a qualitative check because the discrepancy was probably explained by rounding issues, inverted signs for results (when effect sizes were reported in absolute values) and primary data, minor reporting errors, or minor adjustments in the analytical scheme\footnote{Full details in Supplementary File at: \url{https://osf.io/fjhpw}}.
 In the remaining 20, and in the 7 re-analysed again without success, some issues or relevant discrepancies without apparent explanation were found.
@@
 As shown in Figures 5 and 6, the discrepancies found in the heterogeneity statistic \(I^2\) are larger than those found in the summary effects and their confidence intervals.
-\textcolor{blue}{The Pearson's correlation between the summary effect and $I^2$ discrepancies was .172.} The lack of precision of the available data (rounded data) or incomplete information on aspects such as the tau-squared estimator applied seem to have a substantial impact on the reproducibility of this result.
+The Pearson's correlation between the summary effect and \(I^2\) discrepancies was .172.
+The lack of precision of the available data (rounded data) or incomplete information on aspects such as the tau-squared estimator applied seem to have a substantial impact on the reproducibility of this result.
 
@@
 Also, in a paper where primary data were available in both a table and a forest plot, minor inconsistencies were found between the primary data of the table and the forest plot.
-\textcolor{blue}{These examples of inconsistencies in original results or data were found in 4 cases (3\%, 4/146).} These appeared to be typos.
+These examples of inconsistencies in original results or data were found in 4 cases (3\%, 4/146).
+These appeared to be typos.
 Furthermore, some inconsistencies were found with respect to the number of primary studies included in each meta-analysis.
@@
 
-\textcolor{blue}{A more positive sign comes from the positive association between publication year and the possibility of retrieving the data that was observed in an exploratory analysis in the supplementary materials.
-This tentatively suggests that data-availability is improving over time.
-This observation could be related to the existence of well-established meta-analysis reporting guidelines.
-For instance, the first PRISMA guideline} (Moher et al., 2009) \textcolor{blue}{encouraged meta-analyst to report results of primary studies (e.g.
-primary effect sizes and their confidence interval through a forest plot, as was a common scenario among the cases included in this project), and the latest PRISMA guideline} (Page et al., 2021) \textcolor{blue}{which puts more emphasis on appropriate data sharing through data files ready for reuse.} At the same time in only 5\% of the cases where data were retrieved in our sample were we able to retrieve the data in a machine-readable data file that was ready for reuse (e.g., \emph{csv}, \emph{xlsx}).
+Nevertheless, a more positive sign comes from the positive association between publication year and the possibility of retrieving the data.
+\textcolor{blue}{The results tentatively suggest a trend of improving data availability over the years, with a notable rate of 80\% observed in meta-analyses published between 2016 and 2020.} This observation could be related to the existence of well-established meta-analysis reporting guidelines.
+For instance, the first PRISMA guideline (Moher et al., 2009) encouraged meta-analyst to report results of primary studies (e.g.~primary effect sizes and their confidence interval through a forest plot, as was a common scenario among the cases included in this project), and the latest PRISMA guideline (Page et al., 2021) which puts more emphasis on appropriate data sharing through data files ready for reuse.
+At the same time in only 5\% of the cases where data were retrieved in our sample were we able to retrieve the data in a machine-readable data file that was ready for reuse (e.g., \emph{csv}, \emph{xlsx}).
 Most often the data had to be retrieved from files in document format (e.g., \emph{docx}, \emph{pdf}).
@@
 Furthermore, because the tables in manuscript are often generated manually in document file formats (e.g.~Word), we observed examples where this introduced another source of error.
-\textcolor{blue}{The foregoing discussion raises a key point about how time consuming the appraisal of meta-analytic reproducibility currently is, and how efficiency would be improved by having open access to the underlying meta-analytic data in data file formats ready for reuse.
-The latest PRISMA guidelines, along with some initiatives that promote appropriate data sharing} (e.g.
-Wilkinson et al., 2016) \textcolor{blue}{have the potential to generate significant improvements in the re-use of meta-analytic data in the years ahead.
-In this regard, our results provide a useful baseline for future assessments.}
+The foregoing discussion raises a key point about how time consuming the appraisal of meta-analytic reproducibility currently is, and how efficiency would be improved by having open access to the underlying meta-analytic data in data file formats ready for reuse.
+The latest PRISMA guidelines, along with some initiatives that promote appropriate data sharing (e.g.
+Wilkinson et al., 2016) have the potential to generate significant improvements in the re-use of meta-analytic data in the years ahead.
+In this regard, our results provide a useful baseline for future assessments.
 
@@
 In most cases, the original analyses were reconstructed from the description provided in the paper itself, which was not always rich in detail, so many of these computational details had to be inferred from the default settings of the software authors used.
-The availability of analysis scripts often shows similar rates, both in meta-analyses (Page et al., 2022; Polanin et al., 2020) and in primary research (Hardwicke et al., 2022, 2020).
+The availability of analysis scripts often shows similar rates, both in meta-analyses (Page et al., 2022; Polanin et al., 2020) and in primary research (Hardwicke et al., 2020, 2022).
 This makes it more difficult to easily check the computational reproducibility of the results from such studies.
@@
 
-This research has been funded with a grant from the Spanish Ministry of Science and Innovation (Project PID2019-104080GB-I00/AEI/10.13039/501100011033, FEDER funds) and by the Spanish Ministry of Universities (predoctoral grant: FPU18/04805).
+This research has been funded with a grant from the Spanish Ministry of Science and Innovation (Project PID2019-104080GB-I00/AEI/10.13039/501100011033, and PID2019-104033GA-I00/MCIN/AEI/10.13039/501100011033, FEDER funds) and by the Spanish Ministry of Universities (predoctoral grant: FPU18/04805).
 

### 2023-06-21 supplementary_file.Rmd
Second revision

@@
 ```
-
 # Inter-coder agreement 
-
 Out of the 25 papers selected to carry out independent double-coding, 21 had primary data available for one or more meta-analyses selected under the criteria explained in the main manuscript.
@@
 # Sensitivity analysis using other possible criteria
-
 In the first stage, a cut-off point of 5% discrepancy between reported and reproduced results was set to screen meta-analyses.
@@
 # Data availability over years
+\textcolor{blue}{The publication year range of the included meta-analyses in our study is quite extensive.
+The initial pool, from which we randomly selected a sample, comprised meta-analytic reports published between 2000 and 2020, encompassing a span of two decades.
+For our analysis, we focused on a random sample of 100 of these meta-analytic reports.
+From the 100 included reports, 217 independent meta-analyses were selected following the criteria explained in the ‘Identification and selection of articles and meta-analyses’ section of the main paper.
+These meta-analyses were published between} `r min(df_mas_pyear1$publication_year)` and `r max(df_mas_pyear1$publication_year)` (`r sprintf("mean = %0.2f; sd = %0.2f; median = %0.0f; interquartile range = %0.0f-%0.0f", mean(df_mas_pyear1$publication_year), sd(df_mas_pyear1$publication_year), median(df_mas_pyear1$publication_year), quantile(df_mas_pyear1$publication_year)[2], quantile(df_mas_pyear1$publication_year)[3])`).
+\textcolor{blue}{As an unrestricted random sample, the publication year distribution is clearly left-skewed, with} `r sprintf("%0.1f%%", (nrow(subset(df_mas_pyear1, publication_year >= 2010))/nrow(df_mas_pyear1))*100)` \textcolor{blue}{of the included meta-analyses published between 2010 and 2020 (see Figure 2 of the main paper for the full distribution).}
+
+\textcolor{blue}{As shown in the main paper (see Figure 3a), there appears to be an improvement in the rate of data availability over the years.
+The overall data availability rate for the full sample was found to be 67\%.
+However, when examining meta-analyses published within specific time periods, the rates varied.
+For meta-analyses published between 2000 and 2010, the data availability rate was 41\%.
+For those published between 2011 and 2015, the rate increased to 59\%.
+Notably, meta-analyses published between 2016 and 2020 exhibited the highest data availability rate of 80\%.
+These findings suggest a positive trend of improved data availability in more recent years.}
 
@@
   linesep = '\\addlinespace',
-  col.names = c("Level", "Before 10s exclusion", "Slope", "OR", "OR LL", "OR UL", "$p$"),
-  align = c("l", "l", "l","l", "l", "l","l"),
+  col.names = c("Level", "Before 10s exclusion", "Slope", "OR", "OR LL", "OR UL", "$p$", "Pertecenage change"),
+  align = c("l", "l", "l","l", "l", "l","l", "l"),
   caption = "Binary logistic regression models results",
@@
   kable_styling(full_width = T, latex_options = "hold_position") %>% 
-  column_spec(2, width = "2cm")
+  column_spec(c(1, 2, 8), width = "2cm")
 
@@
 We found that all 4 ORs computed were > 1, indicating a higher probability of retrieving data the more recent the publication year of the meta-analysis.
-Additionally, in only one of the cases (paper-level model without excluding cases published before 2010) did the 95%CI of the OR include a value < 1.
+\textcolor{blue}{Specifically, the odds increased from 11.85\% to 34.46\% per year.}Additionally, in only one of the cases (paper-level model without excluding cases published before 2010) did the 95%CI of the OR include a value < 1.
 \pagebreak

### 2023-06-21 analysis/00_functions.R

@@ -15,7 +15,7 @@ pacman::p_load(tidyverse, metafor)
 # width: desired bar width
 #
 
-customized_barplot<- function(d, pal, title, legend, width=0.35, rate=TRUE){
+customized_barplot<- function(d, pal, title, legend, width=0.35, rate=TRUE, NPos = 0.5){
   
   plt <- ggplot(data=d, aes(x=NA, y=perc, fill=Item)) +
     geom_bar(colour = 'black', stat="identity", width = width) +
@@ -40,7 +40,7 @@ customized_barplot<- function(d, pal, title, legend, width=0.35, rate=TRUE){
           axis.title.y=element_blank(),
           axis.text.y=element_blank(),
           axis.ticks.y=element_blank(),
-          axis.title.x=element_blank(),
+          axis.title.x= element_blank(),
           plot.title = element_text(size = 15, face = "bold")) 
   
   if (rate == TRUE) {  
@@ -61,7 +61,7 @@ customized_barplot<- function(d, pal, title, legend, width=0.35, rate=TRUE){
     ggtitle(sprintf("      %s", title)) +
     coord_flip(clip = 'off') +
     geom_text(
-      x = 0.5,
+      x = NPos,
       y = sum(d$perc),
       inherit.aes = FALSE,
       label = sprintf("N = %i", sum(d$n)),

### 2023-06-21 analysis/01_importing_data_and_descriptives.R

@@ -45,6 +45,38 @@ df_process_rep<- df_mas %>%
   rename(perc=est)%>%
   mutate_if(is.numeric, round, 2)
 
+#Process reproducibility by year
+
+df_process_rep2<- subset(df_mas, publication_year <= 2010) %>% 
+  select(order, ID, orign_data) %>% 
+  mutate(Item = ifelse(orign_data!="not_available", "Yes", "No")) %>% 
+  group_by(Item) %>% 
+  tally() %>% 
+  cbind(rbind(BinomCI(.$n[1], .$n[1]+.$n[2], conf.level = 0.95, method = "wilson"),
+              BinomCI(.$n[2], .$n[1]+.$n[2], conf.level = 0.95, method = "wilson")))%>%
+  rename(perc=est)%>%
+  mutate_if(is.numeric, round, 2)
+
+df_process_rep3<- subset(df_mas, publication_year > 2010 & publication_year <= 2015) %>% 
+  select(order, ID, orign_data) %>% 
+  mutate(Item = ifelse(orign_data!="not_available", "Yes", "No")) %>% 
+  group_by(Item) %>% 
+  tally() %>% 
+  cbind(rbind(BinomCI(.$n[1], .$n[1]+.$n[2], conf.level = 0.95, method = "wilson"),
+              BinomCI(.$n[2], .$n[1]+.$n[2], conf.level = 0.95, method = "wilson")))%>%
+  rename(perc=est)%>%
+  mutate_if(is.numeric, round, 2)
+
+df_process_rep4<- subset(df_mas, publication_year > 2015) %>% 
+  select(order, ID, orign_data) %>% 
+  mutate(Item = ifelse(orign_data!="not_available", "Yes", "No")) %>% 
+  group_by(Item) %>% 
+  tally() %>% 
+  cbind(rbind(BinomCI(.$n[1], .$n[1]+.$n[2], conf.level = 0.95, method = "wilson"),
+              BinomCI(.$n[2], .$n[1]+.$n[2], conf.level = 0.95, method = "wilson")))%>%
+  rename(perc=est)%>%
+  mutate_if(is.numeric, round, 2)
+
 
 #Source of primary data
 
@@ -278,20 +310,86 @@ figure2<- ggarrange(hist_primary_studies, hist_pubyear + rremove("ylab"), hist_c
 
 Moonrise3 <-rev(wes_palette("Moonrise3", n=5))
 
[…]

### 2023-06-21 analysis/06_supplementary.R

@@ -80,6 +80,8 @@ df_mas_pyear1<-read_xlsx(here::here("data",
   mutate(publication_year_centered = scale(publication_year)) %>% 
   mutate(process_rep = ifelse(orign_data!="not_available", 1, 0))
 
+  
+
 df_mas_pyear2<- df_mas_pyear1 %>% 
   group_by(order) %>% 
   mutate(process_rep2 = ifelse(all(orign_data=="not_available"), 0, ifelse(any(orign_data=="not_available"), 2, 1))) %>% 
@@ -102,7 +104,8 @@ log_reg_results<- data.frame(Level = c("Meta-analysis", "Paper", "Meta-analysis"
                              OR = c(odds.ratio(log_reg_malevel)$OR[2], odds.ratio(log_reg_paperlvl)$OR[2], odds.ratio(log_reg_malevel_10)$OR[2], odds.ratio(log_reg_paperlvl_10)$OR[2]),
                              "OR LL" = c(odds.ratio(log_reg_malevel)$`2.5 %`[2], odds.ratio(log_reg_paperlvl)$`2.5 %`[2], odds.ratio(log_reg_malevel_10)$`2.5 %`[2], odds.ratio(log_reg_paperlvl_10)$`2.5 %`[2]),
                              "OR UL" = c(odds.ratio(log_reg_malevel)$`97.5 %`[2], odds.ratio(log_reg_paperlvl)$`97.5 %`[2], odds.ratio(log_reg_malevel_10)$`97.5 %`[2], odds.ratio(log_reg_paperlvl_10)$`97.5 %`[2]),
-                             p = c(coef(summary(log_reg_malevel))[8], coef(summary(log_reg_paperlvl))[8], coef(summary(log_reg_malevel_10))[8], coef(summary(log_reg_paperlvl_10))[8])) %>%
+                             p = c(coef(summary(log_reg_malevel))[8], coef(summary(log_reg_paperlvl))[8], coef(summary(log_reg_malevel_10))[8], coef(summary(log_reg_paperlvl_10))[8])) %>% 
+  mutate("Percentage change" = ifelse(OR < 1, (1/OR - 1)*-100, (OR - 1)*100  )) %>% 
   mutate_if(is.numeric, round, 3)
   
 

### 2023-08-10 submission.Rmd
Accepted version

@@
  - name: "Maria Rubio-Aparicio"
-   affiliation: "3"
+   affiliation: "1"
  - name: "Alejandro Sandoval-Lentisco"
@@
    institution: "Eindhoven University of Technology, The Netherlands"
- - id: "3"
-   institution: "University of Alicante, Spain"
 
@@
 The original data were retrieved for 67% (146/217) meta-analyses.
-\textcolor{blue}{While this rate showed an improvement over the years, in only 5\% of these cases was it possible to retrieve a data file ready for reuse.} Of these 146, 52 showed a discrepancy larger than 5% in the main results in the first stage.
-For 10 meta-analyses this discrepancy was solved after fixing a coding error \textcolor{blue}{of our data retrieval process} and for 15 of them it was considered approximately reproduced in a qualitative assessment.
+While this rate showed an improvement over the years, in only 5\% of these cases was it possible to retrieve a data file ready for reuse.
+Of these 146, 52 showed a discrepancy larger than 5% in the main results in the first stage.
+For 10 meta-analyses this discrepancy was solved after fixing a coding error of our data retrieval process and for 15 of them it was considered approximately reproduced in a qualitative assessment.
 In the remaining meta-analyses (18%, 27/146), different issues were identified in an in-depth review, such as reporting inconsistencies, lack of data, or transcription errors.
 Nevertheless, the numerical discrepancies were mostly minor, with little or no impact on the conclusions.
-\textcolor{blue}{Overall, one of the biggest threats to the reproducibility of meta-analysis is related to data availability and current data sharing practices in meta-analysis.}
+Overall, one of the biggest threats to the reproducibility of meta-analysis is related to data availability and current data sharing practices in meta-analysis.
 
@@
 Second, we verified the outcome reproducibility of the meta-analyses that were process-reproducible using the available data.
-Where previous work focused on the reproducibility of primary effect sizes \textcolor{blue}{by recoding data from primary studies}, we explored meta-analysis outcome reproducibility using the primary \textcolor{blue}{data} already coded by the original authors.
-\textcolor{blue}{Therefore, we attempted to retrieve the data shared by the authors of the meta-analysis.}
+Where previous work focused on the reproducibility of primary effect sizes by recoding data from primary studies, we explored meta-analysis outcome reproducibility using the primary data already coded by the original authors.
+Therefore, we attempted to retrieve the data shared by the authors of the meta-analysis.
 
@@
 These are generally computed from statistics retrieved from the primary studies such as means, standard deviations or sample sizes.
-We attempted to retrieve the least processed data \textcolor{blue}{shared by the authors of the meta-analysis.} First, we sought for the statistics used to compute primary effect sizes (e.g., means, sd); second, we sought for the primary effects sizes already computed and their standard errors (or, alternatively, the sampling variances): finally, we sought for the primary effects sizes and their confidence limits, from which the standard errors were approximated as follows:
+We attempted to retrieve the least processed data shared by the authors of the meta-analysis.
+First, we sought for the statistics used to compute primary effect sizes (e.g., means, sd); second, we sought for the primary effects sizes already computed and their standard errors (or, alternatively, the sampling variances): finally, we sought for the primary effects sizes and their confidence limits, from which the standard errors were approximated as follows:
 $$se_i = (\frac{UB_i - LB_i}{2z_{\alpha/2}})$$
@@
 3a) were labelled as process reproducible.
-\textcolor{blue}{Additionally, as the time span covered is fairly wide, the process reproducible rate was also computed for different time periods.
+Additionally, as the time span covered is fairly wide, the process reproducible rate was also computed for different time periods.
 The meta-analyses were grouped into five-year periods, except for the initial period, which was grouped into a ten-year period due to the limited number of meta-analyses available during the first five-year period, which consisted of only five meta-analyses.
-The process reproducibility rate was }`r sprintf("%0.0f%%, (%0.0f/%0.0f)", df_process_rep2$perc[2]*100, df_process_rep2$n[2], sum(df_process_rep2$n))`, `r sprintf("%0.0f%%, (%0.0f/%0.0f)", df_process_rep3$perc[2]*100, df_process_rep3$n[2], sum(df_process_rep3$n))`, and `r sprintf("%0.0f%%, (%0.0f/%0.0f)", df_process_rep4$perc[2]*100, df_process_rep4$n[2], sum(df_process_rep4$n))` \textcolor{blue}{for meta-analyses published between 2000 and 2010, 2011 and 2015, and 2016 and 2020, respectively (see Fig.
+The process reproducibility rate was `r sprintf("%0.0f%%, (%0.0f/%0.0f)", df_process_rep2$perc[2]*100, df_process_rep2$n[2], sum(df_process_rep2$n))`, `r sprintf("%0.0f%%, (%0.0f/%0.0f)", df_process_rep3$perc[2]*100, df_process_rep3$n[2], sum(df_process_rep3$n))`, and `r sprintf("%0.0f%%, (%0.0f/%0.0f)", df_process_rep4$perc[2]*100, df_process_rep4$n[2], sum(df_process_rep4$n))` for meta-analyses published between 2000 and 2010, 2011 and 2015, and 2016 and 2020, respectively (see Fig.
 3a).
-This trend is further explored in the Supplementary file available at: https://osf.io/fjhpw.}
+This trend is further explored in the Supplementary file available at: https://osf.io/fjhpw.
 
@@
 Nevertheless, a more positive sign comes from the positive association between publication year and the possibility of retrieving the data.
-\textcolor{blue}{The results tentatively suggest a trend of improving data availability over the years, with a notable rate of 80\% observed in meta-analyses published between 2016 and 2020.} This observation could be related to the existence of well-established meta-analysis reporting guidelines.
+The results tentatively suggest a trend of improving data availability over the years, with a notable rate of 80% observed in meta-analyses published between 2016 and 2020.
+This observation could be related to the existence of well-established meta-analysis reporting guidelines.
 For instance, the first PRISMA guideline [@moher2009] encouraged meta-analyst to report results of primary studies (e.g.

### 2023-08-10 submission.tex
Accepted version

@@
   pdftitle={Reproducibility of published meta-analyses on clinical psychological interventions},
-  pdfauthor={Rubén López-Nicolás1, Daniel Lakens2, Jose A. López-López1, Maria Rubio-Aparicio3, Alejandro Sandoval-Lentisco1, Carmen López-Ibáñez1, Desirée Blázquez-Rincón1, \& Julio Sánchez-Meca1},
+  pdfauthor={Rubén López-Nicolás1, Daniel Lakens2, Jose A. López-López1, Maria Rubio-Aparicio1, Alejandro Sandoval-Lentisco1, Carmen López-Ibáñez1, Desirée Blázquez-Rincón1, \& Julio Sánchez-Meca1},
   pdflang={en-EN},
@@
 \author{Rubén López-Nicolás\textsuperscript{1}, Daniel Lakens\textsuperscript{2}, Jose A.
-López-López\textsuperscript{1}, Maria Rubio-Aparicio\textsuperscript{3}, Alejandro Sandoval-Lentisco\textsuperscript{1}, Carmen López-Ibáñez\textsuperscript{1}, Desirée Blázquez-Rincón\textsuperscript{1}, \& Julio Sánchez-Meca\textsuperscript{1}}
+López-López\textsuperscript{1}, Maria Rubio-Aparicio\textsuperscript{1}, Alejandro Sandoval-Lentisco\textsuperscript{1}, Carmen López-Ibáñez\textsuperscript{1}, Desirée Blázquez-Rincón\textsuperscript{1}, \& Julio Sánchez-Meca\textsuperscript{1}}
 \date{}
@@
 
-\affiliation{\vspace{0.5cm}\textsuperscript{1} University of Murcia, Spain\\\textsuperscript{2} Eindhoven University of Technology, The Netherlands\\\textsuperscript{3} University of Alicante, Spain}
+\affiliation{\vspace{0.5cm}\textsuperscript{1} University of Murcia, Spain\\\textsuperscript{2} Eindhoven University of Technology, The Netherlands}
 
@@
 The original data were retrieved for 67\% (146/217) meta-analyses.
-\textcolor{blue}{While this rate showed an improvement over the years, in only 5\% of these cases was it possible to retrieve a data file ready for reuse.} Of these 146, 52 showed a discrepancy larger than 5\% in the main results in the first stage.
-For 10 meta-analyses this discrepancy was solved after fixing a coding error \textcolor{blue}{of our data retrieval process} and for 15 of them it was considered approximately reproduced in a qualitative assessment.
+While this rate showed an improvement over the years, in only 5\% of these cases was it possible to retrieve a data file ready for reuse.
+Of these 146, 52 showed a discrepancy larger than 5\% in the main results in the first stage.
+For 10 meta-analyses this discrepancy was solved after fixing a coding error of our data retrieval process and for 15 of them it was considered approximately reproduced in a qualitative assessment.
 In the remaining meta-analyses (18\%, 27/146), different issues were identified in an in-depth review, such as reporting inconsistencies, lack of data, or transcription errors.
 Nevertheless, the numerical discrepancies were mostly minor, with little or no impact on the conclusions.
-\textcolor{blue}{Overall, one of the biggest threats to the reproducibility of meta-analysis is related to data availability and current data sharing practices in meta-analysis.}
+Overall, one of the biggest threats to the reproducibility of meta-analysis is related to data availability and current data sharing practices in meta-analysis.
 }
@@
 These are generally computed from statistics retrieved from the primary studies such as means, standard deviations or sample sizes.
-We attempted to retrieve the least processed data \textcolor{blue}{shared by the authors of the meta-analysis.} First, we sought for the statistics used to compute primary effect sizes (e.g., means, sd); second, we sought for the primary effects sizes already computed and their standard errors (or, alternatively, the sampling variances): finally, we sought for the primary effects sizes and their confidence limits, from which the standard errors were approximated as follows:
+We attempted to retrieve the least processed data shared by the authors of the meta-analysis.
+First, we sought for the statistics used to compute primary effect sizes (e.g., means, sd); second, we sought for the primary effects sizes already computed and their standard errors (or, alternatively, the sampling variances): finally, we sought for the primary effects sizes and their confidence limits, from which the standard errors were approximated as follows:
 \[se_i = (\frac{UB_i - LB_i}{2z_{\alpha/2}})\]
@@
 3a) were labelled as process reproducible.
-\textcolor{blue}{Additionally, as the time span covered is fairly wide, the process reproducible rate was also computed for different time periods.
+Additionally, as the time span covered is fairly wide, the process reproducible rate was also computed for different time periods.
 The meta-analyses were grouped into five-year periods, except for the initial period, which was grouped into a ten-year period due to the limited number of meta-analyses available during the first five-year period, which consisted of only five meta-analyses.
-The process reproducibility rate was }41\%, (12/29), 59\%, (44/75), and 80\%, (90/113) \textcolor{blue}{for meta-analyses published between 2000 and 2010, 2011 and 2015, and 2016 and 2020, respectively (see Fig.
+The process reproducibility rate was 41\%, (12/29), 59\%, (44/75), and 80\%, (90/113) for meta-analyses published between 2000 and 2010, 2011 and 2015, and 2016 and 2020, respectively (see Fig.
 3a).
-This trend is further explored in the Supplementary file available at: https://osf.io/fjhpw.}
+This trend is further explored in the Supplementary file available at: \url{https://osf.io/fjhpw}.
 
@@
 3b for further details).
-Although attempts were made to retrieve data for 75 meta-analyses from 25 different papers by emailing the corresponding authors, data was only retrieved for 4 meta-analyses, from 3 different papers (12\%, 3/25, see Fig.
+Although attempts were made to retrieve data for 78 meta-analyses from 25 different papers by emailing the corresponding authors, data was only retrieved for 7 meta-analyses, from 3 different papers (12\%, 3/25, see Fig.
 3c).
@@
 Furthermore, when data was reported through general tables (i.e.~tables listing all the primary studies included with their characteristics), the meta-analysis associated with each data entry was not always obvious, leading to the time-consuming task of matching each data entry with each independent meta-analytic result reported in the paper.
-There were only 4 meta-analyses (from three different papers) of the 146 meta-analyses labelled as process reproducible (3\%), where the task of retrieving the data required simply downloading the data in an machine-readable data file format.
+There were only 7 meta-analyses (from three different papers) of the 146 meta-analyses labelled as process reproducible (5\%), where the task of retrieving the data required simply downloading the data in an machine-readable data file format.
 On the other hand, as shown in Figure 3c, when the necessary data was not available, retrieving it upon request to the original authors led to a low response rate.
@@
 Nevertheless, a more positive sign comes from the positive association between publication year and the possibility of retrieving the data.
-\textcolor{blue}{The results tentatively suggest a trend of improving data availability over the years, with a notable rate of 80\% observed in meta-analyses published between 2016 and 2020.} This observation could be related to the existence of well-established meta-analysis reporting guidelines.
+The results tentatively suggest a trend of improving data availability over the years, with a notable rate of 80\% observed in meta-analyses published between 2016 and 2020.
+This observation could be related to the existence of well-established meta-analysis reporting guidelines.
 For instance, the first PRISMA guideline (Moher et al., 2009) encouraged meta-analyst to report results of primary studies (e.g.~primary effect sizes and their confidence interval through a forest plot, as was a common scenario among the cases included in this project), and the latest PRISMA guideline (Page et al., 2021) which puts more emphasis on appropriate data sharing through data files ready for reuse.
